---
output: 
  #word_document: default
  #html_document: rmarkdown::github_document
  #bookdown::pdf_document2: 
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
    latex_engine: xelatex
    highlight: tango
    extra_dependencies: ["float"]
mainfont: Roboto Condensed
lang: en
fontsize: 11pt
geometry: margin=1in
urlcolor: blue
linkcolor: blue
editor_options: 
  chunk_output_type: console
params: 
    region: NA
title: "`r paste0('CLIAR Regional Profile Report: ', params$region)`"
author: ""  
date: |
 | \textcolor[RGB]{0,35,69}{\textbf{`r format(Sys.time(), '%Y-%m-%d')`}}
header-includes: 
  \usepackage{titling}
  \usepackage{graphicx}
  \usepackage{color}
  \usepackage{fontspec}
  \usepackage{background}
  \pretitle{
    \begin{center}
    \includegraphics[width=7in]{cliar.png}\LARGE\\
  }
  \backgroundsetup{
    scale=0.85,
    color=black,
    opacity=1,
    angle=0,
    position=current page.south,
    hshift=8cm,
    vshift=1.5cm,
    contents={\includegraphics[height=1cm]{wb-logo.jpg}}
  }
---

```{r setup,  include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.pos = "H", out.extra = "")

packages <- c("tidyverse","here","knitr","sf","ggtext","showtext","ggflags","countrycode","geomtextpath","patchwork","ggbeeswarm")
pacman::p_load(packages,character.only = TRUE)

font_add_google("Roboto Condensed")
showtext_auto()
options(scipen=999, dplyr.summarise.inform = FALSE)

# params <- list(region = "Latin America & Caribbean")
source(here("regional_profile/aux", "fun_plots.R"))

# viz id ----
id_colors <- list(
  primary = "#002244"
)

threshold <- "Default"

 if (threshold=="Default"){
      cutoff<-c(25,50)
      custom_levels <- c("Weak (bottom 25%)", "Emerging (25% - 50%)", "Strong (top 50%)")
    } else if (threshold=="Terciles")
    {
      cutoff<-c(33,66)
      custom_levels <- c("Weak (bottom 33%)", "Emerging (33% - 66%)", "Strong (top 34%)")
    }

if (cutoff[[1]]==25){
  colors <-
    c(
      "Weak (bottom 25%)" = "#D2222D",
      "Emerging (25% - 50%)" = "#FFBF00",
      "Strong (top 50%)" = "#238823"
    )
  } else if (cutoff[[1]]==33){
    colors <-c(
      "Weak (bottom 33%)" = "#D2222D",
      "Emerging (33% - 66%)" = "#FFBF00",
      "Strong (top 34%)" = "#238823"
    )
  }

status_order <- c(
  "Strong (top 50%)",
  "Emerging (25% - 50%)",
  "Weak (bottom 25%)"
)

income_order <- c(
  "Low income",
  "Lower middle income",
  "Upper middle income",
  "High income"
)

# data ----
income_class <- read_csv2(
  here(
   "regional_profile/data/class_income_fy24.csv"
  )
) 

country_flags_codes <- countrycode::codelist

data <- read_csv2(
  here(
    "regional_profile/data/countries_vs_region.csv"
  )
) |>
  filter(
    comparison_group == params$region
  ) |>
  left_join(
    income_class |> select(country_code, country, income_group), by = c("country_name" = "country")
  ) |> 
  filter(!is.na(var_name)) |>
  relocate(comparison_group, base_country, country_code, country_name, income_group) |>
  left_join(
    country_flags_codes |> select(genc3c,ecb),
    by = c("country_code" = "genc3c")
  ) |>
  relocate(ecb, .after = country_code) |>
  mutate(
    ecb = tolower(ecb),
    ecb = case_when(
      country_name == "West Bank and Gaza" ~ "ps",
      country_name == "Kosovo" ~ "xk",
      TRUE ~ ecb
    ),
    status = case_when(
      status == "Strong\n(top 50%)" ~ "Strong (top 50%)",
      status == "Emerging\n(25% - 50%)" ~ "Emerging (25% - 50%)",
      status == "Weak\n(bottom 25%)" ~ "Weak (bottom 25%)"
    )
  )

data_clusters <- read_csv2(
  here(
    "regional_profile/data/countries_vs_region_clusters.csv"
  )
) |>
  filter(
    comparison_group == params$region
  ) |>
  left_join(
    income_class |> select(country_code, country, income_group), by = c("country_name" = "country")
  ) |> 
  #filter(!is.na(var_name)) |>
  relocate(comparison_group, base_country, country_code, country_name, income_group) |>
  left_join(
    country_flags_codes |> select(genc3c,ecb),
    by = c("country_code" = "genc3c")
  ) |>
  relocate(ecb, .after = country_code) |>
  mutate(
    ecb = tolower(ecb),
    ecb = case_when(
      country_name == "West Bank and Gaza" ~ "ps",
      country_name == "Kosovo" ~ "xk",
      TRUE ~ ecb
    ),
     status = case_when(
      status == "Strong\n(top 50%)" ~ "Strong (top 50%)",
      status == "Emerging\n(25% - 50%)" ~ "Emerging (25% - 50%)",
      status == "Weak\n(bottom 25%)" ~ "Weak (bottom 25%)"
    )
  )

countries_sf <- read_rds(
  here(
   "regional_profile/data/countries_sf.rds"
  )
) |>
  mutate(
    group_selected = ifelse(country_code %in% data$country_code, "Y", "N")
  )

region_countries <- data |>
  pull(country_name) |>
  unique()

family_order <- read.csv(
  here(
    "regional_profile/data/family_order.csv"
  )
)|> 
  arrange(-family_order) |>
  mutate(
    family_name = ifelse(
      family_name == "Public Financial Management Institutions", 
      "Public Finance Institutions",
      family_name
    )
  ) |>
  pull(family_name)

if(length(region_countries) < 25){flag_size <- 9}
if(length(region_countries) >= 25 & length(region_countries < 30)){flag_size <- 7}
if(length(region_countries) >= 30 & length(region_countries < 35)){flag_size <- 6.5}
if(length(region_countries) >= 35 & length(region_countries < 50)){flag_size <- 6}
if(length(region_countries) >= 50){flag_size <- 4.75}

point_size <- flag_size * 1.1
status_size <- flag_size * 1.5

plot_theme <- theme(
    text = element_text(color = id_colors$primary, family = 'Roboto Condensed'),
    plot.title =  element_text(
      size = 18, 
      hjust = 0.5, 
      #face = 'bold', 
      margin = margin(t = 0, r = 0, b = 10, l = 0)
    ),
    plot.background = element_rect(fill = NA, colour=NA),
    
    panel.background = element_rect(fill = NA, colour=NA),
    panel.border = element_rect(fill=NA, colour = NA),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
     panel.spacing = unit(1, "lines"),
    
    legend.position="top",
    #legend.key = element_rect(fill = "white", colour = "black"),
    legend.text = element_text(size=14, hjust = 0.5),
    legend.title = element_text(size=14, margin = margin(t = 10, r = 0, b = 0, l = 0)),
    legend.background = element_rect(fill = NA),
    legend.box = "vertical",
    
    strip.background = element_rect(fill=NA),
    strip.text = element_text(size = 11, color = id_colors$primary),

    
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_blank()
  )

plot_country_theme <- theme(
    text = element_text(color = id_colors$primary, family = 'Roboto Condensed'),
    plot.title =  element_text(
      size = 18, 
      hjust = 0.5, 
      face = 'bold', 
      margin = margin(t = 0, r = 0, b = 0, l = 0)
    ),
    plot.background = element_rect(fill = NA, colour=NA),
    plot.margin = margin(t = 0, r = 0, b = 0, l = 0),
    
    panel.background = element_rect(fill = NA, colour=NA),
    panel.border = element_rect(fill=NA, colour = NA),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.spacing = unit(0, "lines"),
    
    legend.position="top",
    #legend.key = element_rect(fill = "white", colour = "black"),
    legend.text = element_text(size=20, hjust = 0.5),
    legend.title = element_text(size=20, margin = margin(t = 10, r = 0, b = 0, l = 0)),
    legend.background = element_rect(fill = NA),
    legend.box = "vertical",
    
    strip.background = element_rect(fill=NA),
    strip.text = element_text(size = ifelse(params$region=="Europe & Central Asia",12,14), color = id_colors$primary),
    #strip.text = element_blank(),
    
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_blank()
  )

fig_asp <- 1.25
fig_width <- 14

wrap_labeller <- function(variable, value) {
  return(str_wrap(as.character(value), width = 12))
}

```

\newpage

# Introduction

This regional profile for **`r params$region`** is based on the **CLIAR Dashboard data**. The group is composed of the following **`r paste(length(region_countries))` countries**:
  
```{r countries_flags, fig.cap=NULL, out.width = "100%", warning=F}

data_plot <- 
  data |> 
  distinct(country_name, ecb) |>
  arrange(country_name) |>
  mutate(
    rank = row_number(),   
    row = (rank - 1) %/% 7 + 1, 
    column = (rank - 1) %% 7 + 1 
  )

ggplot(data = data_plot) +
  scale_x_continuous(
    expand = c(0, 1)
  ) +
  scale_y_continuous(
    expand = c(0, 1)
  ) +
  labs(
    title = NULL,
    y = NULL,
    x = NULL,
    fill = NULL,
    shape = NULL
  ) +
  geom_point(
    aes(
      x = column,
      y = -row,  
    ),
    shape = 21,
    size = 7.5,
    fill = id_colors$primary,
    color = "transparent"
  ) +
  ggflags::geom_flag(
    aes(
      x = column,
      y = -row,  
      country = ecb
    ),
    size = 6.25
  ) +
  geom_text(
    aes(
      x = column,
      y = -row - 0.325,
      label = str_wrap(country_name, 22),
    ),
    size = 2.25,
    vjust = 1,
    hjust = 0.5,
    color = id_colors$primary,
    family = "Roboto Condensed"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    panel.grid = element_blank()
  )

```

```{r map_region, fig.cap="Featured countries of the group", fig.height = 3, warning=F}

countries_sf |>
  ggplot() +
  geom_sf(
    aes(
      fill = group_selected,
      color = group_selected
    ),
    stroke = 0.01
  ) +
  scale_fill_manual(
    values = c("grey85",id_colors$primary),
  ) +
  scale_color_manual(
    values = c("grey80","white")
  ) +
  labs(
    title = paste0(params$region, " countries"),
    fill = NULL,
    caption = paste0(
      str_wrap(
        "Disclaimer: Country borders or names do not necessarily reflect the World Bank Group's official position.
        This map is for illustrative purposes and does not imply the expression of any opinion on the part of the World Bank,
        concerning the legal status of any country or territory or concerning the delimitation of frontiers or boundaries.",
        175
      )
    )
  ) +
  theme(
    text = element_text(color = id_colors$primary, family = 'Roboto Condensed'),
    plot.title =  element_text(hjust = 0.5, face = 'bold', margin = margin(t = 0, r = 0, b = 5, l = 0)),
    plot.caption = element_text(size = 6.5, hjust = 0.5),
    plot.background = element_rect(fill = NA, colour=NA),
    
    panel.background = element_rect(fill = NA, colour=NA),
    panel.border = element_rect(fill=NA, colour = NA),
    panel.grid = element_blank(),
    
    legend.position="none",
    
    axis.ticks = element_blank(),
    axis.text = element_blank()
  )


```

\newpage

# About CLIAR

The **Country Level Institutional Assessment and Review (CLIAR)** is a methodological framework to make the Bank’s institutional diagnostic work and policy dialogue at the country level more integrated and data-driven. The aim of CLIAR’s institutional analysis is to support the World Bank’s policy dialogue with counterparts and help identify entry-points and priorities for institutional reform.

The **CLIAR Benchmarking** is a quick and accessible methodology that quantitatively assesses the strengths and weaknesses of a country’s institutional dimensions against a set of comparator countries. A set of curated institutional indicators are aggregated institutional clusters so to empirically map the institutional capital across substantive issue areas.

# Overview by Institutional Cluster

```{r countries_region, fig.cap="Group countries overview static CTF", fig.width = 12, fig.height=8, warning=F}

data_plot <- 
  data |>
  filter(base_country == country_name) |>
  group_by(var_name) |>
  mutate(
    rank = rank(-dtt, ties.method = "random")
  ) |>
  ungroup()

annotation_data <- data.frame(
  x = 2.25,
  xend = 1.3,
  y = -0.25,
  yend = 0.3
)

ggplot() +
  geom_vline(xintercept = 1, size = 2, color = "#8ec18e") +
  geom_vline(xintercept = max(data_plot$rank), size = 2, color = "#e47a81") +
  geom_point(
    data = data_plot,
    aes(
      y = factor(var_name, levels = family_order),
      x = rank,
      fill = factor(status, levels = status_order)
    ),
    shape = 21,
    size = status_size,
    color = "transparent"
  )  +
  geom_point(
    data = data_plot,
    aes(
      y = var_name,
      x = rank
    ),
    shape = 21,
    size = point_size,
    color = id_colors$primary
  )  +
  scale_fill_manual(
    values = colors
  ) +
  scale_y_discrete(
    labels = function(x) str_wrap(x, width = 30)
  ) +
  scale_x_continuous(
    limits = c(1,max(data_plot$rank)),
    breaks = seq(1, max(data_plot$rank), by = 4), 
    expand = c(0,1)
  ) +
  labs(
    title = NULL,
    y = NULL,
    x = "Performance ranking in comparison",
    fill = NULL,
    shape = NULL
  ) +
  ggflags::geom_flag(
    data = data_plot,
    aes(
      y = var_name,
      x = rank,
      country = ecb
    ),
    size = flag_size
  ) +
  geom_curve(
    data = annotation_data,
    aes(x = x, y = y, xend = xend, yend = yend),
    curvature = -.2, 
    arrow = arrow(length = unit(1.5, "mm")),
    color = id_colors$primary
  ) +
  geom_text(
    data = annotation_data,
    aes(x = x + 0.1, y = y),
    hjust = "left",
    label = str_wrap("Countries with the best performance when compared to the group",35),
    size = 4.5,
    family = "Roboto Condensed",
    color = id_colors$primary
  ) +
  coord_cartesian(clip = "off") +
  theme(
    text = element_text(color = id_colors$primary, family = 'Roboto Condensed'),
    plot.title =  element_text(size = 16, hjust = 0.5, face = 'bold', margin = margin(t = 5, r = 0, b = 5, l = 0)),
    plot.caption = element_text(size = 6.5, hjust = 0),
    plot.caption.position =  "plot",
    plot.background = element_rect(fill = NA, colour=NA),
    
    panel.background = element_rect(fill = NA, colour=NA),
    panel.border = element_rect(fill=NA, colour = NA),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    
    legend.position="top",
    legend.key.size = unit(0.5,"line"),
    legend.text = element_text(size=16, hjust = 0.5),
    legend.title = element_text(size=16, margin = margin(t = 0, r = 0, b = 0, l = 0)),
    legend.background = element_rect(fill = NA),
    
    strip.background = element_rect(fill=NA),
    strip.text = element_text(size = 10),
    
    axis.ticks = element_blank(),
    axis.title.x = element_text(size = 18, face = "bold", margin = margin(t = 10, r = 0, b = 5, l = 0)),
    axis.text.y = element_text(size = 14, color = id_colors$primary),
    axis.text.x = element_text(size = 12, color = id_colors$primary, margin = margin(t = 20, r = 0, b = 5, l = 0)),
    legend.box = "vertical"
  )

```

# Institutional Clusters

## Political Institutions

```{r political_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Political Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 12, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

## Social Institutions

```{r social_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Social Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

wrap_labeller <- function(variable, value) {
  return(str_wrap(as.character(value), width = 12))
}

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 10, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 11, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(2, 3.5))

```

## Absence of Corruption

```{r corruption, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Absence of Corruption"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

wrap_labeller <- function(variable, value) {
  return(str_wrap(as.character(value), width = 12))
}

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 20, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

## Transparency and Accountability Institutions

```{r transp_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Transparency and Accountability Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

## Justice Institutions

```{r just_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Justice Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 10, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(2, 3))

```

```{r just_violin, fig.cap="Justice Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Justice Institutions"

#violin_plot(data_clusters, family, params$region)

```

## Public Finance Institutions

```{r finan_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Public Finance Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 9, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1, 1))

```


```{r finance_violin, fig.cap="Public Finance Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Public Finance Institutions"

#violin_plot(data_clusters, family, params$region)

```

## Public Human Resource Management Institutions

```{r human_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Public Human Resource Management Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 15, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```


```{r human_violin, fig.cap="Public Human Resource Management Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Public Human Resource Management Institutions"

#violin_plot(data_clusters, family, params$region)

```

## Digital and Data Institutions

```{r digital_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Digital and Data Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 15, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

```{r digi_violin, fig.cap="Digital and Data Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Digital and Data Institutions"

#violin_plot(data_clusters, family, params$region)

```




















## Business Environment

```{r business_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Business Environment"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

```{r busi_violin, fig.cap="Business Environment static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Business Environment"

#violin_plot(data_clusters, family, params$region)

```

## SOE Corporate Governance

```{r soe_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "SOE Corporate Governance"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

if(nrow(data_plot)>0){

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 15, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

} else (paste0("No data available."))

```

```{r soe_violin, fig.cap="SOE Corporate Governance static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "SOE Corporate Governance"

#violin_plot(data_clusters, family, params$region)

```


## Labor and Social Protection Institutions

```{r labor_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Labor and Social Protection Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 15, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 13, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

```{r labor_violin, fig.cap="Labor and Social Protection Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Labor and Social Protection Institutions"

#violin_plot(data_clusters, family, params$region)

```


## Service Delivery Institutions

```{r service_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Service Delivery Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 12, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 11, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3.5))

```

```{r service_violin, fig.cap="Service Delivery Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Service Delivery Institutions"

#violin_plot(data_clusters, family, params$region)

```


## Climate Change and Environment Institutions

```{r climate_radar, fig.cap=NULL, fig.width=fig_width, fig.asp = fig_asp, fig.dpi=600, warning=F, fig.align = "center"}

family <- "Climate Change and Environment Institutions"

data_plot <- 
  data_clusters |>
  filter(comparison_group == params$region) |>
  filter(family_name == family) |>
  filter(base_country == country_name) #|>
  #filter(!grepl("Average", var_name))

#center_flag <- data |>
#  filter(country_name %in% data_plot$country_name) |>
#  select(
#    country_name, ecb
#  )|>
#  unique() |>
#  mutate(
#    var_name = NA,
#    dtf = 0,
#    status = NA,
#    x = 0,
#    y = 0
#  )

ind_order <- 
  data_plot |> 
  arrange(var_name) |> 
  pull(var_name) |> 
  unique()

average_elements <- ind_order[grep("Average", ind_order)]
other_elements <- ind_order[!grepl("Average", ind_order)]

ind_order <- c(average_elements, other_elements)

country_order_avg <- 
  data_plot |>
  filter(grepl("Average", var_name)) |>
  arrange(-dtf) |> 
  pull(country_name)

countries_no_avg <- 
  data_plot |>
  filter(!grepl("Average", var_name)) |>
  filter(!country_name %in% country_order_avg) |> 
  pull(country_name) |>
  unique()

country_order <- c(country_order_avg, countries_no_avg)

data_plot <- data_plot |> 
  mutate(country_name = factor(country_name, levels = country_order))

how_to_plot <- 
  ggplot(
    data = 
      data_plot |>
      select(var_name) |>
      unique() |>
      mutate(
        dtf = runif(n(), min = 0.8, max = 0.8),
        avg_color = ifelse(grepl("Average", var_name), "avg", "ind")
      ) 
  ) +
  geom_bar(
    aes(
      x = var_name,
      y = dtf,
      fill = avg_color
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    position = position_stack()
  ) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1.2),
    expand = c(0, 0),
    breaks = c(0.5)
  ) +
  scale_x_discrete(
    limits = ind_order,
    labels = function(x) str_wrap(x, width = 9, whitespace_only = F)
  ) +
  scale_fill_manual(values = c("avg" = "grey25", "ind" = "grey70")) + 
  guides(
    fill = F
  ) +
  labs(
    title = str_wrap("How to read: Each part represents an indicator. The size represents the CTF value and the color indicates the status compared to the group.", width = 40)
  ) +
  plot_theme +
  theme(
    plot.margin = margin(t = 0, r = 0, b = 0, l = 10),
    axis.text.x = element_text(size = 8, color = "black", vjust = 0.5),
    plot.title =  element_text(size = 16, hjust = 0, margin = margin(t = 0, r = 0, b = 50, l = 0))
  )

countries_plot <- 
  ggplot(
    data = data_plot
  ) +
  geom_bar(
    aes(
      x = factor(var_name, levels = ind_order),
      y = dtf,
      fill = factor(status, levels = status_order)
    ),
    stat = "identity", 
    color = "transparent", 
    size = 0,
    width = 0.85, 
    alpha = 1, 
    position = position_stack()
  ) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 6,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.5
  #) +
  #geom_point(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2
  #  ),
  #  size = 7,
  #  color = id_colors$primary,
  #  fill = "transparent",
  #  shape = 21,
  #  stroke = 1.25
  #) +
  #ggflags::geom_flag(
  #  data = center_flag,
  #  aes(
  #    x = ind_order[1], 
  #    y = -0.2, 
  #    country = ecb
  #  ),
  #  size = 6
  #) +
  coord_curvedpolar(clip = "off") +
  scale_y_continuous(
    limits = c(-0.2, 1),
    expand = c(0, 0),
    breaks = c(0.5)
  ) + 
  scale_fill_manual(
    na.translate = F,
    values = colors,
    name = NULL
  ) +
  scale_x_discrete(limits = ind_order) +
  facet_wrap(~country_name, ncol = 5, labeller = wrap_labeller) +
  labs(
    title = NULL
  ) +
  plot_country_theme

free(how_to_plot) + free(countries_plot) + plot_layout(widths = c(1.5, 3))

```


```{r climate_violin, fig.cap="Climate Change and Environment Institutions static CTF", fig.height=14, fig.width=16, fig.dpi=600, warning=F}

#family <- "Climate Change and Environment Institutions"

#violin_plot(data_clusters, family, params$region)

```

