---
editor_options: 
  markdown: 
    wrap: 72
---

# Data Sources update (optional)

-   Input: `data/input/**`
-   Output: `data/output/2024/clean-2024version-*.csv.gz`

READ ME (new data versions)

-   This script is considered "optional" because its primary purpose is
    to extract new data versions. Therefore, each chunk of this script
    is currently set to `eval=FALSE, include=FALSE` (not running).

-   To effectively execute this code and run the chunks, remove the
    `eval=FALSE, include=FALSE` tags from the chunk names.

-   Latest Data Version Update: September 5, 2024.

## Import Inputs

The data, initially imported manually, will be filtered (relevant
indicators only) and cleaned either calling .do files or in R. It uses
the 'RStata' package for initial cleaning of manually imported data,
streamlining the process and preparing key indicators. This step enables
automation for future data update. Once cleaned, standardized CSV files
will be exported to be further proceed.

```{r do-files-import, eval=FALSE, include=FALSE}

# Setting path based on the user
{
  
  user <- Sys.getenv("USERNAME")
  
  # NEED TO CHANGE THIS DIRECTORY
  if (user == "wb622595") { 
    print("Ileana has been selected")
    directory <- "C:/Users/wb622595/gitHub-repositories/institutional-assessment-dashboard/code"
  } else {
    stop("Unknown user. Please set the correct directory.")
  }
  
  # NEED TO CHANGE STATA (CHANGE DIRECTORY) 
  options("RStata.StataVersion" = 18.0)
  options("RStata.StataPath" = "/ProgramData/Microsoft/Windows/Start Menu/Programs/StataMP 18")
}

# Set working directories
{
  # Data directories
  input_data <- file.path(directory, "data/input")
  output_data <- file.path(directory, "data/output")
  
  # Stata do files to prepare inputs
  do_doc <- file.path(directory, "data/input/0.rtsata_inputs/")
}


# Clean the datasets bash 2024
{
# stata(file.path(do_doc, "clean-2024-heritage.do"))
# stata(file.path(do_doc, "clean-2024-wbl.do"))

}


```

```{r r_packages_import, eval=FALSE, include=FALSE}

wdi <- WDI(
  country = "all",
  indicator = c(
    # Existing indicators
    "GC.DOD.TOTL.GD.ZS", "EN.ATM.CO2E.PP.GD.KD", "BN.CAB.XOKA.GD.ZS",
    "SH.XPD.GHED.GD.ZS", "GC.XPN.TOTL.GD.ZS", "NE.EXP.GNFS.ZS",
    "NE.CON.TOTL.ZS", "BX.KLT.DINV.WD.GD.ZS", "BM.KLT.DINV.WD.GD.ZS",
    "NY.GDP.MKTP.KD", "NY.GDP.DEFL.ZS", "NY.GDP.DEFL.ZS.AD",
    "NY.GDP.MKTP.KD.ZG", "NY.GDP.PCAP.KD", "NY.GDP.PCAP.KD.ZG",
    "NY.GDP.PCAP.PP.KD", "NY.GDP.MKTP.PP.KD", "NE.CON.GOVT.ZS",
    "SE.XPD.TOTL.GD.ZS", "SE.XPD.PRIM.PC.ZS", "SE.XPD.SECO.PC.ZS",
    "SE.XPD.TERT.PC.ZS", "NE.GDI.TOTL.ZS", "NY.GDS.TOTL.ZS",
    "NE.GDI.FTOT.ZS", "NE.DAB.TOTL.ZS", "NY.GNS.ICTR.ZS",
    "NE.IMP.GNFS.ZS", "NY.GDP.DEFL.KD.ZG", "NY.GDP.DEFL.KD.ZG.AD",
    "NV.IND.MANF.ZS", "MS.MIL.XPND.GD.ZS", "NY.GDP.MINR.RT.ZS",
    "NY.GDP.NGAS.RT.ZS", "GC.NLD.TOTL.GD.ZS", "NY.GDP.PETR.RT.ZS",
    "BX.TRF.PWKR.DT.GD.ZS", "GC.REV.XGRT.GD.ZS", "NV.SRV.TOTL.ZS",
    "GC.TAX.TOTL.GD.ZS", "NY.GDP.TOTL.RT.ZS", "NE.TRD.GNFS.ZS",
    "NY.GNP.MKTP.KD", "DT.DOD.DECT.GN.ZS", "NY.GNP.MKTP.KD.ZG",
    "NY.GNP.PCAP.KD", "NY.GNP.PCAP.KD.ZG", "NY.GNP.PCAP.PP.KD",
    "NY.GNP.MKTP.PP.KD", "DT.ODA.ODAT.GN.ZS", "DC.ODA.TOTL.GN.ZS",
    "DT.TDS.DPPG.GN.ZS", "DT.TDS.DECT.GN.ZS", "DT.DOD.PVLX.GN.ZS",
    "DT.DOD.DSTC.ZS", "DT.DOD.DSTC.IR.ZS", "DT.TDS.DECT.EX.ZS",
    "FI.RES.TOTL.DT.ZS", "DT.DOD.DSTC.XP.ZS", "DT.TDS.MLAT.PG.ZS",
    "IQ.CPA.HRES.XQ", "IQ.CPA.BREG.XQ", "IQ.CPA.DEBT.XQ",
    "IQ.CPA.ECON.XQ", "IQ.CPA.REVN.XQ", "IQ.CPA.PRES.XQ",
    "IQ.CPA.FISP.XQ", "IQ.CPA.FINS.XQ", "IQ.CPA.GNDR.XQ",
    "IQ.CPA.MACR.XQ", "IQ.CPA.SOCI.XQ", "IQ.CPA.ENVR.XQ",
    "IQ.CPA.PROP.XQ", "IQ.CPA.PUBS.XQ", "IQ.CPA.FINQ.XQ",
    "IQ.CPA.PADM.XQ", "IQ.CPA.PROT.XQ", "IQ.CPA.STRC.XQ",
    "IQ.CPA.TRAD.XQ", "IQ.CPA.TRAN.XQ",
    # Updated code indicators according the Metadata Glossary 
    # https://databank.worldbank.org/metadataglossary/all/series
    # adjust db_bariables
    "SE.ADT.LITR.FE.ZS",  # Literacy rate, adult female
    "SE.ADT.LITR.MA.ZS",  # Literacy rate, adult male
    "SE.ADT.LITR.ZS",     # Literacy rate, adult total
    "SH.DYN.MORT",        # Mortality rate, under-5
    "SH.STA.ANVC.ZS",     # Pregnant women receiving prenatal care "SH.STA.PRSC.ZS"
    "SH.STA.MMRT",       # Maternal mortality ratio "SH.MMR.RATIO",
    "SH.DYN.MORT.FE",     # Mortality rate, adult female sp.dyn.amrt.fe
    "SH.DYN.MORT.MA",      # Mortality rate, adult male 
    "GC.REV.SOCL.ZS", "MS.MIL.TOTL.TF.ZS", "SL.UEM.TOTL.NE.ZS",
    "SL.UEM.TOTL.ZS", "SE.COM.DURS", "SE.XPD.CPRM.ZS",
    "SE.XPD.CSEC.ZS", "SE.XPD.CTER.ZS", "SE.XPD.CTOT.ZS",
    "SE.XPD.TOTL.GB.ZS", "SE.SEC.TCAQ.LO.ZS", "SE.PRE.TCAQ.ZS",
    "SE.PRM.TCAQ.ZS", "SE.SEC.TCAQ.ZS", "SE.SEC.TCAQ.UP.ZS",
    "SE.PRM.TENR", "SH.STA.BRTC.ZS", "SH.MED.CMHW.P3",
    "SH.XPD.CHEX.GD.ZS", "SH.XPD.OOPC.CH.ZS", "SH.XPD.OOPC.PP.CD",
    "SI.POV.MDIM", "SI.POV.MDIM.XQ", "SI.POV.GAPS",
    "SI.POV.LMIC.GP", "SI.POV.UMIC.GP", "SI.POV.DDAY",
    "SI.POV.LMIC", "SI.POV.UMIC", "SI.POV.NAHC",
    "SE.PRM.ENRL.TC.ZS", "SE.SEC.ENRL.TC.ZS", "SE.TER.ENRL.TC.ZS",
    "SH.MED.BEDS.ZS", "SH.MED.PHYS.ZS", "SP.REG.BRTH.ZS",
    "SP.REG.BRTH.RU.ZS", "SP.REG.BRTH.UR.ZS"
  ),
  start = 1990,
  end = 2023,
  extra = FALSE,
  cache = NULL,
  latest = NULL,
  language = "en"
)


vdem <- vdemdata::vdem 

```

## Clean Inputs

```{r eval=FALSE, include=FALSE}
wdi_clean <- wdi %>%
  clean_names() %>%
  rename(
    country_name = country,
    country_code = iso3c
  )

# Function to convert mixed ISO2 and ISO3 codes to ISO3
convert_to_iso3 <- function(codes) {
  # Convert ISO2 codes to ISO3
  iso3_from_iso2 <- countrycode(
    sourcevar = codes,
    origin = "iso2c",
    destination = "iso3c",
    warn = FALSE
  )
  
  iso3_from_iso3 <- countrycode(
    sourcevar = codes,
    origin = "iso3c",
    destination = "iso3c",
    warn = FALSE
  )
  
  # Return the ISO3 codes from either conversion
  iso3_from_iso2 %>% ifelse(is.na(.), iso3_from_iso3, .)
}

wdi_clean <- wdi_clean %>%
  mutate(
    country_code = convert_to_iso3(iso2c)
  ) %>% 
  select(-iso2c)

# # Check unmatched codes
# unmatched_codes <- wdi_clean$iso2c[is.na(wdi_clean$country_code)]
# print(unmatched_codes)

# Remove underscores from column names and replace prefixes with `wdi_` convention
wdi_clean <- wdi_clean|>
  rename_with(~ str_replace_all(.x, "_", ""), .cols = everything()) %>% 
  rename_with(~ str_replace_all(.x, "^(.+)", "wdi_\\1"), .cols = !starts_with("country") & !starts_with("year"))


vdem_clean <- vdem |>
  filter(year >= 1990) |>
  rename(
  country_code = country_text_id 
  ) |> 
  clean_names() |>  # Clean column names to lower case with underscores
  distinct(country_code, year, .keep_all = TRUE)|>  # Remove duplicates
  select(
    country_code,
    year,
    v2x_corr,
    v2exbribe,
    v2xcl_prpty,
    v2xcl_acjst,
    v2juhcind,
    v2juncind,
    v2juaccnt,
    v2pepwrgen,
    v2pepwrsoc,
    v2pepwrses,
    v2xlg_legcon,
    v2x_gender,
    v2stcritrecadm,
    v2clrspct,
    v2cseeorgs,
    v2dlengage,
    v2clacfree,
    v2csreprss,
    v2x_civlib,
    v2x_cspart,
    v2clstown, ### Former name v2cl_acjst State ownership of economy
    v2clacjstm,
    v2clacjstw,
    v2lgqugen,
    v2lgfemleg,
    v2cldiscm,
    v2cldiscw,
    v2caassemb,
    v2cacamps,
    v2peapsecon,
    v2peasjsoecon,
    v2peapsgen,
    v2peasjgen,
    v2peapspol,
    v2peasjpol,
    v2x_pubcorr,
    v2x_execorr,
    v2lgcrrpt,
    v2dlencmps,
    v2clstown,
    v2peedueq,
    v2pehealth,
    v2peasbepol,
    v2cafres,
    v2cafexch,
    v2x_rule,
    v2xed_ed_cent,
    v2xed_ed_ctag,
    v2xed_ed_con,
    v2edteautonomy,
    v2edteunionindp
  ) |>
 rename_with(
    # replace prefixses with efi conventions
    ~ paste0("vdem_core_", .), 
    .cols = starts_with("v2")
  )

```

## Export Inputs

```{r eval=FALSE, include=FALSE}
write_dta(
  vdem_clean,
  here(
    "data",
    "input",
    "vdem",
    "2024",
    "vdem_19902023.dta"
  )
)


write_dta(
  wdi_clean,
  here(
    "data",
    "input",
    "wdi",
    "2024",
    "wdi_19902023.dta"
  )
)

```
