# Process data

- Input: `data/input/**/*.csv`
- Output: `data/output/cliar_compiled_indicators.rds`

This script generates the consolidated indicators for the CLIAR dashboard. It imports, processes and consolidates a diverse range of datasets, including from EFI360 and others. An exhaustive list of datasets is provided below:

```{r set-up, include = FALSE}
# define list of variables
source(
  here("vars-control.R")
)

# aux. funs
source(
  here("funs.R")
)

ref_year <- 2023
```

## 1. Import data

The data was imported from (a) the EFI360 shared data and (b) manual imports.

```{r read_in}
efi <- read_dta(
  here("data", "input", "efi", "EFI360_CLIAR_1990-2022.dta")
)

romelli <- read_dta(
  here("data", "input", "romelli", "CBIData_Romelli2022.dta")
) |>
  clean_names()

debt_transparency <- read_dta(
  here("data", "input", "debt_transparency", "debt_transparency_2021-2022.dta")
)

fraser <- read_csv(
  here("data", "input", "fraser", "fraser.csv")
) |>
  clean_names()

gfdb <- read_dta(
  here("data", "input", "gfdb", "GFDB_19902021.dta")
)

oecd_epl_regular <- read_csv(
  here("data", "input", "oecd", "epl_regular.csv")
)

oecd_epl_temporary <- read_csv(
  here("data", "input", "oecd", "epl_temporary.csv")
)

oecd_pmr <- read_dta(
  here("data", "input", "pmr", "PMR_2018.dta")
)

spi <- read_csv(
  here("data", "input", "spi", "spi_index.csv")
) |> 
  clean_names()

aspire <- read_dta(
  here("data", "input", "aspire", "ASPIRE performance indicators.dta")
)

rise <- read_dta(
  here("data", "input", "rise", "RISE_20102021.dta")
)

wdi <- read_dta(
  here("data", "input", "wdi", "WDI_19902022_CLIAR.dta")
)

vdem <- read_dta(
  here("data", "input", "vdem", "VDEM_1990_2022.dta")
)

heritage <- read_dta(
  here("data", "input", "heritage", "heritage20122022.dta")
)

open_budget <- list.files(
    here("data", "input", "ibp"),
    full.names = TRUE
  ) |> 
    map_dfr(
      read_csv,
      col_select = c(ISO, year, obi)
    )

wb_country_list <- read_xlsx(
  here(
   "data",
    "input",
    "wb",
    "CLASS.xlsx"
    ),
    sheet = "Groups"
  ) %>%
  transmute(
    country_code = CountryCode,
    country_name = CountryName,
    group = GroupName,
    group_code = GroupCode
  )

wbl <- read_dta(
  here("data", "input", "wbl", "WBL_19902022_CLIAR.dta")
)

# note that North America is not included in this list
wb_regions <- c(
  "Africa Eastern and Southern",
  "Africa Western and Central",
  "East Asia & Pacific",
  "Europe & Central Asia",
  "Latin America & Caribbean",
  "Middle East & North Africa",
  "South Asia"
)

country_region_list <- wb_country_list |> 
  # this filter excludes Canada, Bermuda and USA
  filter(group %in% wb_regions) |> 
  select(country_code, region = group)
```

## 2. Process data
```{r clean_data}
# in this section, we take the EFI files, plus the manual import data,
# to process them.
# 1. efi
efi_clean <- efi |> 
  clean_names() |> 
  # fix enterprise surveys variable name
  rename_with(
    \(x) str_replace(x, "wb_survey", "wb_es_ic_frm"),
    .cols = starts_with("wb_survey")
  ) |> 
  # create PFM MIS indicator by summing over the following and rescaling:
  # GTMI_I-13       Is there a Debt Management System (DMS) in place? (foreign and domestic debt)
  # GTMI_I-14       Is there a Public Investment Management System (PIMS) in place?
  # GTMI_I-7         Is there a Tax Management Information System in place?
  # GTMI_I-6         Is there a TSA supported by FMIS to automate payments and bank reconciliation?
  # GTMI_I-5         Is there an operational FMIS in place to support core PFM functions?
  rowwise() |> 
  mutate(
    wb_gtmi_pfm_mis = sum(
      wb_gtmi_i_13,
      wb_gtmi_i_14,
      wb_gtmi_i_7,
      wb_gtmi_i_6,
      wb_gtmi_i_5
    )
  ) |> 
  ungroup() |> 
  mutate(
    wb_gtmi_pfm_mis = scale_values(wb_gtmi_pfm_mis)
  ) |> 
  select(
    -index,
    -country_name,
    country_code = iso3,
    year,
    everything()
  )

# 2. fraser - market regulations
fraser_clean <- fraser |>
  transmute(
    country_code = iso_code_3,
    year = as.numeric(year),
    x4diii_freedom_of_foreigners_to_visit,
    x4dii_capital_controls,
    x5a_credit_market_regulations,
    x3d_freedom_to_own_foreign_currency_bank_accounts,
    x2b_impartial_courts,
    x2e_integrity_of_the_legal_system,
    x2a_judicial_independence,
    x2f_legal_enforcement_of_contracts
  ) |>
  rename_with(
    # replace prefixes with efi conventions
    ~ str_replace(., "^x[:alnum:]+_", "fraser_efw_")
  )

# 3. romelli - central bank independence
romelli_clean <- romelli |>
  transmute(
    country_code = wb_a3,
    year = as.numeric(year),
    romelli_cbi_central_bank_independence = lvau
  )

# 4. oecd - employment protection laws
oecd_epl_regular_clean <- oecd_epl_regular |>
  filter(
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    # the country code used by the OECD is equivalent to the WB
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_regular = Value
  )

oecd_epl_temporary_clean <- oecd_epl_temporary |>
  filter(
    # Series == "Version 1 (1985-2019)"
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_temporary = Value
  )

# note that there is higher coverage for regular vs. temporary contracts
oecd_epl_clean <- oecd_epl_regular_clean |>
  full_join(
    oecd_epl_temporary_clean
  )

# 5. spi - statistical performance indicators
# SPI.DIM4.1.CEN.INDEX	SPI.DIM4.1.SVY.INDEX Dimension 5.2: Standards and Methods
# SPI.DIM5.2.INDEX
spi_clean <- spi |> 
  rowwise() |> 
  # generate an average index of the census and survey indexes
  mutate(
    spi_census_and_survey_index = mean(
      c(spi_dim4_1_cen_index, spi_dim4_1_svy_index),
      na.rm = TRUE
    )
  ) |> 
  ungroup() |> 
  transmute(
    country_code = iso3c,
    year = as.numeric(date),
    spi_census_and_survey_index,
    spi_std_and_methods = spi_dim5_2_index # standards and methods
  )

# 6. aspire data
aspire_clean <- aspire |> 
  filter(
    indicator_name %in% c(
      "Adequacy of benefits (%) -All Social Protection and Labor",
      "Coverage (%) -All Social Protection and Labor"
    )
  ) |> 
  transmute(
    # identify non-country codes (aspire includes regions, for example)
    country_code = countrycode(
      Country_Code, 
      origin = "iso3c", destination = "iso3c",
      # create exception for kosovo
      custom_match = c("XKX" = "XKX")
    ),
    year = as.numeric(Year),
    Indicator_Code,
    value = val_w
  ) |> 
  filter(
    # exclude non-country codes
    !is.na(country_code)
  ) |> 
  pivot_wider(
    id_cols = c(country_code, year),
    values_from = value,
    names_from = Indicator_Code
  ) |> 
  rename(
    wb_aspire_coverage = per_allsp.cov_pop_tot,
    wb_aspire_adequacy_benefits = per_allsp.adq_pop_tot
  )

# 7. rise data
rise_clean <- rise |> 
  clean_names()

# 8. wdi data
wdi_clean <- wdi |> 
  clean_names()

# 9. vdem
vdem_clean <- vdem |> 
  clean_names()

# 10. heritage
heritage_clean <- heritage |> 
  clean_names()

# 11. OECD Product Market Regulation
oecd_pmr_clean <- oecd_pmr |> 
  select(
    country_code,
    year,
    PMR_2018_3_3,
    PMR_2018_1_3,
    PMR_2018_6,
    PMR_2018_1_4,
    PMR_2018_1_2,
    PMR_2018_2_1,
    PMR_2018_1_1,
    PMR_2018_2_2
  ) |>
  clean_names() |> 
  rename_with(
    # replace prefixes with efi conventions
    ~ paste0("oecd_", .),
    .cols = starts_with("pmr")
  )

# 12. Open Budget Survey
open_budget_clean <- open_budget |> 
  select(
    country_code = ISO,
    year,
    ibp_obs_obi = obi
  ) |> 
  # fix cambodia ISO3
  mutate(
    country_code = if_else(
      country_code == "KMH",
      "KHM",
      country_code
    )
  )

# 13. Debt Transparency
debt_transparency_clean <- debt_transparency |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("debt")
  )

# 14. GFDB Bank Concentration
gfdb_clean <- gfdb |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("gfdb")
  )

# 15. Women, Business and the Law
wbl_clean <- wbl |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("wbl")
  )
```

## Consolidate data
```{r consolidate_data}
excluded_country_code <- c(
  "AIA", # anguilla
  "OECD", # OECD
  "SML", # somaliland
  "ZZB", # zanzibar,
  "KMH" # unclear, listed in Open Budget Survey
)

cliar_indicators <- list(
  efi_clean,
  fraser_clean,
  romelli_clean,
  oecd_epl_clean,
  spi_clean,
  aspire_clean,
  rise_clean,
  wdi_clean,
  vdem_clean,
  heritage_clean,
  oecd_pmr_clean,
  open_budget_clean,
  debt_transparency_clean,
  gfdb_clean,
  wbl_clean
) |> 
  map(
    # fix country codes for full join
    ~ mutate(
        .,
        country_code = case_when(
          country_code == "ZAR" ~ "COD", # democratic republic of congo
          country_code == "ROM" ~ "ROU", # romania
          T ~ country_code
        )
      ) |> 
      filter(
        !(country_code %in% excluded_country_code)
      )
  ) |> 
  reduce(
    full_join,
    by = c("country_code", "year")
  ) |> 
  filter(
    year >= 1990
  )
  
# order column names
cliar_indicators <- cliar_indicators %>%
  select(
    country_code,
    year,
    sort(colnames(.)),
    -starts_with("country_name")
  ) |> 
  arrange(
    country_code,
    year
  ) |> 
  mutate(
    index = row_number()
  )
```

## Compute family averages

```{r}
# compute family averages
cliar_indicators_long <-
  cliar_indicators %>%
  pivot_longer(
    any_of(vars_all),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  )

# only calculate family averages for relevant institutional clusters
cliar_family_level_long <- cliar_indicators_long |>
  filter(
    family_var %in% vars_family
  ) |>
  group_by(
    country_code, year, family_var
  ) |>
  summarise(
    value = mean(value, na.rm = TRUE),
    .groups = "drop"
  )

cliar_family_level <- cliar_family_level_long |>
  pivot_wider(
    id_cols = c(country_code, year),
    names_from = family_var,
    names_glue = "{family_var}_avg",
    values_from = value
  )

cliar_indicators <- cliar_indicators |>
  left_join(
    cliar_family_level,
    by = c("country_code", "year")
  )
```

## Data Quality Control: Indicator Selection

```{r indicator_selection}
# verify that the indicators are selected correctly
db_variables_indicators <- db_variables |> 
  select(
    variable
  )

# only retain indicators contained in metadata + id cols
cliar_indicators_clean <- cliar_indicators |> 
  # add country names
  left_join(
    wb_country_list |> 
      distinct(country_code, country_name),
    by = "country_code"
  ) |> 
  select(
    country_code,
    country_name,
    year,
    all_of(db_variables_indicators |> pull(variable))
  )

cliar_indicators_id <- cliar_indicators_clean |> 
  colnames() %>% 
  tibble(
    variable = .
  )

test_that(
  "All indicators contained in metadata are in the CLIAR dataset",{
    expect_equal(
      nrow(
        db_variables_indicators |> 
          anti_join(cliar_indicators_id, by = "variable") |> 
          as.data.frame()
        ),
      0
    )
  }
)
```

## Data Quality Control: verify country_code, country_name consistency and completeness of country-year combinations
```{r country_validation}
# there are 218 country codes listed in the WB's official website
# https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups
# a. verify that all the country codes from the official data are included
test_that(
  "Verify that all the country codes from the official data are included",
  expect_equal(
    # number of rows is zero
    cliar_indicators |> 
      distinct(country_code) |> 
        anti_join(
          wb_country_list |> 
            distinct(country_code, country_name),
          by = c("country_code")
        ) |> nrow(),
      0
  )
)

# b. verify that cliar has distinct country-year
test_that(
  "Verify that CLIAR has distinct country years",{
    expect_equal(
      nrow(cliar_indicators),
      cliar_indicators |> 
        distinct(country_code, year) |> 
        nrow()
    )
  }
)

# c. verify that all countries have complete year coverage
test_that(
  "Verify that country codes have coverage for all years",{
    expect_equal(
      # calculate number of years covered by country
      cliar_indicators |> 
        count(country_code) |> 
        pull(n) |> 
        unique(),
      ref_year - 1990
    )
  }
)
```

# 6. Compute coverage diagnostics
```{r coverage_diagnostics}
cliar_indicators_diagnostic <- cliar_indicators_clean |>
  select(-country_name) |> 
  compute_coverage(country_code, year, ref_year - 5) |> 
  left_join(
    db_variables |> select(variable, var_name, source, family_name),
    by = c("Indicator" = "variable")
  ) |> 
  select(
    `Indicator`,
    `Indicator Name` = var_name,
    `Institutional Family` = family_name,
    everything(),
    `Data Source` = source
  ) |> 
  arrange(
    `Institutional Family`,
    Indicator
  )
```

## 7. Save data

```{r}
write_rds(
  cliar_indicators_clean,
  here(
    "data",
    "output",
    "compiled_indicators.rds"
  )
)

cliar_indicators_diagnostic |> 
    write_csv(
      here(
        "data",
        "output",
        "diagnostics_compiled_indicators.rds"
      )
    )
```
