# Clean list of contries

This file creates a clean list of countries to be used calculating CTF.
In order to clean the list of countries, only countries with data are kept,
duplicate group names are removed, and column names are standardized

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/input/wb/CLASS.xlsx`, obtained from https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups on September 1, 2022
  - `data/input/wb/group_list.csv`, input by the research team to list relevant groups
      
- Outputs:
  - `data/final/wb_country_list.rds`
  - `data/final/wb_country_groups.rds`


## Inputs

Read in a list of compiled indicators, which includes all of the indicator values
for each country year.

Read in a list of all of the country groups being used, these groups can be
regional, income based, or economic.

Read in a country list, which includes countries, their country codes, the region
they are in and the group code. Clean this list to have standardized column names

```{r}
  indicators <-
    read_rds(
      here(
        "data",
        "output",
        "compiled_indicators.rds"
      )
    )

  group_list <-
    read_csv(
      here(
        "data",
        "input",
        "wb",
        "group_list.csv"
      )
    )

  country_list <-
    read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "Groups"
    ) %>%
    transmute(
      country_code = CountryCode,
      country_name = CountryName,
      group = GroupName,
      group_code = GroupCode
    )
```

## Subset country list

Take the country list that was loaded in the last section and select only 
countries that we have data for. 

```{r}
country_list <-
  indicators %>%
  select(country_code) %>%
  unique %>%
  left_join(country_list)
```

## Subset groups

Filter out any duplicate groups from the country list file

```{r}
country_list <-
  country_list %>%
  filter(
    group %in% group_list$group_name
  ) %>%
  unique
```

## Save datasets

Dataset with list of countries in our sample

```{r}
write_rds(
  country_list,
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

write_rds(
  group_list,
  here(
    "data",
    "output",
    "wb_country_groups.rds"
  )
)
```
