# Process data

- Input: `data/input/**/*.csv`
- Output: `data/output/cliar_compiled_indicators.rds`

This script generates the consolidated indicators for the CLIAR dashboard. It imports, processes and consolidates a diverse range of datasets, including from EFI360 and others. An exhaustive list of datasets is provided below:

```{r set-up, include = FALSE}
# define list of variables
source(
  here("vars-control.R")
)

# Load in the funs.R file which contains many of the specialized functions
# used in this process.
source(
  here("funs.R")
)

#ref_year <- 2024
#Data final year + 1
ref_year <- 2025
```

## Import data

The data was imported from (a) the EFI360 shared data and (b) manual imports.
This section first reads in each of the individual manual-input files (Note that the updated version count with '2024' as folder and the column id names are cleaned with the clean_names() function. After this is done, a list of of standardized WB country names and codes is read in and mutated to be better compatible with the CLIAR data

```{r read in}
efi <- read_dta(
  here("data", "input", "efi", "Update_EFI360_1990_2024.dta")
)

romelli <- read_dta(
  here("data", "input", "romelli", "CBIData_Romelli2022.dta")
) |>
  clean_names()

debt_transparency <- read_dta(
  here("data", "input", "debt_transparency", "debt_transparency_2021-2022.dta")
)

fraser <- read_xlsx(
  here("data", "input", "fraser", "2024", "efotw-2023-master-index-data-for-researchers-iso.xlsx")
) |> 
  clean_names() |> 
  slice(-c(1:2)) 

  
gfdb <- read_dta(
  here("data", "input", "gfdb", "GFDB_19902021.dta")
)

oecd_epl_regular <- read_csv(
  here("data", "input", "oecd", "epl_regular.csv")
)

oecd_epl_temporary <- read_csv(
  here("data", "input", "oecd", "epl_temporary.csv")
)

oecd_pmr <- read_dta(
  here("data", "input", "pmr", "PMR_2018.dta")
)

spi <- read_csv(
  here("data", "input", "spi", "2024", "SPI_index_labelled.csv")
) |> 
  clean_names() 

aspire <- read_dta(
  #Testing new ASPIRE pulled from Pros360 API
  here("data", "input", "aspire", "API_ASPIRE.dta")
  #VV Original Dataset
  #here("data", "input", "aspire", "ASPIRE performance indicators.dta")
)

rise <- read_dta(
  here("data", "input", "rise", "RISE_20102021.dta")
)


wdi <- read_dta(
  here("data", "input", "wdi", "2024", "wdi_19902023.dta")
)

vdem <- read_dta(
  here("data", "input", "vdem", "2024", "vdem_19902023.dta")
)


heritage <- read_dta(
  here("data", "input", "heritage", "2024", "heritage20122024.dta")
)

open_budget <- list.files(
    here("data", "input", "ibp"),
    full.names = TRUE
  ) |> 
    map_dfr(
      read_csv,
      col_select = c(ISO, year, obi)
    )

# read in world bank standard country codes and mutate them to be compatible
# with the other files
wb_country_list <- read_xlsx(
  here(
   "data",
    "input",
    "wb",
    "CLASS.xlsx"
    ),
    sheet = "Groups"
  ) %>%
  transmute(
    country_code = CountryCode,
    country_name = CountryName,
    group = GroupName,
    group_code = GroupCode
  ) |> 
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )

# country income group and region
country_income_and_region <- read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "List of economies",
      n_max = 219
    ) %>%
    transmute(
      country_code = Code,
      region = Region,
      income_group = `Income group`
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )

wblx <- read_dta(
  here("data", "input", "wbl", "WBL_19902022_CLIAR.dta")
)

wbl <- read_dta(
  here("data", "input", "wbl", "WBL_19902023_CLIAR.dta")
)

# note that North America is not included in this list
wb_regions <- c(
  "Africa Eastern and Southern",
  "Africa Western and Central",
  "East Asia & Pacific",
  "Europe & Central Asia",
  "Latin America & Caribbean",
  "Middle East & North Africa",
  "South Asia"
)

country_region_list <- wb_country_list |> 
  # this filter excludes Canada, Bermuda and USA
  filter(group %in% wb_regions) |> 
  select(country_code, region = group)
```

## Process data

In this section, we take the EFI files, plus the manual import data, and clean them. In order to ensure clean column names and accurate variables, certain datasets are edited to create new variables or to change other factors. More detail given in each subsection.

```{r clean_data}
# 1. efi
#       For the EFI, first the name of enterprise survey variables is changed to 
#       be more consistent. Then a single PFM indicator is by taking the sum of
#       several GTMI variables. 
efi_clean <- efi |> 
  clean_names() |> 
  # fix enterprise surveys variable name
  rename_with(
    \(x) str_replace(x, "wb_survey", "wb_es_ic_frm"),
    .cols = starts_with("wb_survey")
  ) |> 
  # create PFM MIS indicator by summing over the following and rescaling:
  # GTMI_I-12       Is there an e-Procurement System in place? (foreign and domestic debt)
  # GTMI_I-13       Is there a Debt Management System (DMS) in place? (foreign and domestic debt)
  # GTMI_I-14       Is there a Public Investment Management System (PIMS) in place?
  # GTMI_I-8        Is there a Customs System in place?
  # GTMI_I-7        Is there a Tax Management Information System in place?
  # GTMI_I-6        Is there a TSA supported by FMIS to automate payments and bank reconciliation?
  # GTMI_I-5        Is there an operational FMIS in place to support core PFM functions?
  rowwise() |> 
  mutate(
    wb_gtmi_pfm_mis = sum(
      # wb_gtmi_i_12,
      wb_gtmi_i_13,
      wb_gtmi_i_14,
      wb_gtmi_i_8,
      wb_gtmi_i_7,
      wb_gtmi_i_6,
      wb_gtmi_i_5
    )
  ) |> 
  ungroup() |> 
  mutate(
    wb_gtmi_pfm_mis = scale_values(wb_gtmi_pfm_mis)
  ) |> 
  # edit WJP indicators to: (1) use 2018 data for 2017 in WJP and drop data if year < 2015
  arrange(
    iso3, year
  ) |> 
  mutate(
    across(
      starts_with("wjp_rol"),
      ~ case_when(
        year == 2017 ~ lead(.), # use 2018 data for 2017
        year < 2015 ~ NA, # drop data if year < 2015
        T ~ .
      )
    )
  ) |> 
  select(
    country_code = iso3,
    year,
    everything()
  ) |> 
  select(
    -index,
    -country_name
  )

# 2. fraser - market regulations
      # For the fraser data, the clean dataset is created by selecting only the
      # necessary columns, standardizing the country code variable name, casting
      # the year variable to numeric, and changing variable prefixes to be
      # in line with EFI conventions

      # NOTE 2024:
      # Change variable names https://www.fraserinstitute.org/economic-freedom/approach
fraser <- fraser |> 
  slice(-1) |> 
  setNames(as.character(fraser[1, ])) 

fraser_clean <- fraser |> 
  clean_names() 

# Define the columns to convert to double type
double_columns <- c(
  "year",
  "x5a_credit_market_regulation",
  "x3d_foreign_currency_bank_accounts",
  "x4diii_freedom_of_foreigners_to_visit", 
  "x4dii_capital_controls",
  "x2b_impartial_courts",
  "x2e_legal_integrity",
  "x2a_judicial_independence",
  "x2f_contracts"
)

fraser_clean <- fraser_clean %>% 
  transmute(
    country_code = iso_code_3,
    across(all_of(double_columns), as.double)
  ) |> 
  rename_with(
    ~ str_replace(., "^x[:alnum:]+_", "fraser_efw_")
  )

###
### After using the new fraser file, 4 indicators would need renaming in db_var
### at the time of transforming the variables, Batlesman Institute seems to be the official source
###


  

# 3. romelli - central bank independence
#       The romelli data is cleaned by setting the country code variable name
#       and casting the year variable to numeric
romelli_clean <- romelli |>
  transmute(
    country_code = wb_a3,
    year = as.numeric(year),
    romelli_cbi_central_bank_independence = lvau
  )

# 4. oecd - employment protection laws
#       To clean this data, first the necessary data is taken from both the 
#       regular and temporary employees datasets, as well as standardizing
#       country code and making the year variable numeric. Then these two 
#       categories are merged together.
oecd_epl_regular_clean <- oecd_epl_regular |>
  filter(
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    # the country code used by the OECD is equivalent to the WB
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_regular = Value
  )

oecd_epl_temporary_clean <- oecd_epl_temporary |>
  filter(
    # Series == "Version 1 (1985-2019)"
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_temporary = Value
  )

# note that there is higher coverage for regular vs. temporary contracts
oecd_epl_clean <- oecd_epl_regular_clean |>
  full_join(
    oecd_epl_temporary_clean
  )

# 5. spi - statistical performance indicators
#       First  generate an average index of the census and survey indexes, and
#       then perform the standard cleanings of changing the country code column
#       name and casting the year as numeric

# SPI.DIM4.1.CEN.INDEX	SPI.DIM4.1.SVY.INDEX Dimension 5.2: Standards and Methods
# SPI.DIM5.2.INDEX
spi_clean <- spi %>%
slice(-1)|> 
  mutate(
    spi_dim4_1_cen_index = as.numeric(spi_dim4_1_cen_index),
    spi_dim4_1_svy_index = as.numeric(spi_dim4_1_svy_index),
    spi_dim5_2_index = as.numeric(spi_dim5_2_index),
    date = as.numeric(date) # Relevant cols as numeric
  ) |> 
  rowwise() |> 
  # generate an average index of the census and survey indexes
  mutate(
    spi_census_and_survey_index = mean(
      c(spi_dim4_1_cen_index, spi_dim4_1_svy_index),
      na.rm = TRUE
    )
  ) |> 
  ungroup() |> 
  transmute(
    country_code = iso3c,
    year = as.numeric(date),
    spi_census_and_survey_index,
    spi_std_and_methods = spi_dim5_2_index # standards and methods
  )

# 6. aspire data
#       Filter for the correct indicators, standardize name for country codes 
#       remove non-country codes, and change shape of the data. 
aspire_clean <- aspire |> 
  filter(
    indicator_name %in% c(
      "Adequacy of benefits (%) -All Social Protection and Labor",
      "Coverage (%) -All Social Protection and Labor"
    )
  ) |> 
  transmute(
    # identify non-country codes (aspire includes regions, for example)
    country_code = countrycode(
      Country_Code, 
      origin = "iso3c", destination = "iso3c",
      # create exception for kosovo
      custom_match = c("XKX" = "XKX")
    ),
    year = as.numeric(Year),
    Indicator_Code,
    value = val
  ) |> 
  filter(
    # exclude non-country codes
    !is.na(country_code)
  ) |> 
  pivot_wider(
    id_cols = c(country_code, year),
    values_from = value,
    names_from = Indicator_Code
  ) |> 
  rename(
    wb_aspire_coverage = per_allsp.cov_pop_tot,
    wb_aspire_adequacy_benefits = per_allsp.adq_pop_tot
  )


# 7. rise data
rise_clean <- rise |> 
  clean_names()

# 8. wdi data
wdi_clean <- wdi |>
  rename(
    country_name = countryname,
    country_code = countrycode
  ) |>
  rename_with(
    ~ str_to_lower(.) %>% 
      str_replace_all("^wdi_", "wdi_"), 
      starts_with("wdi_")
  )

columns_to_drop <- c(
  "country_name",
  "wdi_dcodatotlgnzs", 
  "wdi_dtdodpvlxgnzs", 
  "wdi_shmedcmhwp3",  
  "wdi_sipovmdim",     
  "wdi_sipovmdimxq"  
)  
  
wdi_clean <- wdi_clean |>
  select(!all_of(columns_to_drop)) |>
  # rename(
  #   wdi_spdynamrtfe = wdi_shdynmortfe,
  #   wdi_spdynamrtma = wdi_shdynmortma
  # ) |>
  filter(!is.na(country_code) & country_code != ""
  ) |>
  distinct(country_code, year, .keep_all = TRUE)


# 9. vdem
vdem_clean <- vdem 

# 10. heritage
heritage_clean <- heritage |> 
  clean_names() |>
  filter(!is.na(country_code) & country_code != "")

# 11. OECD Product Market Regulation
oecd_pmr_clean <- oecd_pmr |> 
  select(
    country_code,
    year,
    PMR_2018_3_3,
    PMR_2018_1_3,
    PMR_2018_6,
    PMR_2018_1_4,
    PMR_2018_1_2,
    PMR_2018_2_1,
    PMR_2018_1_1,
    PMR_2018_2_2
  ) |>
  clean_names() |> 
  rename_with(
    # replace prefixes with efi conventions
    ~ paste0("oecd_", .),
    .cols = starts_with("pmr")
  )

# 12. Open Budget Survey
open_budget_clean <- open_budget |> 
  select(
    country_code = ISO,
    year,
    ibp_obs_obi = obi
  ) |> 
  # fix cambodia ISO3
  mutate(
    country_code = if_else(
      country_code == "KMH",
      "KHM",
      country_code
    )
  ) |> 
  # shift values one year earlier, to reflect year of measurement
  # this holds starting in year = 2015
  mutate(
    year = if_else(
      year >= 2015,  year - 1, year
    )
  )

# 13. Debt Transparency
debt_transparency_clean <- debt_transparency |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("debt")
  )

# 14. GFDB Bank Concentration
gfdb_clean <- gfdb |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("gfdb")
  )

# 15. Women, Business and the Law
wbl_clean <- wbl |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("wbl")
  )
```

## Consolidate data

This section joins all of the datasets together to make the full data. The join is done by country code and year. This section excludes certain codes and alters others so that all of them fit the same standard. Once the country codes are standard, the excluded codes are filtered out and the datasets are joined. Lastly, any year before 1990 is excluded from the final set and the
columns are ordered by country name.

```{r consolidate_data}
excluded_country_code <- c(
  "AIA", # anguilla
  "OECD", # OECD
  "SML", # somaliland
  "ZZB", # zanzibar
  "CUB", # cuba
  "PRK", # democratic people's republic of Korea
  "KMH", # unclear, listed in Open Budget Survey
  "PSG" # palestine and gaza (VDEM)
)

cliar_indicators <- list(
  efi_clean,
  fraser_clean,
  romelli_clean,
  oecd_epl_clean,
  spi_clean,
  aspire_clean,
  rise_clean,
  wdi_clean,
  vdem_clean,
  heritage_clean,
  oecd_pmr_clean,
  open_budget_clean,
  debt_transparency_clean,
  gfdb_clean,
  wbl_clean
) |> 
  map(
    # fix country codes for full join
    ~ mutate(
        .,
        country_code = case_when(
          country_code == "ZAR" ~ "COD", # democratic republic of congo
          country_code == "ROM" ~ "ROU", # romania
          T ~ country_code
        )
      ) |> 
      filter(
        !(country_code %in% excluded_country_code)
      )
  ) |> 
  reduce(
    full_join,
    by = c("country_code", "year")
  ) |> 
  filter(
    year >= 1990
  )
  
# order column names
cliar_indicators <- cliar_indicators %>%
  select(
    country_code,
    year,
    sort(colnames(.)),
    -starts_with("country_name")
  ) |> 
  arrange(
    country_code,
    year
  ) |> 
  mutate(
    index = row_number()
  )
```

## Data Quality Control: Indicator Selection

Verify that the indicators are selected correctly. To do this, take the non-removed indicators from the metadata file as the indicators from combined dataset created in step 5 and ensure they have the same contents by using an anti-join in both directions. Re-select indicators to ensure that only the indicators in metadata and v2 id cols are in data.

```{r indicator_selection}
# verify that the indicators are selected correctly
db_variables_indicators <- db_variables |> 
  select(
    variable
  )

# only retain indicators contained in metadata + id cols
cliar_indicators <- cliar_indicators %>%  
  # add country names
  left_join(
    wb_country_list |> 
      distinct(country_code, country_name),
    by = "country_code"
  ) |> 
  select(
    country_code,
    country_name,
    year,
    all_of(db_variables_indicators |> pull(variable))
  )

cliar_indicators_id <- cliar_indicators |> 
  colnames()|> 
  tibble(
    variable = colnames(cliar_indicators)
  )

test_that(
  "All indicators contained in metadata are in the CLIAR dataset",{
    expect_equal(
      nrow(
        db_variables_indicators |> 
          anti_join(cliar_indicators_id, by = "variable") |> 
          as.data.frame()
        ),
      0
    )
  }
)
```

## Compute family averages

This section computes family averages, dynamically adapting to the selection of indicators.

```{r}
# compute family averages
cliar_indicators_long <-
  cliar_indicators %>%
  pivot_longer(
    any_of(vars_all),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  )

# only calculate family averages for relevant institutional clusters
cliar_family_level_long <- cliar_indicators_long |>
  filter(
    family_var %in% vars_family
  ) |>
  group_by(
    country_code, year, family_var
  ) |>
  summarise(
    value = mean(value, na.rm = TRUE),
    .groups = "drop"
  )

cliar_family_level <- cliar_family_level_long |>
  pivot_wider(
    id_cols = c(country_code, year),
    names_from = family_var,
    names_glue = "{family_var}_avg",
    values_from = value
  )

cliar_indicators_clean <- cliar_indicators |>
  left_join(
    cliar_family_level,
    by = c("country_code", "year")
  ) |>
  filter(!country_code %in% c("DDR", "YMD"))

```

```{r panel balance}
# ## Balancing the panel
# # Define the range of years
# year_range <- 1990:2024
# 
# balanced_panel <- cliar_indicators_clean %>%
#   group_by(country_name) %>%
#   filter(n_distinct(year) < 35) %>%
#   complete(year = year_range) %>%
#   ungroup() %>%
#     mutate(country_code = countrycode(country_name, "country.name", "iso3c"))
# 
# 
# 
# cliar_indicators_balanced <- left_join(
#   cliar_indicators_clean,
#   balanced_panel,
#   by = c("year", "country_name")
#   )
# 
# cliar_indicators_clean <- cliar_indicators_balanced

```



```{r}
# Create a new row with specified values
# new_row <- tibble(
#   country_code = "CHI",
#   country_name = "Channel Islands",
#   year = 2023
# )
#Commenting out as this is causing issues

# Add NA for all other columns
# new_row <- new_row %>%
#   mutate(
#   add_column(across(everything(), ~ NA))
# )

# # Add the new row to the existing dataframe
# cliar_indicators_clean <- cliar_indicators_clean %>%
#   bind_rows(new_row)
# 
cliar_indicators_clean %>%
  filter(is.na(country_code))

```


## Data Quality Control: verify country_code and country_name consistency

This section ensures that the country_code code and the country name are consistent. Check this by performing an anti-join in both directions on the official WB list of country codes and names and the cliar indicators dataset.

```{r country_validation}
# there are 218 country codes listed in the WB's official website
# https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups


# a. verify that all the country codes from the official data are included
test_that(
  "Verify that all the country codes from the official data are included",
  expect_equal(
    # number of rows is zero
    cliar_indicators_clean |> 
      distinct(country_code, country_name) |> 
        anti_join(
          wb_country_list |> 
            distinct(country_code, country_name),
          by = c("country_code", "country_name")
        ) |> nrow(),
      0
  )
)

# b. verify that cliar has distinct country-year
test_that(
  "Verify that CLIAR has distinct country years",{
    expect_equal(
      nrow(cliar_indicators_clean),
      cliar_indicators_clean |> 
        distinct(country_code, year) |> 
        nrow()
    )
  }
)

distinct_years_per_country <- cliar_indicators_clean %>%
  group_by(country_name) %>%
  summarize(distinct_years = n_distinct(year))

# c. verify that all countries have complete year coverage
test_that(
  "Verify that country codes have coverage for all years",{
    expect_equal(
      # calculate number of years covered by country
      cliar_indicators_clean |> 
        count(country_code) |> 
        pull(n) |> 
        unique(),
      ref_year - 1990
    )
  }
)
```

## Compute coverage diagnostics

Use the compute_coverage function from funs.R to create the coverage countries and years it is present for. With that information, percentage coverage, year range, percent of complete records, as well as standard distribution information such as mean and standard deviation are calculated.

```{r coverage_diagnostics}
cliar_indicators_diagnostic <- cliar_indicators_clean |>
  select(-country_name) |> 
  compute_coverage(country_code, year, ref_year - 5) |> 
  left_join(
    db_variables |> select(variable, var_name, source, family_name),
    by = c("Indicator" = "variable")
  ) |> 
  select(
    `Indicator`,
    `Indicator Name` = var_name,
    `Institutional Family` = family_name,
    everything(),
    `Data Source` = source
  ) |> 
  arrange(
    `Institutional Family`,
    Indicator
  )
```

## Incorporate country income and region

We incorporate the country income group and region. Please note that there is no available data on income group for Venezuela (`country_code` == "VEN"). We retroactively classify income groups using 2023 data.

```{r country_income_and_region}
cliar_indicators_complete <- cliar_indicators_clean |> 
  left_join(
    country_income_and_region,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, year, everything()
  )
```

## Save data

```{r}
write_rds(
  cliar_indicators_complete,
  here(
    "data",
    "output",
    "compiled_indicators.rds"
  )
)

cliar_indicators_diagnostic |> 
    write_rds(
      here(
        "data",
        "output",
        "diagnostics_compiled_indicators.rds"
      )
    )
```
