# Calculate distance to frontier

NOTE: We have to add the dynamic benchmarking that Shel has designed for us.

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/outut/country_list.rds`
  - `data/output/db_variables.rds`
      
- Outputs:
 - `data/output/closeness_to_frontier.rds`
 - `data/output/closeness_to_frontier_long.rds`
 - `data/output/closeness_to_frontier_dynamic.rds`
 - `data/output/closeness_to_frontier_dynamic_long.rds`

## Calculate global closeness to frontier

Closeness to frontier (CTF) is global, meaning that we identify the worst and best performance in the full sample (all countries). For each indicator $i$, we compare the last available value of indicator $i$ with the worst and best
performance for indicator $i$ among all countries and in the last $y$ years (2013 - most recent data).^[In [the doing business report](https://www.doingbusiness.org/content/dam/doingBusiness/media/Annual-Reports/English/DB17-Chapters/DB17-DTF-and-DBRankings.pdf) they consider the last 5 years, but here for some indicators we have shorter time series].


1. Keep only data from after 2013

Ideally, this will use data for the last 7 years in any given year

```{r}
cliar_indicators <-
  read_rds(
    here(
      "data",
      "output",
      "compiled_indicators.rds"
    )
  ) %>%
  # we subset our data to the post-2013 period.
  # note: for the static exercise, we further subset to time period after 2018.
  # for the dynamic exercise, we maintain our cutpoint at 2013.
  filter(
    year >= 2013
  )

country_list <- read_rds(
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

db_variables <- read_rds(
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)
```

2. Rescale indicators so a higher number denotes stronger institutions

```{r}
cliar_indicators_rescaled <- cliar_indicators |>
  mutate(
    # V-DEM: corruption: flip direction because “The directionality of the V-Dem corruption index runs from less corrupt to more corrupt unlike the other V-Dem variables that generally run from less democratic to more democratic situation”.
    vdem_core_v2x_corr = 1 - vdem_core_v2x_corr,
    # V-DEM: political polarization, higher scores denote higher polarization, which can lead to institutional weakness
    # so we decide to flip the indicator by multiplying by -1
    vdem_core_v2cacamps = -1 * vdem_core_v2cacamps,
    # PRM indicators: Countries are graded between 0 (less control/involvement) and 6 (more control/involvement).
    # Methodological note for PRM indicates that 1998 and 2013 indicators are comparable,
    # but not with 2018 due to change in methodology, so we only retain post-2018 data.
    across(
      c(
        starts_with("oecd_pmr")
      ),
      ~ ifelse(year < 2018, NA, 6 - .x)
    ),
    # Enterprise Survey: Percent Of Firms Identifying X As A Major Constraint
    across(
      c(starts_with("wb_enterprisesurveys")),
      ~ 100 - .
    ),
    # Freedom house: Countries are graded between 1 (most free) and 7 (least free)
    across(
      c(starts_with("fh_fiw")),
      ~ (8 - .x)
    ),
    # WDI: ensure that pupil-teacher ratio increases lead to a worse score
    # note that because there is no pre-defined maximum for the ratio so we flip direction multiplying by -1
    across(
      c(wdi_seprmenrltczs, wdi_sesecenrltczs),
      ~ -1 * .x
    ),
    # GFDB:Bank concentration, the higher it is, the less competition. therefore indicator is flipped
    wb_gfdb_oi_01 = 100 - wb_gfdb_oi_01
  )
```


3. Calculate country-level average for each indicator

For the static benchmark, we only calculate averages for indicators starting in the year 2018.

```{r}
country_average <-
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |>
  group_by(
    country_code
  ) %>%
  summarise(
    across(
      all_of(c(vars_static_ctf)),
      ~ mean(., na.rm = TRUE)
    ),
    wdi_nygdppcapppkd = wdi_nygdppcapppkd[year == max(year)]
  )
```

4. Identify worst and best performance for each indicator

```{r}
# static
min_max <-
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |>
  summarise(
    across(
      all_of(vars_static_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  )

# dynamic: note that there are quite a few cases of Infinite warnings (due to missingness)
min_max_dynamic <- cliar_indicators_rescaled %>%
  filter(
    between(year, 2013, 2022)
  ) |> 
  summarise(
    across(
      all_of(vars_dynamic_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  ) %>%
  filter(!is.infinite(min) & !is.infinite(max))
```

5. Calculate closeness to frontier at indicator level

```{r}
ctf <-
  country_average %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )

ctf_dynamic <-
  cliar_indicators_rescaled %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max_dynamic,
    by = c("variable")
  ) %>%
  mutate(
    ctf_dyn = (min - value) / (min - max),
    ctf_dyn = ifelse(
      ctf_dyn == 0,
      0.01,
      ctf_dyn
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code", "year"),
    names_from = "variable",
    values_from = "ctf_dyn"
  ) %>%
  left_join(
    cliar_indicators_rescaled %>%
      select(country_code, year)
  )
```

## Calculate median per group

```{r}
group_ctf <-
  country_list %>%
  left_join(
    ctf,
    by = "country_code"
  ) %>%
  group_by(
    group_code, group
  ) %>%
  summarise(
    across(
      c(all_of(vars_static_ctf)),
      ~ median(., na.rm = TRUE)
    )
  ) %>%
  filter(!is.na(group)) %>%
  rename(
    country_name = group,
    country_code = group_code
  )

# static
ctf <- tibble::add_column(ctf, country_group = 0, .after = "country_code")
group_ctf <- tibble::add_column(group_ctf, country_group = 1, .after = "country_code")

# dynamic
group_ctf_dynamic <- country_list %>%
  left_join(
    ctf_dynamic,
    by = "country_code",
    relationship = "many-to-many"
  ) %>%
  group_by(
    group_code, group, year
  ) %>%
  summarise(
    across(
      c(all_of(vars_dynamic_ctf)),
      ~ median(., na.rm = TRUE)
    )
  ) %>%
  filter(!is.na(group)) %>%
  rename(
    country_name = group,
    country_code = group_code
  )

ctf_dynamic <- add_column(ctf_dynamic, country_group = 0, .after = "country_code")
group_ctf_dynamic <- add_column(group_ctf_dynamic, country_group = 1, .after = "country_code")
```

## Clean CTF data and incorporate logged GDP per capita

```{r}
# static
ctf <-
  ctf %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |>
  # add gdp per capita (PPP) data
  # use average value (as in legacy ctf)
  left_join(
    country_average |> select(country_code, wdi_nygdppcapppkd),
    by = c("country_code")
  ) |>
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |>
  bind_rows(group_ctf) %>%
  ungroup() %>%
  arrange(country_name) |>
  select(
    country_code,
    country_name,
    everything()
  )

# dynamic
ctf_dynamic <-
  ctf_dynamic %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |>
  # add gdp per capita (PPP) data
  left_join(
    cliar_indicators |> select(country_code, year, wdi_nygdppcapppkd),
    by = c("country_code", "year")
  ) |>
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |>
  bind_rows(group_ctf_dynamic) %>%
  ungroup() %>%
  arrange(country_name) |>
  select(
    country_code,
    country_name,
    everything()
  )
```

## Convert to long-form

```{r}
# static
ctf_long <-
  ctf %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    relationship = "many-to-many",
    by = "country_code",
  )

ctf_long_clean <-
  ctf_long %>%
  group_by(family_name, family_var, country_name, country_code, group, country_group) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_long)

# dynamic
ctf_dynamic_long <-
  ctf_dynamic %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var)
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    relationship = "many-to-many",
    by = "country_code",
  )

ctf_dynamic_long_clean <-
  ctf_dynamic_long %>%
  group_by(family_name, family_var, country_name, country_code, country_group, group, year) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_dynamic_long)
```

## Calculate family level data

### Static

```{r}
# static
ctf_static_family <- ctf |> 
  compute_family_average(
    vars = vars_static_family_ctf,
    db_variables = db_variables
  )

# dynamic
ctf_dynamic_family <- ctf_dynamic |> 
  # only retain even years because data is updated every two-years
  filter(
    year %% 2 == 0
  ) |> 
  compute_family_average(
    vars = c(vars_dynamic_family_ctf, vars_dynamic_partial_ctf),
    type = "dynamic",
    db_variables = db_variables
  )

# join family averages to ctfs
ctf_clean <- ctf |> 
  left_join(
    ctf_static_family,
    by = "country_code"
  )

ctf_dynamic_clean <- ctf_dynamic |> 
  left_join(
    ctf_dynamic_family,
    by = c("country_code", "year")
  )
```

## Diagnostics on family averages
```{r}
# select family averages to diagnose
vars_family_static_ctf <- ctf_static_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

vars_family_dynamic_ctf <- ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

# missingness by institutional family average
# static
ctf_static_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Static CTF",
    subtitle = "Unit of Analysis: Country"
  )

# dynamic
ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Dynamic CTF",
    subtitle = "Unit of Analysis: Country-Year"
  )

# static family averages diagnosis
theme_set(
  theme_minimal()
)

vars_family_static_ctf |> 
  set_names(vars_family_static_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_static_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Static Benchmarking"
  )
  
# dynamic family averages diagnosis
vars_family_dynamic_ctf |> 
  set_names(vars_family_dynamic_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_dynamic_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Dynamic Benchmarking"
  )
```


## Data Quality Control
```{r}
test_that(
  "All countries are covered",
  {
    expect_setequal(
      ctf_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
    expect_setequal(
      ctf_dynamic_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
  }
)

test_that(
  "All indicators are covered",
  {
    ## Shel added _avg to the pattern to take care of the new family level indicators (that all have an _avg suffix)
    expect_setequal(
      ctf_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_static_ctf
    )
    expect_setequal(
      ctf_dynamic_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_dynamic_ctf
    )
  }
)
```

## Update db_variables to contain the family averages

```{r}
db_variables <- db_variables %>% 
  mutate(
    across(where(is.character), str_squish)
  ) |> 
  rename(
    rank_id = indicator_order
  ) |> 
  mutate(
    rank_id = rank_id + 1
  )

# add family level vars
family_level_vars <- db_variables %>% 
  distinct(family_var, family_name) %>% 
  rowwise() %>% 
  mutate(
    variable = paste0(family_var, "_avg"),
    var_name = paste0(family_name, " Average"),
    var_level = "indicator",
    benchmarked_ctf = "Yes",
    rank_id = 1
  )

db_variables <- db_variables %>% 
  bind_rows(family_level_vars) %>%
  arrange(family_var, rank_id)
```

## Write-out data

```{r}
write_rds(
  ctf_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier.rds"
  )
)

write_rds(
  ctf_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_long.rds"
  )
)

write_rds(
  ctf_dynamic_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic.rds"
  )
)

write_rds(
  ctf_dynamic_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic_long.rds"
  )
)

write_rds(
  db_variables,
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)
```

