# Calculate distance to frontier

NOTE: We have to add the dynamic benchmarking that Shel has designed for us.

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/outut/country_list.rds`
  - `data/output/db_variables.rds`
      
- Outputs:
 - `data/output/closeness_to_frontier.rds`
 - `data/output/closeness_to_frontier_long.rds`
 - `data/output/closeness_to_frontier_dynamic.rds`
 - `data/output/closeness_to_frontier_dynamic_long.rds`

## Calculate global closeness to frontier

Closeness to frontier (CTF) is global, meaning that we identify the worst and best performance in the full sample (all countries). For each indicator $i$, we compare the last available value of indicator $i$ with the worst and best
performance for indicator $i$ among all countries and in the last $y$ years (2013 - most recent data).^[In [the doing business report](https://www.doingbusiness.org/content/dam/doingBusiness/media/Annual-Reports/English/DB17-Chapters/DB17-DTF-and-DBRankings.pdf) they consider the last 5 years, but here for some indicators we have shorter time series].


1. Keep only data from after 2013

Ideally, this will use data for the last 7 years in any given year

```{r}
cliar_indicators <-
  read_rds(
    here(
      "data",
      "output",
      "compiled_indicators.rds"
    )
  ) %>%
  # we need to verify what we are doing with the cut-off points
  filter(
    year >= 2013
  )

country_list <- read_rds(
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

db_variables <- read_rds(
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)

vars_ctf <- db_variables |> 
  filter(
    benchmarked_ctf == "Yes"
  ) |> 
  pull(variable)
```

2. Rescale indicators so a higher number denotes stronger institutions

```{r}
cliar_indicators_rescaled <- cliar_indicators |> 
  mutate(
    # V-DEM: corruption
    # PRM indicators: Countries are graded between 0 (less control/involvement) and 6 (more control/involvement). 
    # Methodological note for PRM indicates that 1998 and 2013 indicators are comparable, 
    # but not with 2018 due to change in methodology, so we only retain post-2018 data.
    across(
      c(
        starts_with("oecd_pmr")
      ),
      ~ ifelse(year < 2018, NA, 6 - .x)
    ),
    # Enterprise Survey: Percent Of Firms Identifying X As A Major Constraint
    across(
      c(starts_with("wb_enterprisesurveys")),
      ~ 100 - .
    ),
    # Freedom house: Countries are graded between 1 (most free) and 7 (least free)
    across(
      c(starts_with("fh_fiw")),
      ~ (8 - .x)
    )
  )

```


3. Calculate country-level average for each indicator

For the static benchmark, we only calculate averages for indicators starting in the year 2018.

```{r}
country_average <-
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |> 
  group_by(
    country_code
  ) %>%
  summarise(
    across(
      all_of(c(vars_ctf, "wdi_nygdppcapppkd")),
      ~ mean(., na.rm = TRUE)
    )
  )
```

4. Identify worst and best performance for each indicator

```{r}
# static
min_max <-
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |> 
  summarise(
    across(
      all_of(vars_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names="{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  )

# dynamic: note that there are quite a few cases of Infinite warnings (due to missingness)
min_max_dynamic <- cliar_indicators_rescaled %>%
  group_by(year) %>% 
  summarise(
    across(
      all_of(vars_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names="{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    -year, 
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  ) %>% 
  filter(!is.infinite(min) & !is.infinite(max))
```

5. Calculate closeness to frontier at indicator level

```{r}
ctf <-
  country_average %>%
  pivot_longer(
    all_of(vars_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )

ctf_dynamic <-
  cliar_indicators_rescaled %>%
  pivot_longer(
    all_of(vars_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max_dynamic,
    by = c("year", "variable")
  ) %>%
  mutate(
    ctf_dyn = (min - value) / (min - max),
    ctf_dyn = ifelse(
      ctf_dyn == 0,
      0.01,
      ctf_dyn
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code", "year"),
    names_from = "variable",
    values_from = "ctf_dyn"
  ) %>%
  left_join(
    cliar_indicators_rescaled %>%
      select(country_code, year)
  )
```

## Calculate median per group

```{r}
group_ctf <-
  country_list %>%
  left_join(
    ctf,
    by = "country_code"
  ) %>%
  group_by(
    group_code, group
  ) %>%
  summarise(
    across(
      c(all_of(vars_ctf)),
      ~ median(., na.rm = TRUE)
    )     
  ) %>%
  filter(!is.na(group)) %>%
  rename(
    country_name = group,
    country_code = group_code
  )

group_ctf_dynamic <- country_list %>%
  left_join(
    ctf_dynamic,
    by = "country_code",
    relationship = "many-to-many"
  ) %>%
  group_by(
    group_code, group, year
  ) %>%
  summarise(
    across(
      c(all_of(vars_ctf)),
      ~ median(., na.rm = TRUE)
    )     
  ) %>%
  filter(!is.na(group)) %>%
  rename(
    country_name = group,
    country_code = group_code
  ) 

# static
ctf <- tibble::add_column(ctf,country_group = 0,.after = 'country_code')
group_ctf <- tibble::add_column(group_ctf,country_group=1,.after = 'country_code')

# dynamic
ctf_dynamic <- add_column(ctf_dynamic, country_group = 0,.after = 'country_code')
group_ctf_dynamic <- add_column(group_ctf_dynamic, country_group=1,.after = 'country_code')
```

## Clean CTF data and incorporate logged GDP per capita

```{r}
# static
ctf_clean <-
  ctf %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |> 
  # add gdp per capita (PPP) data
  # use average value (as in legacy ctf)
  left_join(
    country_average |> select(country_code, wdi_nygdppcapppkd),
    by = c("country_code")
  ) |> 
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |> 
  bind_rows(group_ctf) %>%
  ungroup %>%
  arrange(country_name) |> 
  select(
    country_code,
    country_name,
    everything()
  )

# dynamic
ctf_dynamic_clean <-
  ctf_dynamic %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |> 
  # add gdp per capita (PPP) data
  left_join(
    cliar_indicators |> select(country_code, year, wdi_nygdppcapppkd),
    by = c("country_code", "year")
  ) |> 
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |> 
  bind_rows(group_ctf) %>%
  ungroup %>%
  arrange(country_name) |> 
  select(
    country_code,
    country_name,
    everything()
  )
```

## Convert to long-form

```{r}
# static
ctf_long <-
  ctf_clean %>%
  pivot_longer(
    all_of(vars_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    by = "country_code",
    relationship = "many-to-many"
  )

ctf_long_clean <-
  ctf_long %>%
  group_by(family_name, family_var, country_name, country_code, group) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_long)

# dynamic
ctf_dynamic_long <-
  ctf_dynamic_clean %>%
  pivot_longer(
    all_of(vars_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var)
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    by = "country_code",
    relationship = "many-to-many"
  )

ctf_dynamic_long_clean <-
  ctf_dynamic_long %>%
  group_by(family_name, family_var, country_name, country_code, country_group, group, year) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_dynamic_long)
```

## Data Quality Control
```{r}
test_that(
  "All countries are covered", {
  expect_setequal(
    ctf_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
    country_list |> distinct(country_code) |> pull()
  )
  expect_setequal(
    ctf_dynamic_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
    country_list |> distinct(country_code) |> pull()
  )
  }
)

test_that(
  "All indicators are covered",{
    expect_setequal(
    ctf_clean |> colnames() |> str_subset("year|country|gdp", negate = TRUE),
    vars_ctf
    )
    expect_setequal(
      ctf_dynamic_clean |> colnames() |> str_subset("year|country|gdp", negate = TRUE),
      vars_ctf
    )
  }
)
```

## Write-out data.

```{r}
write_rds(
  ctf_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier.rds"
  )
)

write_rds(
  ctf_long_clean,
  here( 
    "data",
    "output",
    "closeness_to_frontier_long.rds"
  )
)

write_rds(
  ctf_dynamic_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic.rds"
  )
)

write_rds(
  ctf_dynamic_long_clean,
  here( 
    "data",
    "output",
    "closeness_to_frontier_dynamic_long.rds"
  )
)
```
