# Calculate distance to frontier

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/outut/country_list.rds`
  - `data/output/db_variables.rds`
      
- Outputs:
 - `data/output/closeness_to_frontier.rds`
 - `data/output/closeness_to_frontier_long.rds`
 - `data/output/closeness_to_frontier_dynamic.rds`
 - `data/output/closeness_to_frontier_dynamic_long.rds`

## Calculate global closeness to frontier

Closeness to frontier (CTF) is global, meaning that we identify the worst and best performance in the full sample (all countries). For each indicator $i$, we compare the last available value of indicator $i$ with the worst and best
performance for indicator $i$ among all countries and in the last $y$ years (2013 - most recent data).^[In the [Doing Business report](https://www.doingbusiness.org/content/dam/doingBusiness/media/Annual-Reports/English/DB17-Chapters/DB17-DTF-and-DBRankings.pdf) they consider the last 5 years, but here for some indicators we have shorter time series.]

## Keep only data from after 2013

Ideally, this will use data for the last 7 years in any given year.

```{r}
#load in cleaned indicators from step 3
cliar_indicators <-
  read_rds(
    here(
      "data",
      "output",
      "compiled_indicators.rds"
    )
  ) %>%
  # filter to only years 2013 or later
  filter(
    year >= 2013
  )

#read in country list from step 3
country_list <- read_rds(
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

#read in db_variables
db_variables <- read_rds(
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)

vars_ctf <- db_variables |>
  filter(
    benchmarked_ctf == "Yes"
  ) |>
  pull(variable)

# country income group and region
country_income_and_region <- read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "List of economies",
      n_max = 219
    ) %>%
    transmute(
      country_code = Code,
      region = Region,
      income_group = `Income group`
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )
```

## Rescale indicators so a higher number denotes stronger institutions

V-DEM: corruption
PRM indicators: Countries are graded between 0 (less control/involvement) and 6 (more control/involvement). 
    In order to rescale these indicators, the years after 2018 are selected, 
    and then each indicator value is subtracted from 6. so that a value that was
    previously 0 for less control, is now 6, indicating a stronger institution.
    
    NOTE:
    Methodological note for PRM indicates that 1998 and 2013 indicators are 
    comparable, but not with 2018 due to change in methodology, so we only retain
    post-2018 data.
    
Enterprise Survey: Percent Of Firms Identifying X As A Major Constraint
    Subtract each indicator from 100, so that a low percentage of firm, for example
    10%, will now have a score of 90, indicating stronger institutions
    
Freedom house: Countries are graded between 1 (most free) and 7 (least free)
    Subtract each indicator from 8 so that a value of 1 for the most free is now 7,
    indicating stronger institutions.
    
```{r}
#create new table to hold rescaled values
cliar_indicators_rescaled <- cliar_indicators |> 
  mutate(
    # V-DEM: political and executive corruption: flip direction because “The directionality of the V-Dem corruption index runs from less corrupt to more corrupt unlike the other V-Dem variables that generally run from less democratic to more democratic situation”.
    vdem_core_v2x_pubcorr = -1 * vdem_core_v2x_pubcorr,
    vdem_core_v2x_execorr = -1 * vdem_core_v2x_execorr,
    # V-DEM: political polarization, higher scores denote higher polarization, which can lead to institutional weakness
    # so we decide to flip the indicator by multiplying by -1
    vdem_core_v2cacamps = -1 * vdem_core_v2cacamps,
    # PRM indicators: Countries are graded between 0 (less control/involvement) and 6 (more control/involvement).
    # Methodological note for PRM indicates that 1998 and 2013 indicators are comparable,
    # but not with 2018 due to change in methodology, so we only retain post-2018 data.
    across(
      c(
        starts_with("oecd_pmr")
      ),
      ~ ifelse(year < 2018, NA, 6 - .x)
    ),
    # Enterprise Survey: Percent Of Firms Identifying X As A Major Constraint
    across(
      c(starts_with("wb_enterprisesurveys")),
      ~ 100 - .
    ),
    # Freedom house: Countries are graded between 1 (most free) and 7 (least free)
    across(
      c(starts_with("fh_fiw")),
      ~ (8 - .x)
    ),
    # WDI: ensure that pupil-teacher ratio increases lead to a worse score
    # note that because there is no pre-defined maximum for the ratio so we flip direction multiplying by -1
    across(
      c(wdi_seprmenrltczs, wdi_sesecenrltczs),
      ~ -1 * .x
    ),
    # GFDB:Bank concentration, the higher it is, the less competition. therefore indicator is flipped
    wb_gfdb_oi_01 = 100 - wb_gfdb_oi_01
  )
```

## Calculate country-level average for each indicator

For the static benchmark, we only calculate averages for indicators starting in the year 2018.

```{r}
country_average <-
  #filter only data from years we are using
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |> 
  #this groups countries together so average can be taken 
  group_by(
    country_code
  ) %>%
  summarise(
    across(
      all_of(c(vars_static_ctf)),
      ~ mean(., na.rm = TRUE)
    ),
    wdi_nygdppcapppkd = wdi_nygdppcapppkd[year == max(year)]
  )

country_last_year <-
  #filter only data from years we are using
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |> 
  arrange(country_code, year) |> 
  #this groups countries together so average can be taken 
  group_by(
    country_code
  ) |> 
  select(
    all_of(c(vars_static_ctf))
  ) |> 
  # fill missing observations for each indicator with the latest available data
  fill() |> 
  # slice last available data for each country_code
  slice_tail() |> 
  ungroup()
```

## Identify worst and best performance for each indicator

Find this data both on a global time-scale, and for each individual year.

Inspect the entire dataset of rescaled indicator values - so including the indicator
values for every country year after 2013 - and identify the lowes tand highest 
values in each category. 

```{r}
# static
min_max <-
  cliar_indicators_rescaled %>%
  filter(year >= 2018) |>
  summarise(
    across(
      all_of(vars_static_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  )

# dynamic: note that there are quite a few cases of Infinite warnings (due to missingness)
min_max_dynamic <- cliar_indicators_rescaled %>%
  filter(
    between(year, 2014, 2022)
  ) |> 
  summarise(
    across(
      all_of(vars_dynamic_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  ) %>%
  filter(!is.infinite(min) & !is.infinite(max))
```

## Calculate closeness to frontier at indicator level

```{r}
ctf <-
  country_average %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )

# reproduce CTF scores using latest available data for each country-indicator
ctf_static_last_year <- country_last_year %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )
  
ctf_dynamic <-
  cliar_indicators_rescaled %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max_dynamic,
    by = c("variable")
  ) %>%
  mutate(
    ctf_dyn = (min - value) / (min - max),
    ctf_dyn = ifelse(
      ctf_dyn == 0,
      0.01,
      ctf_dyn
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code", "year"),
    names_from = "variable",
    values_from = "ctf_dyn"
  ) %>%
  left_join(
    cliar_indicators_rescaled %>%
      select(country_code, year)
  )
```

## Calculate median per group

Group countries by regional, economic, or income groups and take indicator median
for those groups
```{r}
# static
group_ctf <-
  #join country list with ctf
  country_list %>%
  left_join(
    ctf,
    by = "country_code"
  ) %>%
  #group by group code
  group_by(
    group_code, group
  ) %>%
  #take median
  summarise(
    across(
      c(all_of(vars_static_ctf)),
      ~ median(., na.rm = TRUE)
    )
  ) %>%
  #filter for any na values 
  filter(!is.na(group)) %>%
  #rename values to be consisted with other datasets
  rename(
    country_name = group,
    country_code = group_code
  )

#add group_ctf value to ctf dataset
ctf <- tibble::add_column(ctf, country_group = 0, .after = "country_code")
group_ctf <- tibble::add_column(group_ctf, country_group = 1, .after = "country_code")

# dynamic
group_ctf_dynamic <- country_list %>%
  #join country list with ctf
  left_join(
    ctf_dynamic,
    by = "country_code",
    relationship = "many-to-many"
  ) %>%
  #group by group code
  group_by(
    group_code, group, year
  ) %>%
  #take mediam
  summarise(
    across(
      c(all_of(vars_dynamic_ctf)),
      ~ median(., na.rm = TRUE)
    )
  ) %>%
  #filter out na and rename for consistency
  filter(!is.na(group)) %>%
  rename(
    country_name = group,
    country_code = group_code
  )

ctf_dynamic <- add_column(ctf_dynamic, country_group = 0, .after = "country_code")
group_ctf_dynamic <- add_column(group_ctf_dynamic, country_group = 1, .after = "country_code")
```

## Clean CTF data and incorporate logged GDP per capita

```{r}
# static
ctf <-
  ctf %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |>
  # add gdp per capita (PPP) data
  # use average value (as in legacy ctf)
  left_join(
    country_average |> select(country_code, wdi_nygdppcapppkd),
    by = c("country_code")
  ) |>
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |>
  bind_rows(group_ctf) %>%
  ungroup() %>%
  arrange(country_name) |>
  select(
    country_code,
    country_name,
    everything()
  )

# dynamic
ctf_dynamic <-
  ctf_dynamic %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |>
  # add gdp per capita (PPP) data
  left_join(
    cliar_indicators |> select(country_code, year, wdi_nygdppcapppkd),
    by = c("country_code", "year")
  ) |>
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |>
  bind_rows(group_ctf_dynamic) %>%
  ungroup() %>%
  arrange(country_name) |>
  select(
    country_code,
    country_name,
    everything()
  )
```

## Convert to long-form

This changes the CTF dataset from wide form to long form and adds some additional 
data such as indicator family.

```{r}
# static
ctf_long <-
  ctf %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    relationship = "many-to-many",
    by = "country_code",
  )

ctf_long_clean <-
  ctf_long %>%
  group_by(family_name, family_var, country_name, country_code, group, country_group) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_long)

# dynamic
ctf_dynamic_long <-
  ctf_dynamic %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var)
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group),
    relationship = "many-to-many",
    by = "country_code",
  )

ctf_dynamic_long_clean <-
  ctf_dynamic_long %>%
  group_by(family_name, family_var, country_name, country_code, country_group, group, year) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_dynamic_long)
```

## Calculate family level data

Similarly to creating group-level data, this section calculates median CTF for each indicator family 

### Static

```{r}
# static
ctf_static_family <- ctf |> 
  compute_family_average(
    vars = vars_static_family_ctf,
    db_variables = db_variables
  )

# dynamic
ctf_dynamic_family <- ctf_dynamic |> 
  # only retain even years because data is updated every two-years
  filter(
    year %% 2 == 0
  ) |> 
  compute_family_average(
    vars = c(vars_dynamic_family_ctf, vars_dynamic_partial_ctf),
    type = "dynamic",
    db_variables = db_variables
  )

# join family averages to ctfs
ctf_clean <- ctf |> 
  left_join(
    ctf_static_family,
    by = "country_code"
  )

ctf_dynamic_clean <- ctf_dynamic |> 
  left_join(
    ctf_dynamic_family,
    by = c("country_code", "year")
  )
```

## Diagnostics on family averages

Take the family averages for dynamic data.

```{r}
# select family averages to diagnose
vars_family_static_ctf <- ctf_static_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

vars_family_dynamic_ctf <- ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

# missingness by institutional family average
# static
ctf_static_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Static CTF",
    subtitle = "Unit of Analysis: Country"
  )

# dynamic
ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Dynamic CTF",
    subtitle = "Unit of Analysis: Country-Year"
  )

# static family averages diagnosis
theme_set(
  theme_minimal()
)


vars_family_static_ctf |> 
  set_names(vars_family_static_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_static_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Static Benchmarking"
  )
  
# dynamic family averages diagnosis
vars_family_dynamic_ctf |> 
  set_names(vars_family_dynamic_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_dynamic_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Dynamic Benchmarking"
  )
```

## Data Quality Control

Test that all expected indicators and countries are covered
```{r}
test_that(
  "All countries are covered",
  {
    expect_setequal(
      ctf_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
    expect_setequal(
      ctf_dynamic_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
  }
)

test_that(
  "All indicators are covered",
  {
    ## Shel added _avg to the pattern to take care of the new family level indicators (that all have an _avg suffix)
    expect_setequal(
      ctf_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_static_ctf
    )
    expect_setequal(
      ctf_dynamic_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_dynamic_ctf
    )
  }
)
```

## Update db_variables to contain the family averages

```{r}
db_variables <- db_variables %>% 
  mutate(
    across(where(is.character), str_squish)
  ) |> 
  rename(
    rank_id = indicator_order
  ) |> 
  mutate(
    rank_id = rank_id + 1
  )

# add family level vars
family_level_vars <- db_variables %>% 
  distinct(family_var, family_name) %>% 
  rowwise() %>% 
  mutate(
    variable = paste0(family_var, "_avg"),
    var_name = paste0(family_name, " Average"),
    var_level = "indicator",
    description = "The cluster-level average is an unweighted average of the corresponding indicators of this cluster. See Methodological note for details on the inclusion criteria.",
    description_short = "The cluster-level average is an unweighted average of the corresponding indicators for this cluster.",
    source = "CLIAR",
    benchmarked_ctf = "Yes",
    rank_id = 1
  )

db_variables <- db_variables %>% 
  bind_rows(family_level_vars) %>%
  arrange(family_var, rank_id)
```

## Add income group and region

In this section, we add income groups and region. Note that the CTF includes groups as observations, meaning that not all rows are expected to have an income group or region.

```{r}
ctf_complete <- ctf_clean |> 
  left_join(
    country_income_and_region,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, everything()
  )

ctf_dynamic_complete <- ctf_dynamic_clean |> 
  left_join(
    country_income_and_region,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, year, everything()
  )
```

## Institutional Family-level Variance

We compute the dispersion of our institutional family-level scores by country. For the static benchmarking, we provide three metrics:

1. Minimum CTF scores for indicators in the same family, for a given country.
2. Maximum CTF scores for indicators in the same family, for a given country.
3. The variance of CTF scores for indicators in the same family, for a given country.

In the case of the dynamic benchmarking we extend our analysis by specifying min-max and standard deviation for a given country and year.

```{r}
ctf_static_variance <- ctf_complete |> 
  compute_family_variance(
    vars_static_ctf,
    db_variables = db_variables
  )

ctf_dynamic_variance <- ctf_dynamic_complete |> 
  compute_family_variance(
    vars_dynamic_ctf,
    type = "dymamic", 
    db_variables
  )
```

## Robustness checks: 5-year average vs. Last available data

This section produces a set of robustness checks on the computation of the static CTF, comparing the 5-year average scores with the scores computed using the latest available data. We conduct two tests: (a) a scatterplot, where the unit of analysis is a country-indicator combination and (b) a histogram of the correlation for each indicator. 

For (a), we plot the values of CTF-scores for the 5-year average against the last-year available, using as the join keys the country code and variable. We find that the CTF scores produced using these different approaches are along the 45 degree line, indicating that they are strongly correlated and consistent with one another.

For (b), we summarize the CTF scores presented in (a) at the indicator level, computing the correlation between the CTF scores using 5-year averages and last-year values for each indicator. For example, for the indicator "Separation of powers", we calculate the correlation of its two types of CTF scores (5-year vs. last-year) across countries. This gives us a final correlation score at the indicator level, e.g., `0.982`. The same procedure is repeated for each indicator. Finally, we produce a histogram of all correlation scores at the indicator level. We find that the majority of scores (96.4%) have a correlation above 0.95. 

```{r}
ctf_static_last_year_long <- ctf_static_last_year |> 
  pivot_longer(
    cols = c(
      all_of(vars_static_ctf)
    ),
    names_to = "variable",
    values_to = "ctf_last_year"
  )

ctf_static_long <- ctf_clean |> 
  filter(country_group == 0) |> 
  select(country_code, all_of(vars_static_ctf)) |> 
  pivot_longer(
    cols = c(
      all_of(vars_static_ctf)
    ),
    names_to = "variable",
    values_to = "ctf_year_average"
  )

# merge datasets using country code and variable to compute correlation
ctf_robustness <- ctf_static_last_year_long |> 
  inner_join(
    ctf_static_long,
    by = c("country_code", "variable")
  )

# (a) scatterplot of last year vs. year-average ctf scores
ctf_robustness |> 
  ggplot() +
  geom_point(
    aes(ctf_year_average, ctf_last_year),
    color = "steelblue3",
    alpha = 0.7
  ) +
  labs(
    x = "CTF score: 5-year average",
    y = "CTF score: latest available data",
    caption = "The unit of analysis is at the country-indicator level. Please note that indicators for which either value were missing are not plotted."
  ) +
  ggtitle(
    "Correlation between CTF scores computed using (a) 5-Year Average and (b) Last-Year values for indicators"
  ) +
  theme_minimal()

# (b) distribution of correlations by indicator
ctf_robustness |> 
  group_by(variable) |> 
  summarise(
    correlation = cor(ctf_last_year, ctf_year_average, use = "pairwise.complete", method = "pearson")
  ) |> 
  ggplot() +
  geom_histogram(
    aes(correlation, y = stat(width*density), binwidth = 0.01)
  ) +
  geom_vline(
    xintercept = 0.95,
    linetype = "dashed",
    color = "red3"
  ) +
  scale_y_continuous(
    labels = percent_format()
  ) +
  coord_cartesian(
    xlim = c(0.9, 1)
  ) +
  labs(
    x = "Correlation between CTF scores",
    y = "Percentage of Indicators",
    caption = "Dashed red line indicators a correlation above 0.95. 5 out of 137 (3.6%) indicators have a correlation below 0.95. No indicators have a correlation between 0.9."
  ) +
  ggtitle(
    "Distribution of indicator-level correlations of CTF scores"
  ) +
  theme_minimal()
```

## Write-out data

```{r}
write_rds(
  ctf_complete,
  here(
    "data",
    "output",
    "closeness_to_frontier.rds"
  )
)

write_rds(
  ctf_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_long.rds"
  )
)

write_rds(
  ctf_dynamic_complete,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic.rds"
  )
)

write_rds(
  ctf_dynamic_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic_long.rds"
  )
)

write_rds(
  ctf_static_variance,
  here(
    "data",
    "output", 
    "closeness_to_frontier_var_static.rds"
  )
)

write_rds(
  ctf_dynamic_variance,
  here(
    "data",
    "output", 
    "closeness_to_frontier_var_dynamic.rds"
  )
)

write_rds(
  db_variables,
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)
```

