# Clean list of contries

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/input/wb/CLASS.xlsx`, obtained from https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups on September 1, 2022
  - `data/input/wb/group_list.csv`, input by the research team to list relevant groups
      
- Outputs:
  - `data/final/wb_country_list.rds`
  - `data/final/wb_country_groups.rds`

## Inputs

```{r}
  indicators <-
    read_rds(
      here(
        "data",
        "output",
        "compiled_indicators.rds"
      )
    )

  group_list <-
    read_csv(
      here(
        "data",
        "input",
        "wb",
        "group_list.csv"
      )
    )

  country_list <-
    read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "Groups"
    ) %>%
    transmute(
      country_code = CountryCode,
      group = GroupName,
      group_code = GroupCode
    )
```

## Subset country list

The only relevant countries are those we have some data for

```{r}
country_list <-
  indicators %>%
  select(country_code) %>%
  unique %>%
  left_join(country_list)
```

## Subset groups

```{r}
country_list <-
  country_list %>%
  filter(
    group %in% group_list$group_name
  ) %>%
  unique
```

## Save datasets

Dataset with list of countries in our sample

```{r}
write_rds(
  country_list,
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

write_rds(
  group_list,
  here(
    "data",
    "output",
    "wb_country_groups.rds"
  )
)
```
