# [Draft] CLIAR dashboard CTF Coverage Report (2019-2023)

-   Input: `data/output/coverage_report_full_for_analysis.rds`

-   Output: `data/output/coverage_report.Rmd`

```{r, include = FALSE}
# This script generates the consolidated report on coverage by country and CLIAR indicator. It imports, processes and visualizes the data coverage and more importantly, explores at a family level the areas of improvement to tackle data deserts - data poverty.

# Load in the funs.R file 
source(
  here("funs_coverage.R")
)

### Theme: https://bookdown.org/yihui/rmarkdown/pdf-document.html

library(ggrepel)
library(forcats)
library(RColorBrewer)

wrap_facet_titles <- function(x, width) {
  str_wrap(x, width = width)
}


theme_set(
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 9, angle = 45, hjust = .5),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 20, face = "bold"),
    plot.subtitle = element_text(size = 14),
    plot.background = element_blank(),
    plot.caption = element_text(hjust = 0, size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(), 
    legend.position = "none")
  )

# Set global confition for labels. Source: https://ggrepel.slowkow.com/articles/examples.html
options(ggrepel.max.overlaps = Inf)

```

## Import data

```{r, include = FALSE}
# The data imported here has been processed in the 03-process-data.Rmd script
# coverage_long_panel <- read_rds(
#   here("data", "output","coverage_report_full_for_analysis.rds" )
# )

coverage_long_panel <- read_rds(
  here("data", "output","coverage_ctf_for_analysis.rds" )
)

ctf_static_long <- read_rds(
  here("data", "output","closeness_to_frontier_long.rds" )
)


ctf_dynamic <- read_rds(
  here("data", "output","year_coverage_ctf_for_analysis.rds" )
)


```

## Motivation

Context: CLIAR dashboard, Sources feed framework, best administrative data available in the world not a balanced panel and opportunities for improvement

Sample size details: countries and indicator level, time frame

Objective: Data poverty overview at a country level

## I. Avg Data Coverage Map

### a. Regional distribution

```{r,  fig.height= 8, fig.width=12}
# Apply group_average function and specifying
# the following arguments: data, group, subgroup, quantity
coverage_regional <- coverage_long_panel |>
  select(region_short, country_code, available_share) |>
   group_average(region_short, country_code, available_share)

coverage_regional |>
  ggplot(aes(x = group_av, fill = region_short)) +
  geom_density(alpha = 0.5) + 
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Regions?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Family Name") +
  facet_grid(~region_short) +
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  coord_flip() +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100))

```

### b. Income distribution

```{r, fig.height= 8, fig.width=12}
coverage_income <- coverage_long_panel |>
  select(income_group, region_short, country_code, available_share) |>
  group_facet_average(income_group, region_short, country_code, available_share) |>
  filter(!is.na(income_group))

coverage_income |>
  ggplot(aes(x = group_av, fill = income_group)) +
  geom_density(alpha = 0.75) + 
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
    geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Income Groups?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Income Group") +
  facet_grid(~income_group) + 
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_color_brewer(palette = "Spectral") +
  coord_flip() +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100)) 

```

### c. Cluster distribution

```{r,  fig.height= 8, fig.width=12}
coverage_family <- coverage_long_panel |>
  select(family_name, region_short, country_code, available_share) |>
  group_facet_average(family_name, region_short, country_code, available_share) |>
  filter(!is.na(family_name)) |>
  filter(family_name != "(other indicators)")

coverage_family |>
  ggplot(aes(x = group_av, fill =family_name)) +
  geom_density(alpha = 0.75) +
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
    geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Clusters?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Family Name") +
  facet_wrap(
    vars(wrap_facet_titles(family_name, width = 30))) +
  # facet_wrap(~family_name, nrow = 2) + 
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100)) +
  coord_flip()  


```

## II. Country Coverage

### a. Region

Which is the country data coverage within the regions?

```{r, fig.height= 8, fig.width= 12}
coverage_regional |> 
  group_by(country_code) |> 
  ggplot(aes(x = region_short,
            y = group_av,
            color = region_short)) +
   geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
   geom_segment(aes(x = region_short,
                    xend = region_short,
                    y = group_min,
                    yend = group_max),
                    linetype = "solid",
                    linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, 
                    segment.color = "grey", 
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
   ggtitle("How Does Data Coverage Vary within the Regions?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
   labs(
     x = "Region",
     y = "Average Values",
     shape = "Values",
     color = "Region",
     hjust = 0
   ) +
   coord_cartesian(ylim = c(0, 100)) +
   scale_color_brewer(palette = "Paired")
```

MENA has great coverage at an indicator level. What happens is we digg into income level and families

```{r}
### NEXT STEPS REGION
# Questions to answer:
# Number of countries per decile?
### mutate to bins and count by category
```

### b. Income

Are there data deserts at a income level?

```{r, fig.height= 8, fig.width= 12}
# Income group
coverage_income |> 
  ggplot(aes(x = income_group,
             y = group_av,
             color = income_group)) +
  geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
  geom_segment(aes(x = income_group,
                   xend = income_group,
                   y = group_min,
                   yend = group_max),
                   linetype = "solid",
                   linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, # Padding around the label
                    segment.color = "grey", # Color of the connecting line
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
  ggtitle("How Does Data Coverage Vary within Income Groups?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators"
  ) +
  labs(
    x = "Region",
    y = "Average Values",
    shape = "Values",
    color = "Region",
    hjust = 0
  ) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(palette = "Dark2")



```

```{r, fig.height= 8, fig.width= 12}
coverage_income |> 
  ggplot(aes(x = income_group,
             y = group_av,
             color = region_short)) +
  geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
  geom_segment(aes(x = income_group,
                   xend = income_group,
                   y = group_min,
                   yend = group_max),
                   linetype = "solid",
                   linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, # Padding around the label
                    segment.color = "grey", # Color of the connecting line
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
    ggtitle("How Does Data Coverage Vary within Income Groups from a Regional perspective?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators"
  ) +
  labs(
    x = "Region",
    y = "Average Values",
    shape = "Values",
    color = "Region",
    hjust = 0
  ) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(palette = "Paired")
 


```

## III. Cluster coverage

How extensive is the country coverage by indicator for the CTF calculations?

Specifically: what indicators exist for a given country

```{r}
### Bins
indicators_bins <- coverage_long_panel |>
  mutate(
    ctf_years = case_when(
      between(available_share, 0, 20) ~ "1 year",
      between(available_share, 21, 40) ~ "2 years",
      between(available_share, 41, 60) ~ "3 years",
      between(available_share, 61, 80) ~ "4 years",
      between(available_share, 81, 100) ~ "5 years",
      TRUE ~ "Data not available"
    )
  ) |>
  filter(family_name != "(other indicators)")


  
```

```{r}
# Duplicated values test: level of observations country-indicator
indicators_bins |>
  add_count(country_name, indicators) |>
  filter(n > 1) |>
  print() # Empty, no duplicates

```

### a. Total Count and Share

```{r, fig.height= 8, fig.width= 12}
theme_set(
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12, hjust = .5),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 20, face = "bold"),
    plot.subtitle = element_text(size = 14),
    plot.background = element_blank(),
    plot.caption = element_text(hjust = 0, size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(), 
    legend.position = "top")
  )

# Count number of indicators per family for each country 
cluster_shares <- indicators_bins |>
  group_by(family_name, ctf_years) |>
  summarise(
    total_country = n(),
    .groups = "drop"  
  ) |>
  group_by(family_name) |>
  mutate(country_share = total_country / sum(total_country)) |>
  ungroup()

cluster_shares %>%
 ggplot(aes(x = reorder(family_name, total_country), y = total_country, fill = as.factor(ctf_years))) +
  geom_col(position = position_stack(reverse = TRUE)) +  
  labs(
    title = "Indicator Availability by Cluster",
    subtitle = "Analyzing the Total Count of Indicators Within Each Cluster",
    x = "Cluster",
    y = "Total indicator count",
    fill = "CTF Years"
  ) +
  scale_fill_brewer(palette = "OrRd", guide = "legend") + 
  coord_flip()  

```

```{r, fig.height= 8, fig.width= 12}
cluster_shares |>
ggplot(aes(x = reorder(family_name, country_share), y = country_share*100, fill = as.factor(ctf_years))) +
  geom_col(position = position_stack(reverse = TRUE)) +  
  labs(
    title = "Indicator Availability Proportion (%) by Cluster",
    subtitle = "Analyzing the Total Share (%) of Indicators Within Each Cluster",
    x = "Cluster",
    y = "Total indicator share (%)",
    fill = "CTF Years"
  ) +
  scale_fill_brewer(palette = "OrRd", guide = "legend") +  
  coord_flip()  # Flip coordinates for easier viewing of the family names
```

###b. Regional Count
```{r, fig.height= 8, fig.width= 12}
regional_cluster_shares <- indicators_bins |>
  group_by(region_short, family_name, ctf_years) |>
  summarise(
    total_country = n(),
    .groups = "drop"  
  ) |>
  group_by(region_short,family_name) |>
  mutate(country_share = total_country / sum(total_country)) |>
  ungroup()

regional_cluster_shares %>%
 ggplot(aes(x = reorder(family_name, total_country), y = total_country, fill = as.factor(ctf_years))) +
  geom_col(position = position_stack(reverse = TRUE)) +  
  labs(
    title = "Regional Indicator Availability by Cluster",
    subtitle = "Analyzing the Total Count of Indicators Within Each Cluster by Region",
    x = "Cluster",
    y = "Total indicator count",
    fill = "CTF Years"
  ) +
  facet_grid(~region_short) +
   theme(
    axis.text.x = element_text(size = 9, angle = 45, hjust = .5)) +
  scale_fill_brewer(palette = "OrRd", guide = "legend") + 
  coord_flip()  

```


##IV. CFT Indicators

###a. Share
```{r}
# Clean and normalize the availability column, handling NA values
availability_ctf_long <- ctf_static_long %>%
  mutate(
    availability = ifelse(is.na(value), "missing",
                   ifelse(value >= 0, "available", availability))
  )

duplicates_ctf <- availability_ctf_long %>%
  group_by(family_name, var_name, country_name) %>%
  tally() %>%
  filter(n > 1) 
```


```{r, fig.height= 10, fig.width= 12}
country_syria_table <- availability_ctf_long %>%
  filter(country_name == "Syrian Arab Republic") %>%  
  group_by(family_name) %>%
  summarise(
    available_count = sum(availability == "available", na.rm = TRUE),
    missing_count = sum(availability == "missing", na.rm = TRUE),
    total_country_indicators = n(),
    .groups = "drop"
  ) 

# Create a table using gt for better formatting
# Load necessary libraries
library(knitr)
library(gt)

# Adding the share columns to the table
country_syria_table %>%
  mutate(
    available_share = available_count / total_country_indicators * 100,
    missing_share = missing_count / total_country_indicators * 100
  ) %>%
  gt() %>%
  tab_header(
    title = "Data Coverage by Cluster",
    subtitle = "Syrian Arab Republic"
  ) %>%
  cols_label(
    family_name = "Family Name",
    available_count = "Full Access",
    missing_count = "No Access",
    total_country_indicators = "Total Indicators",
    available_share = "Full Access Share (%)",
    missing_share = "No Access Share (%)"
  ) %>%
  tab_spanner(
    label = "Indicators Availabilable",
    columns = c("available_count", "missing_count")
  ) %>%
  fmt_number(
    columns = c("available_count", "missing_count", "total_country_indicators"),
    decimals = 0
  ) %>%
  fmt_number(
    columns = c("available_share", "missing_share"),
    decimals = 1
  ) %>%
  tab_style(
    style = list(
      cell_borders(sides = "bottom", color = "gray", weight = 1)
    ),
    locations = cells_body()
  ) %>%
  tab_options(
    table.width = pct(80),
    column_labels.border.top.width = px(2),
    column_labels.border.bottom.width = px(2)
  )




```


```{r, fig.height= 8, fig.width= 12}
# Calculate Proportions for Available and Missing
country_syria_table <- country_syria_table %>%
  mutate(
    available_share = available_count / total_country_indicators,
    missing_share = missing_count / total_country_indicators
  )

# Create a long format directly for ggplot 
country_syria_table_long <- country_syria_table %>%
  select(family_name, available_share, missing_share) %>%
  pivot_longer(cols = c(available_share, missing_share), 
               names_to = "availability_status", 
               values_to = "share") %>%
  mutate(
    availability_status = recode(availability_status, 
                                "available_share" = "Full Access", 
                                "missing_share" = "No Access")
  )

# Plot share
country_syria_table_long %>%
  arrange(desc(share)) %>%
  ggplot(aes(x = reorder(family_name, share),
             y = share * 100,
             fill = availability_status)) + 
  geom_col(position = position_stack(reverse = TRUE)) +  
  labs(
    title = "Syria: Indicator Availability Proportion (%) by Cluster",
    subtitle = "Share of Available vs Missing Indicators for Each Cluster",
    x = "Family Name",
    y = "Cluster Share (%)",
    fill = "Availability Status"
  ) +
  scale_fill_manual(values = c("Full Access" = "#58d68d", "No Access" = "#cd6155")) + 
  coord_flip()





```


### b. Heatmaps 
```{r, fig.height= 8, fig.width= 10}
# Clean Dataframe 
ctf_dynamic_clean <- ctf_dynamic %>%
                    filter(family_name != "(other indicators)") %>% 
                    filter(!is.na(family_name))

# Create a Function
generate_availability_heatmap <- function(data, country_name_input, family_name_input) {
  
  data %>%
    filter(country_name == country_name_input) %>%  # Filter by country
    filter(family_name == family_name_input) %>%    # Filter by family_name
    filter(benchmarked_ctf == "Yes") %>% 
    mutate(
      availability_status = ifelse(is.na(indicator_value), "No Access", "Full Access")
    ) %>%
    ggplot(aes(x = year, y = var_name, fill = availability_status)) +
    geom_tile(color = "white") +  
    labs(
      title = paste(country_name_input, ": Indicator Availability\nCluster: ", family_name_input),
      subtitle = "Availability of Indicators Over Time (2019-2023)",
      x = "Year",
      y = "Cluster Benchmarked Indicators",
      fill = "Availability Status",
      caption = "Note: Indicator availability across clusters may differ based on how often the data source is updated. 
For a deeper understanding, please consult Table <#> to gain more insight into the update cycles."
    ) +
    scale_fill_manual(
      values = c("Full Access" = "#58d68d", "No Access" = "#cd6155"),  
      breaks = c("Full Access", "No Access"),
      labels = c("Full Access", "No Access")
    )
}


```



```{r, fig.height= 8, fig.width= 10}

# Prepare Country to perform analysis
# Example: Create plots for the country "Syrian Arab Republic" and all unique family names
unique_family_names <- unique(ctf_dynamic_clean$family_name)

# Loop through each unique family_name and apply the generate_availability_heatmap formula
for(family_name in unique_family_names) {
  print(generate_availability_heatmap(ctf_dynamic_clean,"Syrian Arab Republic", family_name))
}

```


[End of code]


```{r eval=FALSE, include=FALSE}
# Load Required Libraries
library(shiny)
library(ggplot2)
library(dplyr)

# Clean data 
ctf_dynamic_clean <- ctf_dynamic %>%
  filter(family_name != "(other indicators)", !is.na(family_name))

# Define the heatmap function
generate_availability_heatmap <- function(data, country_name_input, family_name_input) {
  
  # Preprocess data for the plot
  plot_data <- data %>%
    filter(country_name == country_name_input, family_name == family_name_input, benchmarked_ctf == "Yes") %>%
    mutate(
      availability_status = ifelse(is.na(indicator_value), "No Access", "Full Access")
    )
  
  # Create the heatmap plot
  ggplot(plot_data, aes(x = year, y = var_name, fill = availability_status)) +
    geom_tile(color = "white") +  
    labs(
      title = paste(country_name_input, ": Indicator Availability\nCluster: ", family_name_input),
      subtitle = "Availability of Indicators Over Time (2019-2023)",
      x = "Year",
      y = "Cluster Benchmarked Indicators",
      fill = "Availability Status",
      caption = "Note: Indicator availability across clusters may differ based on how often the data source is updated. 
For a deeper understanding, please consult Table <#> to gain more insight into the update cycles."
    ) +
    scale_fill_manual(
      values = c("Full Access" = "#58d68d", "No Access" = "#cd6155"),  
      breaks = c("Full Access", "No Access"),
      labels = c("Full Access", "No Access")
    )
}

# Define UI for the application
ui <- fluidPage(
  
  titlePanel("Indicator Availability Heatmap"),
  
  fluidRow(
    column(12, 
           h4("Objective: To monitor the availability of indicators over time across different countries."),
           br(),
           p(
             strong("This tool addresses the question: "),
             "What indicators exist for a given country?"
           )
    )
  ),
  
  # Sidebar layout
  sidebarLayout(
    sidebarPanel(
      
      # Dropdown for selecting country name
      selectInput("country_name_input", "Select Country:",
                  choices = unique(ctf_dynamic_clean$country_name)),
      
      # Dropdown for selecting family name
      selectInput("family_name_input", "Select Family Name:",
                  choices = unique(ctf_dynamic_clean$family_name))
      
    ),
    
    # Main panel to display the heatmap
    mainPanel(
      plotOutput("heatmap_plot")
    )
  )
)

# Define server logic to plot the heatmap
server <- function(input, output) {
  
  # Reactive expression to generate the plot based on selected inputs
  output$heatmap_plot <- renderPlot({
    
    # Generate the heatmap for selected country and family
    generate_availability_heatmap(ctf_dynamic_clean, input$country_name_input, input$family_name_input)
    
  })
}

# Run the application
shinyApp(ui = ui, server = server)

```




