---
title: "CLIAR dashboard Coverage Report (2000-2024) - DRAFT"
date: December 4, 2005
output:
  html_document:
    theme: united
    toc: yes
    toc_float:
      collapsed: false
---

-   Input: `data/output/coverage_report_full_for_analysis.rds`

-   Output: `data/output/coverage_report.Rmd`

```{r set-up, include = FALSE}
# This script generates the consolidated report on coverage by country and CLIAR indicator. It imports, processes and visualizes the data coverage and more importantly, explores at a family level the areas of improvement to tackle data deserts - data poverty.

# Load in the funs.R file 
source(
  here("funs_coverage.R")
)

### Theme: https://bookdown.org/yihui/rmarkdown/pdf-document.html

library(ggrepel)
library(forcats)
library(RColorBrewer)


theme_set(
  theme_minimal() +
  theme(
    # text = element_text(family = "Segoe UI Semibold"),
    axis.text.x = element_text(size = 9, angle = 45, hjust = .5),
    axis.text.y = element_text(size = 12),
    plot.title = element_text(size = 20, face = "bold"),
    plot.subtitle = element_text(size = 14),
    plot.background = element_blank(),
    plot.caption = element_text(hjust = 0, size = 10),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(), 
    legend.position = "none")
  )

# Set global confition for labels. Source: https://ggrepel.slowkow.com/articles/examples.html
options(ggrepel.max.overlaps = Inf)

```

## Import data

```{r read in, include = FALSE}
# The data imported here has been processed in the 03-process-data.Rmd script
coverage_long_panel <- read_rds(
  here("data", "output","coverage_report_full_for_analysis.rds" )
)

coverage_long_panel <- read_rds(
  here("data", "output","coverage_ctf_for_analysis.rds" )
)
```

## Motivation

Context: CLIAR dashboard, Sources feed framework, best administrative data available in the world not a balanced panel and opportunities for improvement

Sample size detaills: countries and indicator level, time frame

Objective:Data poverty overview at a country level

## I. Density Av Coverage

### a. Region

```{r,  fig.height= 8, fig.width=12}
# Apply group_average function and specifying
# the following arguments: data, group, subgroup, quantity
coverage_regional <- coverage_long_panel |>
  select(region_short, country_code, available_share) |>
   group_average(region_short, country_code, available_share)

coverage_regional %>%
  ggplot(aes(x = group_av, fill = region_short)) +
  geom_density(alpha = 0.5) + 
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Regions?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Family Name") +
  facet_grid(~region_short) +
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  coord_flip() +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100))

```

### b. Income

```{r, fig.height= 8, fig.width=12}
coverage_income <- coverage_long_panel |>
  select(income_group, region_short, country_code, available_share) |>
  group_facet_average(income_group, region_short, country_code, available_share) |>
  filter(!is.na(income_group))

coverage_income %>%
  ggplot(aes(x = group_av, fill = income_group)) +
  geom_density(alpha = 0.75) + 
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
    geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Income Groups?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Income Group") +
  facet_grid(~income_group) + 
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_color_brewer(palette = "Spectral") +
  coord_flip() +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100)) 

```

### c. Family

```{r,  fig.height= 8, fig.width=12}
coverage_family <- coverage_long_panel |>
  select(family_name, region_short, country_code, available_share) |>
  group_facet_average(family_name, region_short, country_code, available_share) |>
  filter(!is.na(family_name))

coverage_family %>%
  ggplot(aes(x = group_av, fill = family_name)) +
  geom_density(alpha = 0.75) +
  geom_vline(xintercept = 50, linetype = "solid", linewidth = 1, color = "grey") + 
  geom_vline(xintercept = 25, linetype = "dotted", linewidth = 1, color = "grey") +
  geom_vline(xintercept = 75, linetype = "dotted", linewidth = 1, color = "grey") +
    geom_boxplot(aes(x = group_av, y = 0), 
               color = "grey3", 
               fill = "white", 
               width = 0.1, 
               alpha = 0.2, 
               position = position_dodge(width = 0.5)) +  
  geom_jitter(aes(x = group_av, y = 0), 
              color = "grey3", 
              width = 0.1, 
              height = 0,  
              alpha = 0.5) +  
  ggtitle("How Does Data Coverage Vary Across Clusters?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
  labs(x = "Average Coverage (%)", y = "Density", fill = "Family Name") +
  facet_wrap(~family_name, nrow = 2) + 
  scale_fill_brewer(palette = "Paired") +
  coord_cartesian(ylim = c(0, 1)) +
  scale_x_continuous(breaks = c(0, 25, 50, 75, 100)) +
  coord_flip()  


```

## II. Country: Av Coverage

### a. Region

Which is the country data coverage within the regions?

```{r, fig.height= 8, fig.width= 12}
coverage_regional %>% 
  group_by(country_code) %>% 
  ggplot(aes(x = region_short,
            y = group_av,
            color = region_short)) +
   geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
   geom_segment(aes(x = region_short,
                    xend = region_short,
                    y = group_min,
                    yend = group_max),
                    linetype = "solid",
                    linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, 
                    segment.color = "grey", 
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
   ggtitle("How Does Data Coverage Vary within the Regions?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators") +
   labs(
     x = "Region",
     y = "Average Values",
     shape = "Values",
     color = "Region",
     hjust = 0
   ) +
   coord_cartesian(ylim = c(0, 100)) +
   scale_color_brewer(palette = "Paired")
```

MENA has great coverage at an indicator level. What happens is we digg into income level and families

```{r}
### NEXT STEPS REGION
# Questions to answer:
# Number of countries per decile?
### mutate to bins and count by category
```

### b. Income

Are there data deserts at a income level?

```{r, fig.height= 8, fig.width= 12}
# Income group
coverage_income %>% 
  ggplot(aes(x = income_group,
             y = group_av,
             color = income_group)) +
  geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
  geom_segment(aes(x = income_group,
                   xend = income_group,
                   y = group_min,
                   yend = group_max),
                   linetype = "solid",
                   linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, # Padding around the label
                    segment.color = "grey", # Color of the connecting line
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
  ggtitle("How Does Data Coverage Vary within Income Groups?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators"
  ) +
  labs(
    x = "Region",
    y = "Average Values",
    shape = "Values",
    color = "Region",
    hjust = 0
  ) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(palette = "Dark2")



```

Here is the same group, bus colored by region

```{r, fig.height= 8, fig.width= 12}
coverage_income %>% 
  ggplot(aes(x = income_group,
             y = group_av,
             color = region_short)) +
  geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
  geom_segment(aes(x = income_group,
                   xend = income_group,
                   y = group_min,
                   yend = group_max),
                   linetype = "solid",
                   linewidth = 5) +
   geom_label_repel(aes(label = country_code, y = group_av), 
                    size = 3, 
                    box.padding = 0.25, # Padding around the label
                    segment.color = "grey", # Color of the connecting line
                    nudge_y = 0.1, 
                    direction = "both", 
                    hjust = 0.5) +  
    ggtitle("How Does Data Coverage Vary within Income Groups from a Regional perspective?",
    subtitle = "Average Country-Level Coverage to CLIAR Indicators"
  ) +
  labs(
    x = "Region",
    y = "Average Values",
    shape = "Values",
    color = "Region",
    hjust = 0
  ) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(palette = "Paired")
 


```

### c. Family

```{r eval=FALSE, fig.height=18, fig.width=, include=FALSE}
# Families
coverage_family %>% 
  group_by(family_name) %>% 
  ggplot(aes(x = family_name,
             y = group_av,
             color = family_name)) +
  geom_hline(yintercept = 50,
              linetype = "solid", 
              linewidth = 1.5,
              color = "grey") +
  geom_segment(aes(x = family_name,
                   xend = family_name,
                   y = group_min,
                   yend = group_max),
                   linetype = "solid",
                   linewidth = 5) +
  geom_text_repel(aes(label = country_code),
                  size = 2.5, hjust = 2, nudge_y = 0.25, 
                  box.padding = 0.25, point.padding = 0.1) +
  
  ggtitle("Data Coverage: Regional Averages by Family",
    subtitle = "Min to Max Average Coverage"
  ) +
  labs(
    x = "Region",
    y = "Average Values",
    shape = "Values",
    color = "Region",
    hjust = 0
  ) +
  facet_wrap(~family_name) +
  coord_cartesian(ylim = c(0, 100)) 

```

## III. Indicator coverage: Cluster specific

-Work in progress- 

How extensive is the country coverage by indicator for the CTF calculations?

Steps:

a)  BINS CLASSIFICATION: 0-25-50-75-100 --- semaforo colorcode
b)  Build function: filter country - viz by indicator - family facet

Corr? region x income

```{r}
### Bins
indicators_bins <- coverage_long_panel %>%
  mutate(
    ctf_years = case_when(
      between(available_share, 0, 20) ~ "1",
      between(available_share, 21, 40) ~ "2",
      between(available_share, 41, 60) ~ "3",
      between(available_share, 61, 80) ~ "4",
      between(available_share, 81, 100) ~ "5",
      TRUE ~ "Other"
    )
  ) %>%
  glimpse()

#Look g=for duplicated values
  
```

```{r}
### Visual
indicators_bins %>% tabyl(family_name, ctf_years)
#

```

```{r}
### Function

```
