---
title: 'Data Quality Control: Exclusion'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: word_document
---

```{r setup, include = FALSE}
packages <- 
  c(
    "tidyverse",
    "here",
    "testthat",
    "naniar",
    "knitr",
    "tidytext"
  )

pacman::p_load(
  packages, 
  character.only = TRUE
)

theme_set(
  theme_minimal(
    base_size = 20
  )
)

opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, 
  fig.width = 10, fig.height = 14, dpi = 300
)
```

```{r readin, include = FALSE}
wb_country_groups <- read_rds(
  here("..", "data", "final", "wb_country_list.rds")
) |>
  # extract only regions
  distinct(
    country_code, country_name, .keep_all = TRUE 
  ) |>
  select(
    country_code,
    country_name,
    region = group
  )

full_data <- read_rds(
  here(
    "..",
    "data",
    "final",
    "compiled_indicators.rds"
  )
) |>
  left_join(
    wb_country_groups,
    by = c("country_code", "country_name")
  )

# variable definitions
db_variables <- read_rds(
   here(
    "..",
    "data",
    "final",
    "db_variables.rds"
  )
)

# import variable definitions
source(
  here("vars-control.R")
)
```

# Quality checks: Coverage Criteria

- Inputs:
  - `data/final/wb_country_list.rds`
  - `data/final/compiled_indicators.rds`
  - `data/final/db_variables.rds`
      
- Outputs:
  - Exclusion Diagnostics

# Introduction:

The objective of this quality check is to verify how different exclusion criteria affect availability of our indicators. In particular, we are interested in the application of the following criteria for exclusion:

  1. **Discontinued Series**. We exclude any variables that have been discontinued. For that, we verify if there has been variation in the update frequency of a variable. For example, if a variable that was annual previously is no longer updated, we may drop it.
  2. **Low country coverage**. We exclude variables that over the past 5 years have data on fewer than 100 countries (we can debate whether 100 is the right number but we need a number). The indicator must cover at least once over the past 5 years (2018-2022) each of the 100 countries.
    2.a. As an exception to the previous rules we will include variables that that cover 50 to 100 countries over the past 5 years that cover all the bank regions (excluding high income). This will eliminate OECD type of data but would keep PEFA data. The OECD is normally missing in PEFA and ES because these datasets normally focus on client countries only.
  3. **Minimal threshold**. We include only variables that have at least 2 years of data (not per country but overall). At least 10 countries per year.
  
For each one of these criteria, we will produce the following indicators:

  1. The set of indicators selected for exclusion.
  2. Sensitivity to the exclusion criterion: cannot use correlation between original and modified CTF indicator, because dropped indicators fall out of sample. [To-Do].
  3. Change in missingness of data: Proportion of missingness, measured as the ratio of missing to number of elements (cells) in the dataset.


# 1. Discontinued Series

We define a series as discontinued if in the past 5 years, a variable has not been updated for any of the countries.

```{r discontinued}
build_missingness_table <- function(data, dimension, vars){
  # this function calculates the amount of missingness
  # of a particular indicator, across a dimension,
  # whether it be (1) a country or (2) a year
  missingness_table <- data |> 
    select(
      {{dimension}},
      any_of(vars)
    ) |> 
    group_by({{dimension}}) |> 
    miss_var_summary() |> 
    select(-n_miss) |> 
    ungroup()
  
  return(missingness_table)
}

complete_var_names <- function(data, dictionary){
  data |> 
    inner_join(
      dictionary |> select(variable, var_name, family_name),
      by = "variable"
    )
}

drop_indicators <- function(data, excluded_indicators){
  indicators_to_exclude <- excluded_indicators %>%
    pull(variable)
  
  pruned_data <- data |> 
    select(
      -any_of(indicators_to_exclude)
    )
  
  return(pruned_data)
}

# identify variables that have not been updated in the past 5 years
discontinued_indicators <- full_data |> 
  build_missingness_table(
    dimension = year,
    vars = vars_all
  ) |>
  filter(year > (2020 - 5)) |> 
  group_by(variable) |> 
  summarise(
    times_updated = sum(pct_miss != 100)
  ) |> 
  filter(
    times_updated == 0
  ) |> 
  complete_var_names(db_variables) |> 
  select(
    variable,
    var_name,
    family_name,
    times_updated
  )

kable(
  discontinued_indicators |> select(-variable),
  col.names = c("Variable", "Family Name", "Times Updated"),
  caption = "Discontinued Indicators in the Past 5 Years"
)
```

## Stress Test for Exclusion: Discontinued Series

```{r}
discontinued_prop_complete <- full_data |> 
  drop_indicators(discontinued_indicators) |> 
  naniar::prop_complete() |> 
  round(2)

full_prop_complete <- full_data |> 
  prop_complete()
```

We calculate the proportion of complete cases for the pruned dataset (excluding the discontinued indicators) and compare it to the original proportion of complete cases for the full data. We find that there is an increase in the proportion of complete cases by `discontinued_prop_complete - full_prop_complete`, from `r full_prop_complete` to `r discontinued_prop_complete`.

# 2. Low Country Coverage

We exclude variables that over the past 5 years have data on fewer than 100 countries (we can debate whether 100 is the right number but we need a number. Note that the number of countries included in the table are increasing over time. Why?). The indicator must cover at least once over the past 5 years (2018-2022) each of the 100 countries.

```{r low_country}
n_countries <- 162

calculate_country_and_region_coverage <- function(data, dictionary){
  data |> 
    summarise(
      across(
        c(any_of(vars_all)),
        ~ n_distinct(country_code[!is.na(.)]),
        .names = "{.col}__total_countries_covered"
      ),
      across(
        c(any_of(vars_all)),
        ~ n_distinct(region[!is.na(.)]),
        .names = "{.col}__total_regions_covered"
      )
    ) |> 
    # create a long-form table of all indicators, with
    # two columns (1) countries covered and (2) regions covered
    pivot_longer(
      cols = c(everything()),
      cols_vary = "slowest",
      names_to = c("variable", ".value"),
      names_pattern = "(\\w+)__(\\w+)"
    ) |> 
    # exclude indicators with less than 100 countries
    # and less than 5 regions covered
    filter(
      total_countries_covered < 100 &
        total_regions_covered < 5
    ) |>
    # inherits db_variables
    complete_var_names(dictionary) |> 
    select(
      variable, 
      var_name,
      family_name,
      total_countries_covered,
      total_regions_covered
    )
}

low_coverage_indicators <- full_data |> 
  # in the last 5 years
  filter(year > (2020 - 5)) |> 
  # compute total countries and regions covered for all vars
  # note that it excludes, per variable, all missing variables
  # and calculates distinct countries and regions
  calculate_country_and_region_coverage(
    dictionary = db_variables
  )

kable(
  low_coverage_indicators |> select(-variable),
  col.names = c("Variable", "Family Name", "Total Countries Covered", "Total Regions Covered"),
  caption = "Low Coverage Indicators in the Past 5 Years"
)
```

## Stress Test for Exclusion: Low Country Coverage

```{r}
low_coverage_prop_complete <- full_data |> 
  drop_indicators(low_coverage_indicators) |> 
  naniar::prop_complete() |> 
  round(2)
```

We calculate the proportion of complete cases for the pruned dataset (excluding the discontinued indicators) and compare it to the original proportion of complete cases for the full data. We find that there is an increase in the proportion of complete cases by `low_coverage_prop_complete - full_prop_complete`, from `r full_prop_complete` to `r low_coverage_prop_complete`.

# 3. Minimal Threshold

We exclude indicators that have less than 2 years of data (not per country but overall) and for each year covered, it covers less than 10 countries per year.

```{r minimal}
calculate_coverage <- function(data, grouping){
  # calculate coverage across year or country
  # if year, countries covered in that year
  # if country, years covered for that country
  if(grouping == "year"){
    value <- "country"
  } else{
    value <- "year"
  }
  
  data |> 
    group_by(
      across(any_of(grouping))
    ) |> 
    summarise(
      across(
        any_of(vars_all),
        n_complete
      )
    ) |> 
    pivot_longer(
      !year,
      names_to = "variable",
      values_to = paste0(value, "_coverage")
    )
}

calculate_minimal_threshold <- function(data, dictionary){
  data |> 
    filter(country_coverage >= 10) |> 
    group_by(variable) |> 
    summarise(
      year_coverage = n_distinct(year)
    ) |> 
    filter(year_coverage <= 2) |> 
    complete_var_names(dictionary) |> 
    select(variable, var_name, family_name, year_coverage)
}

minimal_threshold_indicators <- full_data |> 
  calculate_coverage("year") |> 
  calculate_minimal_threshold(
    dictionary = db_variables
  )

kable(
  minimal_threshold_indicators |> select(-variable),
  col.names = c("Variable", "Family Name", "Year Coverage"),
  caption = "Minimal Threshold Indicators"
)
```

## Stress Test for Exclusion: Minimal Threshold

```{r}
minimal_threshold_prop_complete <- full_data |> 
  drop_indicators(minimal_threshold_indicators) |> 
  naniar::prop_complete() |> 
  round(2)
```

We calculate the proportion of complete cases for the pruned dataset (excluding the discontinued indicators) and compare it to the original proportion of complete cases for the full data. We find that there is an increase in the proportion of complete cases by `minimal_threshold_prop_complete - full_prop_complete`, from `r full_prop_complete` to `r minimal_threshold_prop_complete`.
