---
title: "Data Quality Control: Missingness"
output: word_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

# Quality checks: Missingness

- Inputs:
  - `data/final/wb_country_list.rds`
  - `data/final/compiled_indicators.rds`
  - `data/final/db_variables.rds`
      
- Outputs:
  - Missingness visualizations

## Load packages

```{r, include = FALSE}
packages <- 
  c(
    "tidyverse",
    "here",
    "testthat",
    "naniar",
    "tidytext"
  )

pacman::p_load(
  packages, 
  character.only = TRUE
)

theme_set(
  theme_minimal(
    base_size = 20
  )
)

knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, 
  fig.width = 10, fig.height = 14, dpi = 300
)
```

## Read-in Data

```{r, include = FALSE}
wb_country_groups <- read_rds(
  here("..", "data", "final", "wb_country_list.rds")
) |>
  # extract only regions
  distinct(
    country_code, country_name, .keep_all = TRUE 
  ) |>
  select(
    country_code,
    country_name,
    region = group
  )

full_data <- read_rds(
  here(
    "..",
    "data",
    "final",
    "compiled_indicators.rds"
  )
) |>
  left_join(
    wb_country_groups,
    by = c("country_code", "country_name")
  )

# variable definitions
db_variables <- read_rds(
   here(
    "..",
    "data",
    "final",
    "db_variables.rds"
  )
)

# import variable definitions
source(
  here("vars-control.R")
)
```

## Data Quality Control

We test the data for the following metrics:

  - Uniqueness of country-year observations.
  - Missingness of indicators.
  - Missingness of indicators over time.
  - Missingness of indicators for a country.

## 1. Uniqueness of country-year 

```{r}
n_unique_obs <- full_data |> 
  distinct(
    country_name,
    country_code,
    year
  ) |> 
  nrow()

test_that("uniqueness of country-year",{
  expect_success(
    expect_equal(
      n_unique_obs,
      nrow(full_data)
    )
  )
})
```

## 2. Heatmap of Missingness

```{r}
indicators_missingness_by_country <- full_data |> 
  select(
    country_name,
    any_of(vars_all)
  ) |> 
  group_by(country_name) |> 
  miss_var_summary() |> 
  select(-n_miss) |> 
  pivot_wider(
    id_cols = country_name,
    names_from = variable,
    values_from = pct_miss
  ) |> 
  ungroup() |> 
  arrange(
    desc(country_name)
  )

matrix_missingness_by_country <- indicators_missingness_by_country |> 
  select(-country_name) |> 
  as.matrix()

rownames(matrix_missingness_by_country) <- indicators_missingness_by_country |> 
  pull(country_name)

heatmap(matrix_missingness_by_country, Colv = NA, Rowv = NA)
```


## 3. Missingness of indicators.
  
```{r}
rename_from_dictionary <- function(data, dictionary){
  # function to rename variables from dictionary
  var_tibble <- tibble(
    variable = colnames(data)
  )
  
  # extract only variables contained in the data
  vars_in_data <- dictionary |> 
    inner_join(
      var_tibble,
      by = c("variable")
    )
  
  vars_variable <- vars_in_data |> 
    pull(variable)
  
  vars_complete_name <- vars_in_data |> 
    pull(var_name)
  
  vars_dictionary <- vars_variable |>
    set_names(
      vars_complete_name
    )
  
  data |>
    rename(!!vars_dictionary)
}

full_data_indicators <- full_data |> 
  select(
    any_of(vars_all)
  ) |>
  rename_from_dictionary(db_variables)

gg_miss_var(
  full_data_indicators,
  show_pct = TRUE
) +
  labs(
    title = "Missingness by Indicators, Full Sample (2008-2020)",
    caption = "Percentage of all observations (country-year)"
  )
```

## 4. Missingness by year.

```{r}
select_indicators_by_family <- function(data, family, grouping = NULL){
  # a function that takes each variable family
  # and computes missingness of each indicator
  # input: db_variables
  selected_vars <- db_variables |> 
    filter(family_name == family) |> 
    pull(variable)
  
  vars_dictionary <- c(
    selected_vars
  ) |> 
    set_names(
      db_variables |> 
      filter(family_name == family) |> 
      pull(var_name)
    )
  
  selected_data <- data |> 
    select(any_of(selected_vars), {{grouping}}) |> 
    rename(
      !!vars_dictionary
    )
  
  return(selected_data)
}

var_by_family <- db_variables |> 
  select(
    var_name,
    variable,
    family_name
  )

var_families <- db_variables |> 
  distinct(family_name) |> 
  pull()

plots_missingness_by_family <- var_families |> 
  map(
    ~ select_indicators_by_family(
      data = full_data,
      family = .x,
      grouping = year
    ) |> 
      gg_miss_var(
        facet = year,
        show_pct = TRUE
      ) +
      labs(
        title = "Missingness by Indicators by Year,\n Full Sample (2008-2020)",
        caption = "Percentage of all observations (country-year)"
      )
  ) |> 
  set_names(var_families)

plots_missingness_by_family
```

## 5. Missingness by country.

```{r}
full_data |> 
  select(
    any_of(vars_all), country_name, region
  ) |>
  add_prop_miss() |>
  group_by(region, country_name) |>
  summarise(
    mean_prop_miss = mean(prop_miss_all),
    .groups = "drop"
  ) |>
  mutate(
    country_name = reorder_within(country_name, mean_prop_miss, region)
  ) |>
  ggplot(
    aes(mean_prop_miss, reorder(country_name, mean_prop_miss))
  ) +
  geom_col(
    width = 0.5
  ) +
  scale_y_reordered() +
  scale_x_continuous(
    labels = scales::percent_format(),
    limits = c(0, 1)
  ) +
  facet_wrap(
    vars(region),
    scales = "free_y",
    ncol = 2
  ) +
  labs(
    x = "Average Missingness by Country",
    y = "Country",
    title = "Missingness by Country, Full Sample (2008-2020)",
    caption = "Average Proportion of Missing Indicators"
  )
```

