--- 
title: "Data processing"
author: "Luiza Andrade, Serena Cocciolo, Eric Braian Arias, Gabriel Vaz de Melo"
site: "bookdown::bookdown_site"
output: 
  bookdown::gitbook
config:
    toc:
      collapse: subsection
    download: ["pdf"] 
documentclass: book
link-citations: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(warning =  FALSE, message = FALSE, skimr_include_summary = FALSE)
```

# About

This notebook processes the data used in G-BID.

## Render book

You can render the HTML version of this example book without changing anything:

1. Find the **Build** pane in the RStudio IDE, and

1. Click on **Build Book**, then select your output format, or select "All formats" if you'd like to use multiple formats from the same book source files.

Or build the book from the R console:

```{r, eval=FALSE}
bookdown::render_book()
```

To render this example to PDF as a `bookdown::pdf_book`, you'll need to install XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.
