# Create spatial data

- Inputs:
  - `data/final/closeness_to_frontier.rds`
  - `data/final/compiled_indicators.rds`
  - `data/raw/WB_countries_Admin0_lowres.geojson`, obtained from https://datacatalog.worldbank.org/int/search/dataset/0038272 on September 1, 2022
  - `data/raw/WB_disputed_areas_Admin0_10m_lowres.geojson`, obtained from https://datacatalog.worldbank.org/int/search/dataset/0038272 on September 1, 2022
  
- Output:
  - `data/final/indicators_map.rds`
  
## Packages 

```{r}
packages <-
  c(
    "tidyverse",
    "rmapshaper",
    "sf",
    "here"
  )

pacman::p_load(
  packages,
  character.only = TRUE
)
```

## Input data 

```{r}
ctf <-
  read_rds(
    here(
      "..",
      "data",
      "final",
      "closeness_to_frontier.rds"
    )
  )

raw_indicators <-
  read_rds(
    here(
      "..",
      "data",
      "final",
      "compiled_indicators.rds"
    )
  )
```

## Official WB maps 

```{r}
world_map <-
  read_sf(
    here(
      "..",
      "data",
      "raw",
      "WB_countries_Admin0_lowres.geojson"
    )
  )

disputed_areas <-
  read_sf(
    here(
      "..",
      "data",
      "raw",
      "WB_disputed_areas_Admin0_10m_lowres.geojson"
    )
  )
```

# Clean maps 

```{r}
disputed_areas <-
  disputed_areas %>%
  transmute(country_code = str_trim(WB_A3)) %>%
  filter(
    !is.na(country_code),
    country_code != ""
  )

world_map <-
  world_map %>%
  select(country_code = WB_A3) 

world_map <-
  world_map %>%
  bind_rows(
    disputed_areas
  ) %>%
  ms_simplify(
    keep = 0.04,
    keep_shapes = T
  )

st_crs(world_map) <- "WGS84"

world_map <-
  world_map %>%
  st_transform("+proj=robin")

```


# Combine maps and data

## Closeness to frontier

```{r}
ctf <-
  ctf %>%
  pivot_longer(
    cols = db_variables$variable,
    values_to = "ctf"
  ) %>%
  mutate(
    bin = case_when(
      ctf < .2 ~ "0.0 - 0.2",
      ctf < .4 ~ "0.2 - 0.4",
      ctf < .5 ~ "0.4 - 0.6",
      ctf < .8 ~ "0.6 - 0.8",
      ctf <= 1 ~ "0.8 - 1.0" 
    )
  ) %>%
  pivot_wider(
    id_cols = starts_with("country_"),
    names_from = name,
    values_from = c(bin, ctf)
  )
```

## Raw data

```{r}
raw <-
  raw_indicators %>%
  pivot_longer(
    cols = 4:ncol(.)
  ) %>%
  filter(!is.na(value)) %>%
  group_by(country_name, country_code, name) %>%
  filter(year == max(year)) %>%
  ungroup %>%
  pivot_wider(
    values_from = c(value, year),
    names_from = name
  )

map <-
  world_map %>%
  left_join(
    raw
  ) %>%
  left_join(
    ctf
  )
```


# Save datasets

```{r}
map %>%
  write_rds(
    here(
      "..",
      "data",
      "final",
      "indicators_map.rds"
    )
  )
```
