# Process API data

- Input: `data/final/db_variables.rds`
- Output: `data/clean/original_data.rds`
 
 
```{r}
packages <- 
  c(
    "tidyverse",
    "here",
    "data360r",
    "skimr"
  )

pacman::p_load(packages,
               character.only = TRUE)
```

## List indicators to retrieve

Governance indicators are calculated in a disaggregate manner, so we will import them separately, aggregate them, and combine with the other indicators.

```{r}
governance_data <- c(
  42099, # SOE board of directors independence (Mining)
  42100, # SOE board of directors independence (Oil & Gas)
  #42105, # SOE corporate governance practice (Mining)
  #42106, # SOE corporate governance practice (Oil & Gas)
  42161, # SOE-government transfers governance rule (Mining)
  42162, # SOE-government transfers governance rule (Oil & Gas)
  42092, # SOE annual report disclosure (Oil & Gas)
  42091, # SOE annual report disclosure (Mining)
  42107, # SOE financial audit requirement (Mining)
  42108, # SOE financial audit requirement (Oil & Gas)
  42141, # SOE report legislative review requirement (Mining)
  42142  # SOE report legislative review requirement (Oil & Gas)
)
```

All other indicators are coming from the list of selected indicators.

```{r}
# Get data360
indicator_ids <-
  db_variables %>%
  filter(
    !is.na(api_id),
    !(api_id %in% governance_data)
  ) %>%
  pull(api_id) %>%
  split(
    ceiling(
      seq_along(.)/10
    )
  )
```

```{r}

datalist = list()

for(i in 1:length(indicator_ids)){
  datalist[[i]] <- 
    get_data360(
           indicator_id = c(indicator_ids[[i]]),
           output_type = 'long'
          )
}

data_api_raw = do.call(dplyr::bind_rows , datalist)
```


## Extract and aggregate governance data

The code below imports the data from the API

```{r}
data_api_governance <- 
  get_data360(
    indicator_id = governance_data,
    output_type = 'long'
  )
```

These indicators are calculated separately for the mining and oil & gas industries. We are interested in a more aggregate measure, so we will take the average of the two by country and period.

```{r}
data_api_governance <- 
  data_api_governance %>%
  # Harmonize indicator name across industries
  separate(
    Indicator,
    into = c("Indicator"),
    sep = " [(]"
  ) %>%
  # Group observations to be combined
  group_by(
    `Country ISO3`,
    `Country Name`,
    Indicator,
    Period
  ) %>%
  # Take the average
  summarise(
    Observation = mean(Observation, na.rm = T)
  ) %>%
  mutate(
    Indicator = str_replace_all(Indicator, "-", " ")
  )
```

## Combine all indicators

```{r}
data_api <-
  bind_rows(
    data_api_raw,
    data_api_governance
  ) %>%
  mutate(Indicator = str_trim(Indicator))

metadata_api_gov <-
  get_metadata360(
    site = "gov", 
    metadata_type = "indicators"
  )

metadata_api_tc <-
  get_metadata360(
    site = "tc", 
    metadata_type = "indicators"
  ) 

metadata_api <-
  metadata_api_gov %>%
  bind_rows(metadata_api_tc) %>%
  transmute(
    api_id = id,
    Indicator = str_trim(name)
  ) %>%
  filter(api_id %in% db_variables$api_id)

data_api <-
  data_api %>%
  left_join(metadata_api) 
```

# Cleaning API data ----

```{r}
data_api_clean <- 
  data_api %>%
  unique %>%
  # Remove country-year-indicators with no data
  filter(!is.na(Observation)) %>%
  # Make variable names more manageable
  rename(
    country_code = `Country ISO3`,
    country_name = `Country Name`,
    value = Observation
  ) %>%
  # Sort
  arrange(
    Indicator, country_name
  ) %>%
  # Same values are for a period, not a single year. We turn it into a year by taking the value of the last year in the period
  separate(
    Period,
    into = c("Year1", "year"),
    sep = "-", 
    remove = F
  ) %>%
  mutate(
    year = ifelse(
      is.na(year),
      as.character(Period),
      year
    )
  ) %>%
  # Hiring and firing has both year and period level data. We will keep only year level data
  filter(!(api_id == 657 & str_detect(Period, "-"))) %>%
  select(
    -c(`Subindicator Type`, Period, Year1)
  ) %>%
  complete(
    nesting(country_code, country_name),
    nesting(Indicator, year),
    fill = list(value = NA)
  ) %>%
  unique

# Check that data is uniquely identifed
assert_that(
  (data_api_clean %>% select(country_code, year, Indicator) %>% n_distinct()) ==
    (data_api_clean %>% nrow)
)
```

# Add cleaned variable labels

These variable labels were manually cleaned by the G-BID team

```{r}
var_names <-
  db_variables %>%
  select(
    var = variable,
    api_id
  ) %>%
  filter(!is.na(api_id))

data_api_labeled <-
  data_api_clean %>%
  filter(
    !is.na(value),
    !is.null(value)
  ) %>% 
  left_join(
    var_names,
    by = "api_id"
  )
```

# Put data into panel format

```{r}
data_wide <-
  data_api_labeled %>%
  mutate(
    var = case_when(
      Indicator == "SOE board of directors independence" ~ "soe_board",
      Indicator == "SOE government transfers governance rule" ~ "soe_government",
      Indicator == "SOE annual report disclosure" ~ "soe_annual_report",
      Indicator == "SOE financial audit requirement" ~ "soe_financial",
      Indicator == "SOE report legislative review requirement" ~ "soe_report_legislative",
      TRUE ~ var
    )
  ) %>%
  pivot_wider(
    id_cols = c(country_name, country_code, year),
    names_from = var
  ) %>%
  filter(
    year >= 1950   # variable e_p_polity has values since 1800, filter to reduce # of rows
  ) %>%
  mutate(
    country_code = as.character(country_code),
    year = as.character(year)
  ) %>%
  select(
    country_code,
    year,
    all_of(vars_api)
  )

# Drop partial data ----
rm(datalist, data_api_raw, data_api_governance, indicator_ids, i)

write_rds(
  data_wide,
  here(
    "..",
    "data",
    "clean",
    "api_data.rds"
  )
)

```
