---
title: "Data Quality Control: Metadata on Coverage"
output: html_document
date: '`r format(Sys.Date(), "%B %d, %Y")`'
---

```{r setup, include = FALSE}
library(dplyr)
library(ggplot2)
library(here)
library(testthat)
library(naniar)
library(tidyr)
library(tidytext)
library(readr)
library(pointblank)
library(janitor)
library(DT)
library(scales)

# note that echo has to be set TRUE to display pointblank output
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, 
  fig.width = 10, fig.height = 14, dpi = 300
)

validate_rmd()
```

```{r funs, include = FALSE}
calculate_coverage <- function(indicator, id) {
  coverage_id <- n_distinct({{id}}[!is.na(indicator)])
  
  return(coverage_id)
}

flag_continued <- function(indicator, year_id, ref_year = 2015){
  # this function returns a flag for discontinued series
  # 1. compute the number of times the indicator is measured
  # since a reference year
  times_updated <- length(indicator[{{year_id}} >= ref_year & !is.na(indicator)])
  
  flag_continued <- if_else(times_updated > 0, 1, 0)
  
  return(flag_continued)
}

flag_country <- function(indicator, country_id, year_id, ref_year = 2015){
  # this function returns a flag for the low country coverage
  # 1. compute the number of distinct country ids for indicators
  # if they are not missing and more recent than a reference year
  country_coverage <- n_distinct({{country_id}}[{{year_id}} >= ref_year & !is.na(indicator)])
  
  flag_country <- if_else(country_coverage >= 100, 1, 0)
  
  # still need to add the exception to the rule
  
  return(flag_country)
}

flag_minimum_coverage <- function(indicator, country_id, year_id){
  # this function returns a flag for countries with less than minimum coverage:
  # defined as less than two years with at least 100 countries covered
  # 1. create a table with all relevant variables
  country_coverage <- tibble(
    indicator = indicator,
    country = country_id,
    year = year_id
  )
  
  # 2. calculate by year the number of distinct countries
  # and only maintain years where at least 10 countries are covered
  minimum_country_coverage <- country_coverage |> 
    filter(!is.na(indicator)) |> 
    group_by(year) |> 
    summarise(
      country_coverage = n_distinct(country)
    ) |> 
    filter(
      country_coverage >= 10
    )
  
  # return a flag 1 if more than two years (nrows) are available for that indicator
  flag_minimum_coverage <- if_else(nrow(minimum_country_coverage) >= 2, 1, 0)
}
  
calculate_time_range <- function(time_id){
  year_range <- paste0(min({{time_id}}, na.rm = TRUE), "-", max({{time_id}}, na.rm = TRUE))
  
  return(year_range)
}

compute_coverage <- function(data, country_id, year_id){
  ref_year <- 2018
  
  data_coverage <- data |> 
    # compute (1) number of distinct country codes
    # (2) range of years covered
   summarise(
      across(
        c(
          everything()),
          list(
            country_coverage = ~ calculate_coverage(.x, {{country_id}}),
            year_coverage = ~ calculate_coverage(.x, {{year_id}}),
            flag_continued = ~ flag_continued(.x, {{year_id}}),
            flag_country = ~ flag_country(.x, {{country_id}}, {{year_id}}),
            flag_minimum_coverage = ~ flag_minimum_coverage(.x, {{country_id}}, {{year_id}}),
            year_range = ~ calculate_time_range({{year_id}}),
            percent_complete_records = ~ percent(prop_complete(.x)),
            percent_complete_records_last_five = ~ percent(prop_complete(.x[{{year_id}} >= ref_year]))
          ),
          .names = "{.col}__{.fn}"
      )
  ) |>
  pivot_longer(
      cols = c(everything()),
      cols_vary = "slowest",
      names_to = c("indicator", ".value"),
      names_pattern = "(.*)__(.*)"
  ) |> 
    arrange(
      indicator
    ) |> 
    select(
      Indicator = indicator,
      `Country Coverage` = country_coverage,
      `Year Coverage` = year_coverage,
      `Flag Discontinued` = flag_continued,
      `Flag Low Country Coverage` = flag_country,
      `Flag Minimum Coverage` = flag_minimum_coverage,
      `Year Range` = year_range,
      `Percentage of Complete Records` = percent_complete_records,
      `Percentage of Complete Records in Last Five Years` = percent_complete_records_last_five
    )
  
  return(data_coverage)
}
```

# Introduction:

This document is a subset of the `data-quality-control-import.Rmd` file. It provides a simplified protocol for data validation when manually importing data into CLIAR. It provides metadata on the coverage of indicators in a scalable way.

Please place this file into a folder, containing all data sources to be imported into CLIAR. Each data source should have a separate folder, and stored into a csv file. You may specify the csv files in a vector, provided below.

The goal is to mitigate the following risk:

  1. Low data quality, measured in terms of country and year coverage.

Quantitative Review:

In this section we compute a set of diagnostics that assess the coverage of the dataset indicators, for each data source. These diagnostics are:
  1. Country Coverage,
  2. Year Range,
  3. Year Coverage, and
  4. Proportion of Complete Records.
  5. Additionally, we introduce the following flags:
    5.a. **Continuity**. We verify that there have been updates in the data for the past five years (2015 in the Global Dashboard).
    5.b. **Country Coverage**. The indicator must cover at least once over the past 5 years (2015-2020) each of the 100 countries.
      5.b.1. As an exception to the previous rules we will include variables that that cover 50 to 100 countries over the past 5 years that cover all the bank regions (excluding high income). This will eliminate OECD type of data but would keep PEFA data. The OECD is normally missing in PEFA and ES because these datasets normally focus on client countries only (this can only take place once we have region information, using the `countrycode` package.)
    5.c. **Year Coverage**. We include only variables that have at least 2 years of data (not per country but overall). Additionally, for each year to count, coverage must be of at least 10 countries.

This section provides a set of diagnostic of coverage for all indicators.

```{r input}

```

```{r transformation}
# harmonize country names

# convert into tidy data

# place all datasets into a named list
```

```{r coverage}
# specify country and year id's with respect to the clean names
dataset_coverage <- dataset_clean |> 
  compute_coverage(
    country_id = country_code,
    year_id = year
  )
```

```{r loading}
write_csv
```
