# Clean list of contries

- Inputs:
  - `data/output/compiled_indicators.rds`
  - `data/input/wb/CLASS.xlsx`, obtained from https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups on September 1, 2022
  - `data/input/wb/group_list.csv`, input by the research team to list relevant groups
  - `data/output/grouping_country_income_and_region_updated.rds`, complementary list for groups in the case of splitting SSA into AFW and AFE
      
- Outputs:
  - `data/final/wb_country_list.rds`
  - `data/final/wb_country_groups.rds`

## Inputs

```{r}
  indicators <-                                                       
      read_rds(
      here(
        "data",
        "output",
        "compiled_indicators.rds"
      )
    )

  group_list <-
    read_csv(
      here(
        "data",
        "input",
        "wb",
        "group_list.csv"
      )
    )

  country_list <- read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "compositions"
    ) %>%
    transmute(
      country_code = WB_Country_Code,
      country_name = WB_Country_Name,
      group = WB_Group_Name,
      group_code = WB_Group_Code
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )

# read in world bank standard country codes and mutate them to be compatible
  region_list <-
    read_rds(
      here(
        "data",
        "output",
        "wb_country_list.rds"
      )
    )

### Updated region grouping
  region_list_complement <-
    read_rds(
      here(
        "data",
        "output",
        "grouping_country_income_and_region_updated.rds"
      )
    )
```

## Transform Region List for 2 Africas

```{r}
### Define the indexing regions
target_regions <- c("Africa Eastern and Southern", "Africa Western and Central")

region_list_updated <- country_list %>%
  # Add Abbreviations to AFE and AFE regions in one dataframe
  left_join(
    region_list_complement %>% 
      mutate(region_code = recode(region,
                                  "Africa Eastern and Southern" = "AFE",
                                  "Africa Western and Central" = "AFW",
                                  .default = region)) %>% 
      transmute(country_code, detailed_region = region, detailed_region_code = region_code),
    by = "country_code"
  ) %>%
  # Index SSF region to effectively reclassify it into AFE and AFW
  mutate(
    group_name      = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region, group_code),
    group_code = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region_code, group_code)
  ) %>%
  # Ensure that region_code follows the changes regions
  select(names(country_list)[1:2], group_name, group_code)
```

## Subset country list

The only relevant countries are those we have some data for

```{r}
country_list <-
  indicators %>%
  select(country_code) %>%
  unique %>%
  left_join(country_list)
```

## Subset groups

```{r}
country_list <-
  country_list %>%
  filter(
    group %in% group_list$group_name
  ) %>%
  unique

### Define the indexing regions
target_regions <- c("Africa Eastern and Southern", "Africa Western and Central")

country_list_updated <- country_list %>%
  # Add Abbreviations to AFE and AFE regions in one dataframe
  left_join(
    region_list_complement %>% 
      mutate(region_code = recode(region,
                                  "Africa Eastern and Southern" = "AFE",
                                  "Africa Western and Central" = "AFW",
                                  .default = region)) %>% 
      transmute(country_code, detailed_region = region, detailed_region_code = region_code),
    by = "country_code"
  ) %>%
  # Index SSF region to reclassify it into AFE and AFW
  mutate(
    group_name      = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region, group),
    group_code = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region_code, group_code)
  ) %>%
  # Ensure that region_code follows the changes regions
  select(names(region_list)[1:2], group_name, group_code)
```

## Add AFE anhd AFW to Region list

```{r}
group_list_updated <- group_list %>%
  # Remove the "Sub-Saharan Africa" row
  filter(group_name != "Sub-Saharan Africa") %>%
  # Append new rows with the desired groups and group_category "Region"
  bind_rows(
    tibble(
      group_name = c("Africa Eastern and Southern", "Africa Western and Central"),
      group_category = "Region"
    )
  ) %>% 
  arrange(group_category, group_name)
```

## Save datasets

Dataset with list of countries in our sample

```{r}
write_rds(
  country_list_updated,
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

write_rds(
  group_list_updated,
  here(
    "data",
    "output",
    "wb_country_groups.rds"
  )
)
```
