---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# REPRODUCIBILITY PACKAGE 

This script reproduces the data used to produce the CLIAR dashbaord. All you have to do is: 

- Please reach out to Public Institutions Data and Analytics Team for the input data which you should place in the `data/input` folder.
- Open the `code.Rproj` in the base directory of the ETL folder. 
- Simply click the knit button to the `README.Rmd` file. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

find_root <- function(filename = "renv.lock") {
  path <- normalizePath(getwd(), winslash = "/", mustWork = TRUE)
  while (!file.exists(file.path(path, filename))) {
    new_path <- dirname(path)
    if (new_path == path) stop(paste("Could not find", filename, "in any parent directory"))
    path <- new_path
  }
  return(path)
}

project_root <- find_root()

renv::restore(project = project_root)

pak_list <- c("tidyverse", "readxl", "here", "labelled", "haven", 
               "knitr", "assertthat", "tibble", "sf", "janitor",
               "stringr", "scales", "naniar", "countrycode",
               "purrr", "testthat")

lapply(pak_list, library, character.only = TRUE, quietly = TRUE)


source(here::here("funs.R"))
source(here::here("funs - original.R"))
source(here::here("funs_coverage.R"))

```

## Load List of selected indicators
```{r, echo = FALSE, warning = FALSE, message = FALSE}

db_variables <-
  read_excel(
    here(
      "data",
      "input",
      "cliar",
      "db_variables.xlsx"
    )
  ) |> 
  clean_names() |> 
  mutate(
    variable = make_clean_names(variable),
    var_name = str_to_sentence(var_name, locale = "en") # To Sentence
  )

write_rds(
  db_variables,
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)

description <- 
  function(x) {
    assign(
      x,
      db_variables %>%
        filter(family_name == x) %>%
        select(
          Indicator = var_name,
          Description = description,
          Source = source
        )
    )
  }

description <-
  lapply(
    unique(db_variables$family_name),
    description
  )

names(description) <- 
  unique(db_variables$family_name)

write_rds(
  description,
  here(
    "data",
    "output",
    "definitions.rds"
  )
)




```


## Process Data
```{r, echo = FALSE, warning = FALSE, message = FALSE}

# define list of variables
source(
  here("vars-control.R")
)

ref_year <- 2025

efi <- read_dta(
  here("data", "input", "efi", "2024", "GTMI_Fixed_Update_EFI360_1990_2024.dta") 
) ### Latest API extraction and FTMI patch implemented due to a bug [Github issue #326]

# Data availablke here: https://www.pefa.org/assessments/batch-downloads
# Methodology 2016 and national download
pefa <- read_csv(
        here("data", "input", "efi", "2024", "assessments_1730149268.csv")
) |>
  clean_names()
  

romelli <- read_dta(
  here("data", "input", "romelli", "CBIData_Romelli2022.dta")
) |>
  clean_names()

debt_transparency <- read_dta(
  here("data", "input", "debt_transparency", "debt_transparency_2021-2022.dta")
)

fraser <- read_xlsx(
  here("data", "input", "fraser", "2024", "efotw-2023-master-index-data-for-researchers-iso.xlsx")
) |> 
  clean_names() |> 
  slice(-c(1:2)) 

  
gfdb <- read_dta(
  here("data", "input", "gfdb", "GFDB_19902021.dta")
)

oecd_epl_regular <- read_csv(
  here("data", "input", "oecd", "epl_regular.csv")
)

oecd_epl_temporary <- read_csv(
  here("data", "input", "oecd", "epl_temporary.csv")
)

oecd_pmr <- read_dta(
  here("data", "input", "pmr", "PMR_2018.dta")
)

spi <- read_csv(
  here("data", "input", "spi", "2024", "SPI_index_labelled.csv")
) |> 
  clean_names() 

aspire <- read_dta(
  #Testing new ASPIRE pulled from Pros360 API
  here("data", "input", "aspire", "API_ASPIRE.dta")
  #VV Original Dataset
  #here("data", "input", "aspire", "ASPIRE performance indicators.dta")
)

rise <- read_dta(
  here("data", "input", "rise", "RISE_20102021.dta")
)


wdi <- read_dta(
  here("data", "input", "wdi", "2024", "wdi_19902023.dta")
)

vdem <- read_dta(
  here("data", "input", "vdem", "2024", "vdem_19902023.dta")
)


heritage <- read_dta(
  here("data", "input", "heritage", "2024", "heritage20122024.dta")
)

open_budget <- list.files(
    here("data", "input", "ibp"),
    full.names = TRUE
  ) |> 
    map_dfr(
      read_csv,
      col_select = c(ISO, year, obi)
    )

# read in world bank standard country codes and mutate them to be compatible
# with the other files
wb_country_list <- read_xlsx(
  here(
   "data",
    "input",
    "wb",
    "CLASS.xlsx"
    ),
    sheet = "Groups"
  ) |>
  transmute(
    country_code = CountryCode,
    country_name = CountryName,
    group = GroupName,
    group_code = GroupCode
  ) |> 
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )

# country income group and region
country_income_and_region <- read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "List of economies",
      n_max = 219
    ) |>
    transmute(
      country_code = Code,
      region = Region,
      income_group = `Income group`
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )

wblx <- read_dta(
  here("data", "input", "wbl", "WBL_19902022_CLIAR.dta")
)

wbl <- read_dta(
  here("data", "input", "wbl", "WBL_19902023_CLIAR.dta")
)

# note that North America is not included in this list
wb_regions <- c(
  "Africa Eastern and Southern",
  "Africa Western and Central",
  "East Asia & Pacific",
  "Europe & Central Asia",
  "Latin America & Caribbean",
  "Middle East & North Africa",
  "South Asia"
)

country_region_list <- wb_country_list |> 
  # this filter excludes Canada, Bermuda and USA
  filter(group %in% wb_regions) |> 
  select(country_code, region = group)

# Separate SSA into "Africa Eastern and Southern" and "Africa Western and Central",
country_income_and_region_updated <- country_income_and_region %>%
  left_join(country_region_list, by = "country_code", suffix = c("", "_new")) %>%
  mutate(region = if_else(region == "Sub-Saharan Africa", region_new, region)) %>%
  select(-region_new)

country_income_and_region_updated |> 
    write_rds(
      here(
        "data",
        "output",
        "grouping_country_income_and_region_updated.rds"
      )
    )


# 1. efi
#       For the EFI, first the name of enterprise survey variables is changed to 
#       be more consistent. Then a single PFM indicator is by taking the sum of
#       several GTMI variables. 

efi_clean <- efi |> 
  clean_names() |> 
  # fix enterprise surveys variable name
  rename_with(
    \(x) str_replace(x, "wb_survey", "wb_es_ic_frm"),
    .cols = starts_with("wb_survey")
  ) |> 
  # create PFM MIS indicator by summing over the following and rescaling:
  # GTMI_I-12       Is there an e-Procurement System in place? (foreign and domestic debt)
  # GTMI_I-13       Is there a Debt Management System (DMS) in place? (foreign and domestic debt)
  # GTMI_I-14       Is there a Public Investment Management System (PIMS) in place?
  # GTMI_I-8        Is there a Customs System in place?
  # GTMI_I-7        Is there a Tax Management Information System in place?
  # GTMI_I-6        Is there a TSA supported by FMIS to automate payments and bank reconciliation?
  # GTMI_I-5        Is there an operational FMIS in place to support core PFM functions?
  rowwise() |> 
  mutate(
    wb_gtmi_pfm_mis = sum(
      # wb_gtmi_i_12,
      wb_gtmi_i_13,
      wb_gtmi_i_14,
      wb_gtmi_i_8,
      wb_gtmi_i_7,
      wb_gtmi_i_6,
      wb_gtmi_i_5
    )
  ) |> 
  ungroup() |> 
  mutate(
    wb_gtmi_pfm_mis = scale_values(wb_gtmi_pfm_mis)
  ) |> 
  # edit WJP indicators to: (1) use 2018 data for 2017 in WJP and drop data if year < 2015
  arrange(
    iso3, year
  ) |> 
  mutate(
    across(
      starts_with("wjp_rol"),
      ~ case_when(
        year == 2017 ~ lead(.), # use 2018 data for 2017
        year < 2015 ~ NA, # drop data if year < 2015
        T ~ .
      )
    )
  ) |> 
  select(
    country_code = iso3,
    year,
    everything()
  ) |> 
  select(
    -index,
    -country_name
  )

# PEFA manual update - Defining values, update for 2024
grade_pefa <- c("D" = 1,
                "D* " = 1,
                "D+" = 1.5,
                "C" = 2,
                "C+" = 2.5,
                "B" = 3,
                "A" = 4)

# Transforming the PEFA data
pefa_transformed <- pefa |>
  mutate(across(starts_with("pi_"), 
                 ~ ifelse(. %in% names(grade_pefa), 
                           grade_pefa[.], 
                           NA_real_))) |> 
  rename_with(~ gsub("^pi_", "pi_2016_", .), starts_with("pi_"))

pefa_clean <- pefa_transformed |>
  rename_with(~ paste0("wb_pefa_", .), .cols = starts_with("pi_")) |>
  select(-framework, -uhlg_01, -uhlg_01_1, -uhlg_01_2, -uhlg_01_3)

# Handling country codes, including Kosovo
pefa_country <- pefa_clean %>% 
  mutate(country_code = case_when(
    country == "Kosovo" ~ "XKX",
    TRUE ~ countrycode(country, "country.name", "iso3c", custom_match = c("Kosovo" = "XKX"))
  )) %>% 
  filter(country != "Bosnia and Herzegovina - District Brčko")

# ### Write-out this dataframe for PIGO analysis
# write_rds(
#   pefa_country,
#   here(
#     "data",
#     "output",
#     "pefa_clean_for_analysis.rds"
#   )
# )


# Identify columns that contain "pefa" and are in efi_clean
efi_pefa_subset <- efi_clean  %>% 
  select(country_code, year, contains("pefa")) %>% 
  filter(year <= 2021)

subset_colnames <- colnames(efi_pefa_subset)

# Select only relevant indicators
pefa_subset <- pefa_country %>% 
  select(
    country_code, all_of(subset_colnames)
  ) %>% 
   filter(year >= 2022)

# Merge the dataframes 
efi_pefa_merged <- bind_rows(efi_pefa_subset, pefa_subset)

efi_drop_pefa <- efi_clean %>%
  select(-contains("pefa"))

efi_clean <- left_join(
                efi_drop_pefa,
                efi_pefa_merged,
                by = c("country_code", "year")
)



# 2. fraser - market regulations
      # For the fraser data, the clean dataset is created by selecting only the
      # necessary columns, standardizing the country code variable name, casting
      # the year variable to numeric, and changing variable prefixes to be
      # in line with EFI conventions

      # NOTE 2024:
      # Change variable names https://www.fraserinstitute.org/economic-freedom/approach
fraser <- fraser |> 
  slice(-1) |> 
  setNames(as.character(fraser[1, ])) 

fraser_clean <- fraser |> 
  clean_names() 

# Define the columns to convert to double type
double_columns <- c(
  "year",
  "x5a_credit_market_regulation",
  "x3d_foreign_currency_bank_accounts",
  "x4diii_freedom_of_foreigners_to_visit", 
  "x4dii_capital_controls",
  "x2b_impartial_courts",
  "x2e_legal_integrity",
  "x2a_judicial_independence",
  "x2f_contracts"
)

fraser_clean <- fraser_clean %>% 
  transmute(
    country_code = iso_code_3,
    across(all_of(double_columns), as.double)
  ) |> 
  rename_with(
    ~ str_replace(., "^x[:alnum:]+_", "fraser_efw_")
  )

###
### After using the new fraser file, 4 indicators would need renaming in db_var
### at the time of transforming the variables, Batlesman Institute seems to be the official source
###


  

# 3. romelli - central bank independence
#       The romelli data is cleaned by setting the country code variable name
#       and casting the year variable to numeric
romelli_clean <- romelli |>
  transmute(
    country_code = wb_a3,
    year = as.numeric(year),
    romelli_cbi_central_bank_independence = lvau
  )

# 4. oecd - employment protection laws
#       To clean this data, first the necessary data is taken from both the 
#       regular and temporary employees datasets, as well as standardizing
#       country code and making the year variable numeric. Then these two 
#       categories are merged together.
oecd_epl_regular_clean <- oecd_epl_regular |>
  filter(
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    # the country code used by the OECD is equivalent to the WB
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_regular = Value
  )

oecd_epl_temporary_clean <- oecd_epl_temporary |>
  filter(
    # Series == "Version 1 (1985-2019)"
    Series == "Version 4 (2013-2019)"
  ) |>
  transmute(
    country_code = COUNTRY,
    year = as.numeric(TIME),
    oecd_epl_temporary = Value
  )

# note that there is higher coverage for regular vs. temporary contracts
oecd_epl_clean <- oecd_epl_regular_clean |>
  full_join(
    oecd_epl_temporary_clean
  )

# 5. spi - statistical performance indicators
#       First  generate an average index of the census and survey indexes, and
#       then perform the standard cleanings of changing the country code column
#       name and casting the year as numeric

# SPI.DIM4.1.CEN.INDEX	SPI.DIM4.1.SVY.INDEX Dimension 5.2: Standards and Methods
# SPI.DIM5.2.INDEX
spi_clean <- spi %>%
slice(-1)|> 
  mutate(
    spi_dim4_1_cen_index = as.numeric(spi_dim4_1_cen_index),
    spi_dim4_1_svy_index = as.numeric(spi_dim4_1_svy_index),
    spi_dim5_2_index = as.numeric(spi_dim5_2_index),
    date = as.numeric(date) # Relevant cols as numeric
  ) |> 
  rowwise() |> 
  # generate an average index of the census and survey indexes
  mutate(
    spi_census_and_survey_index = mean(
      c(spi_dim4_1_cen_index, spi_dim4_1_svy_index),
      na.rm = TRUE
    )
  ) |> 
  ungroup() |> 
  transmute(
    country_code = iso3c,
    year = as.numeric(date),
    spi_census_and_survey_index,
    spi_std_and_methods = spi_dim5_2_index # standards and methods
  )

# 6. aspire data
#       Filter for the correct indicators, standardize name for country codes 
#       remove non-country codes, and change shape of the data. 
aspire_clean <- aspire |> 
  filter(
    indicator_name %in% c(
      "Adequacy of benefits (%) -All Social Protection and Labor",
      "Coverage (%) -All Social Protection and Labor"
    )
  ) |> 
  transmute(
    # identify non-country codes (aspire includes regions, for example)
    country_code = countrycode(
      Country_Code, 
      origin = "iso3c", destination = "iso3c",
      # create exception for kosovo
      custom_match = c("XKX" = "XKX")
    ),
    year = as.numeric(Year),
    Indicator_Code,
    value = val
  ) |> 
  filter(
    # exclude non-country codes
    !is.na(country_code)
  ) |> 
  pivot_wider(
    id_cols = c(country_code, year),
    values_from = value,
    names_from = Indicator_Code
  ) |> 
  rename(
    wb_aspire_coverage = per_allsp.cov_pop_tot,
    wb_aspire_adequacy_benefits = per_allsp.adq_pop_tot
  )


# 7. rise data
rise_clean <- rise |> 
  clean_names()

# 8. wdi data
# Step 1: Extract variable names and labels
var_labels <- sapply(wdi, function(x) attr(x, "label"))  # Extract labels from the attributes
var_names <- names(var_labels)  # Get the variable names




wdi_clean <- wdi |>
  rename(
    country_name = countryname,
    country_code = countrycode
  ) |>
  rename_with(
    ~ str_to_lower(.) %>% 
      str_replace_all("^wdi_", "wdi_"), 
      starts_with("wdi_")
  )

columns_to_drop <- c(
  "country_name",
  "wdi_dcodatotlgnzs", 
  "wdi_dtdodpvlxgnzs", 
  "wdi_shmedcmhwp3",  
  "wdi_sipovmdim",     
  "wdi_sipovmdimxq"  
)  
  
wdi_clean <- wdi_clean |>
  select(!all_of(columns_to_drop)) |>
  # rename(
  #   wdi_spdynamrtfe = wdi_shdynmortfe,
  #   wdi_spdynamrtma = wdi_shdynmortma
  # ) |>
  filter(!is.na(country_code) & country_code != ""
  ) |>
  distinct(country_code, year, .keep_all = TRUE)


# 9. vdem
vdem_clean <- vdem 

# 10. heritage
heritage_clean <- heritage |> 
  clean_names() |>
  filter(!is.na(country_code) & country_code != "")

# 11. OECD Product Market Regulation
oecd_pmr_clean <- oecd_pmr |> 
  select(
    country_code,
    year,
    PMR_2018_3_3,
    PMR_2018_1_3,
    PMR_2018_6,
    PMR_2018_1_4,
    PMR_2018_1_2,
    PMR_2018_2_1,
    PMR_2018_1_1,
    PMR_2018_2_2
  ) |>
  clean_names() |> 
  rename_with(
    # replace prefixes with efi conventions
    ~ paste0("oecd_", .),
    .cols = starts_with("pmr")
  )

# 12. Open Budget Survey
open_budget_clean <- open_budget |> 
  select(
    country_code = ISO,
    year,
    ibp_obs_obi = obi
  ) |> 
  # fix cambodia ISO3
  mutate(
    country_code = if_else(
      country_code == "KMH",
      "KHM",
      country_code
    )
  ) |> 
  # shift values one year earlier, to reflect year of measurement
  # this holds starting in year = 2015
  mutate(
    year = if_else(
      year >= 2015,  year - 1, year
    )
  )

# 13. Debt Transparency
debt_transparency_clean <- debt_transparency |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("debt")
  )

# 14. GFDB Bank Concentration
gfdb_clean <- gfdb |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("gfdb")
  )

# 15. Women, Business and the Law
wbl_clean <- wbl |> 
  clean_names() |> 
  rename_with(
    # replace prefixses with efi conventions
    ~ paste0("wb_", .),
    .cols = starts_with("wbl")
  )

excluded_country_code <- c(
  "AIA", # anguilla
  "OECD", # OECD
  "SML", # somaliland
  "ZZB", # zanzibar
  "CUB", # cuba
  "PRK", # democratic people's republic of Korea
  "KMH", # unclear, listed in Open Budget Survey
  "PSG" # palestine and gaza (VDEM)
)

cliar_indicators <- list(
  efi_clean,
  fraser_clean,
  romelli_clean,
  oecd_epl_clean,
  spi_clean,
  aspire_clean,
  rise_clean,
  wdi_clean,
  vdem_clean,
  heritage_clean,
  oecd_pmr_clean,
  open_budget_clean,
  debt_transparency_clean,
  gfdb_clean,
  wbl_clean
) |> 
  map(
    # fix country codes for full join
    ~ mutate(
        .,
        country_code = case_when(
          country_code == "ZAR" ~ "COD", # democratic republic of congo
          country_code == "ROM" ~ "ROU", # romania
          T ~ country_code
        )
      ) |> 
      filter(
        !(country_code %in% excluded_country_code)
      )
  ) |> 
  reduce(
    full_join,
    by = c("country_code", "year")
  ) |> 
  filter(
    year >= 1990
  )
  
# order column names
cliar_indicators <- cliar_indicators %>%
  select(
    country_code,
    year,
    sort(colnames(.)),
    -starts_with("country_name")
  ) |> 
  arrange(
    country_code,
    year
  ) |> 
  mutate(
    index = row_number()
  )


# verify that the indicators are selected correctly
db_variables_indicators <- db_variables |> 
  select(
    variable
  )


cliar_indicators <- cliar_indicators %>%
  # add country names
  left_join(
    wb_country_list |>
       distinct(country_code, country_name),
    by = "country_code"
  ) |>
  select(
    country_code,
    country_name,
    year,
    all_of(db_variables_indicators |> pull(variable))
  )

cliar_indicators_id <- cliar_indicators |>
  colnames()|>
  tibble(
    variable = colnames(cliar_indicators)
  )

test_that(
  "All indicators contained in metadata are in the CLIAR dataset",{
    expect_equal(
      nrow(
        db_variables_indicators |> 
          anti_join(cliar_indicators_id, by = "variable") |> 
          as.data.frame()
        ),
      0
    )
  }
)


# compute family averages
cliar_indicators_long <-
  cliar_indicators %>%
  pivot_longer(
    any_of(vars_all),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  )

# only calculate family averages for relevant institutional clusters
cliar_family_level_long <- cliar_indicators_long |>
  filter(
    family_var %in% vars_family
  ) |>
  group_by(
    country_code, year, family_var
  ) |>
  summarise(
    value = mean(value, na.rm = TRUE),
    .groups = "drop"
  )

cliar_family_level <- cliar_family_level_long |>
  pivot_wider(
    id_cols = c(country_code, year),
    names_from = family_var,
    names_glue = "{family_var}_avg",
    values_from = value
  )

cliar_indicators_clean <- cliar_indicators |>
  left_join(
    cliar_family_level,
    by = c("country_code", "year")
  ) |>
  filter(!country_code %in% c("DDR", "YMD"))

cliar_indicators_clean %>%
  filter(is.na(country_code))

# there are 218 country codes listed in the WB's official website
# https://datahelpdesk.worldbank.org/knowledgebase/articles/906519-world-bank-country-and-lending-groups


# a. verify that all the country codes from the official data are included
test_that(
  "Verify that all the country codes from the official data are included",
  expect_equal(
    # number of rows is zero
    cliar_indicators_clean |> 
      distinct(country_code, country_name) |> 
        anti_join(
          wb_country_list |> 
            distinct(country_code, country_name),
          by = c("country_code", "country_name")
        ) |> nrow(),
      0
  )
)

# b. verify that cliar has distinct country-year
test_that(
  "Verify that CLIAR has distinct country years",{
    expect_equal(
      nrow(cliar_indicators_clean),
      cliar_indicators_clean |> 
        distinct(country_code, year) |> 
        nrow()
    )
  }
)

distinct_years_per_country <- cliar_indicators_clean %>%
  group_by(country_name) %>%
  summarize(distinct_years = n_distinct(year))

# c. verify that all countries have complete year coverage
test_that(
  "Verify that country codes have coverage for all years",{
    expect_equal(
      # calculate number of years covered by country
      cliar_indicators_clean |> 
        count(country_code) |> 
        pull(n) |> 
        unique(),
      ref_year - 1990
    )
  }
)

cliar_indicators_diagnostic <- cliar_indicators_clean |>
  select(-country_name) |> 
  compute_coverage(country_code, year, ref_year - 5) |> 
  left_join(
    db_variables |> select(variable, var_name, source, family_name),
    by = c("Indicator" = "variable")
  ) |> 
  select(
    `Indicator`,
    `Indicator Name` = var_name,
    `Institutional Family` = family_name,
    everything(),
    `Data Source` = source
  ) |> 
  arrange(
    `Institutional Family`,
    Indicator
  )

### Post transformation
gtmi_mistery <- cliar_indicators_clean %>%
  select(year, starts_with("wb_gtmi_")) %>%
  filter(if_any(starts_with("wb_gtmi_"), ~ !is.na(.))) %>%
  group_by(year) %>%
  summarize(count = n())


# Pivot long
cliar_indicators_long_diagnosis <- cliar_indicators_clean %>%
    filter(year >= 2000) |>
    pivot_longer(
      cols = -c(country_code, country_name, year),  # Exclude these columns
      names_to = "indicators", 
      values_to = "indicator_value"  
    )

# Apply coverage calculation from funs.R 
cliar_global_coverage <- cliar_indicators_long_diagnosis |>
  compute_global_coverage(country_name, indicators, year, indicator_value)

# Renaming and joining to db_variables classification 
cliar_global_coverage_renamed <- cliar_global_coverage |>
  mutate(
    available_share = case_when(
      !is.na(available_share) ~ as.numeric(str_remove(available_share, "%")),
      TRUE ~ NA_real_) 
    )|>
  left_join( # Join with db_variables
    db_variables |> select(variable, var_name, source, family_name, benchmarked_ctf),
    by = c("indicators" = "variable")
  ) |>
  select( # Select and reorder columns
    everything(),
    indicators,
    var_name,
    family_name,
    source,
    benchmarked_ctf
  ) |>
  arrange(
    family_name,
    indicators
  )
                                     

# Cleaning for naming conventions
cliar_global_coverage_country <- cliar_global_coverage_renamed |>
  mutate(
    country_code = case_when(
      country_name == "Channel Islands" ~ "GGY", 
      country_name == "Kosovo" ~ "XKX", 
      TRUE ~ countrycode(country_name, "country.name", "iso3c") 
    )
  ) %>% 
  filter(!is.na(available_share))

# Region naming for analysis
cliar_global_coverage_complete <- cliar_global_coverage_country |>
  left_join(
    country_income_and_region_updated,
    by = c("country_code")
  ) %>% 
  mutate(
      region = if_else(region == "North America", "Latin America & Caribbean", region)
             ) %>%
          filter(
           !is.na(region)
              ) %>% 
          mutate(
              region_short = recode(region,
                                 "Europe & Central Asia" = "ECA",
                                 "East Asia & Pacific" = "EAP",
                                 "Latin America & Caribbean" = "LAC",
                                 "Middle East & North Africa" = "MENA",
                                 "South Asia" = "SAR",
                                 "Africa Eastern and Southern" = "AFE",
                                 "Africa Western and Central" = "AFW",
                                 )
                  )


### CTF coverage
ctf_long_diagnosis <- cliar_indicators_clean %>%
                    filter(between(year,2019,2023)) |> 
                     pivot_longer(
                        cols = -c(country_code, country_name, year),  # Exclude these columns
                        names_to = "indicators", 
                        values_to = "indicator_value"  
                      )

ctf_global_coverage <- ctf_long_diagnosis |>
  compute_global_coverage(country_name, indicators, year, indicator_value)

# Renaming and joining to db_variables classification 
ctf_renamed <- ctf_global_coverage |>
  mutate(
    available_share = case_when(
      !is.na(available_share) ~ as.numeric(str_remove(available_share, "%")),
      TRUE ~ NA_real_) 
    )|>
  left_join( # Join with db_variables
    db_variables |> select(variable, var_name, source, family_name, benchmarked_ctf),
    by = c("indicators" = "variable")
  ) |>
  select( # Select and reorder columns
    everything(),
    indicators,
    var_name,
    family_name,
    source,
    benchmarked_ctf
  ) |>
  arrange(
    family_name,
    indicators
  )
                                     

# Cleaning for naming conventions
ctf_coverage_country <- ctf_renamed |>
  mutate(
    country_code = case_when(
      country_name == "Channel Islands" ~ "GGY", 
      country_name == "Kosovo" ~ "XKX", 
      TRUE ~ countrycode(country_name, "country.name", "iso3c") 
    )
  ) %>% 
  filter(!is.na(available_share))

# Region naming for analysis
ctf_coverage_country_complete <- ctf_coverage_country |>
  filter(benchmarked_ctf == "Yes") |> 
  left_join(
    country_income_and_region_updated,
    by = c("country_code")
  ) %>% 
  mutate(
      region = if_else(region == "North America", "Latin America & Caribbean", region)
             ) %>%
          filter(
           !is.na(region)
              ) %>% 
          mutate(
              region_short = recode(region,
                                 "Europe & Central Asia" = "ECA",
                                 "East Asia & Pacific" = "EAP",
                                 "Latin America & Caribbean" = "LAC",
                                 "Middle East & North Africa" = "MENA",
                                 "South Asia" = "SAR",
                                 "Africa Eastern and Southern" = "AFE",
                                 "Africa Western and Central" = "AFW",)
                  )

write_rds(
  wb_country_list,
  here("data",
       "output",
       "wb_country_list.rds")
)

write_rds(
  ctf_coverage_country_complete,
  here(
    "data",
    "output",
    "coverage_ctf_for_analysis.rds"
  )
)


### CTF coverage
ctf_year_long_diagnosis <- cliar_indicators_clean %>%
                    filter(between(year,2019,2023)) |> 
                     pivot_longer(
                        cols = -c(country_code, country_name, year),  
                        names_to = "indicators", 
                        values_to = "indicator_value"  
                      ) |>
                  left_join( # Join with db_variables
                    db_variables |> 
                      select(variable,
                             var_name,
                             source,
                             family_name,
                             benchmarked_ctf),
                            by = c("indicators" = "variable")
                  ) |>
                  select( # Select and reorder columns
                    everything(),
                    indicators,
                    var_name,
                    family_name,
                    source,
                    benchmarked_ctf
                  ) |>
                  arrange(
                    family_name,
                    indicators
                  )
                                     

# Cleaning for naming conventions
ctf_year_rename <- ctf_year_long_diagnosis |>
  mutate(
    country_code = case_when(
      country_name == "Channel Islands" ~ "GGY", 
      country_name == "Kosovo" ~ "XKX", 
      TRUE ~ countrycode(country_name, "country.name", "iso3c") 
    )
  ) 

# Region naming for analysis 
ctf_year_coverage_complete <- ctf_year_rename |>
  left_join(
    country_income_and_region_updated,
    by = c("country_code")
  ) %>% 
  mutate(
      region = if_else(region == "North America", "Latin America & Caribbean", region)
             ) %>%
          filter(
           !is.na(region)
              ) %>% 
          mutate(
              region_short = recode(region,
                                 "Europe & Central Asia" = "ECA",
                                 "East Asia & Pacific" = "EAP",
                                 "Latin America & Caribbean" = "LAC",
                                 "Middle East & North Africa" = "MENA",
                                 "South Asia" = "SAR",
                                 "Africa Eastern and Southern" = "AFE",
                                 "Africa Western and Central" = "AFW")
                  )

# write_rds(
#   ctf_year_coverage_complete,
#   here(
#     "data",
#     "output",
#     "year_coverage_ctf_for_analysis.rds"
#   )
# )
write_rds(
  cliar_indicators_long_diagnosis,
  here(
    "data",
    "output",
    "coverage_report_input.rds"
  )
)

write_rds(
  cliar_global_coverage_complete,
  here(
    "data",
    "output",
    "coverage_report_full_for_analysis.rds"
  )
)

cliar_indicators_complete <- cliar_indicators_clean |> 
  left_join(
    country_income_and_region_updated,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, year, everything()
  )

write_rds(
  cliar_indicators_complete,
  here(
    "data",
    "output",
    "compiled_indicators.rds"
  )
)

cliar_indicators_diagnostic |> 
    write_rds(
      here(
        "data",
        "output",
        "diagnostics_compiled_indicators.rds"
      )
    )




```


## Clean List of Countries
```{r, echo = FALSE, warning=FALSE, message=FALSE}


  indicators <-                                                       
      read_rds(
      here(
        "data",
        "output",
        "compiled_indicators.rds"
      )
    )

  group_list <-
    read_csv(
      here(
        "data",
        "input",
        "wb",
        "group_list.csv"
      )
    )


  country_list <-
    read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "Groups"
    ) %>%
    transmute(
      country_code = CountryCode,
      country_name = CountryName,
      group = GroupName,
      group_code = GroupCode
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )


# read in world bank standard country codes and mutate them to be compatible
  region_list <-
    read_rds(
      here(
        "data",
        "output",
        "wb_country_list.rds"
      )
    )

  
### Updated region grouping
  region_list_compliment <-
    read_rds(
      here(
        "data",
        "output",
        "grouping_country_income_and_region_updated.rds"
      )
    )

  
### Define the indexing regions
target_regions <- c("Africa Eastern and Southern", "Africa Western and Central")

region_list_updated <- region_list %>%
  # Add Abbreviations to AFE and AFE regions in one dataframe
  left_join(
    region_list_compliment %>% 
      mutate(region_code = recode(region,
                                  "Africa Eastern and Southern" = "AFE",
                                  "Africa Western and Central" = "AFW",
                                  .default = region)) %>% 
      transmute(country_code, detailed_region = region, detailed_region_code = region_code),
    by = "country_code"
  ) %>%
  # Index SSF region to effectively reclassify it into AFE and AFW
  mutate(
    group_name      = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region, group_code),
    group_code = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region_code, group_code)
  ) %>%
  # Ensure that region_code follows the changes regions
  select(names(region_list)[1:2], group_name, group_code)

  
country_list <-
  indicators %>%
  select(country_code) %>%
  unique %>%
  left_join(country_list)


country_list <-
  country_list %>%
  filter(
    group %in% group_list$group_name
  ) %>%
  unique



### Define the indexing regions
target_regions <- c("Africa Eastern and Southern", "Africa Western and Central")

country_list_updated <- country_list %>%
  # Add Abbreviations to AFE and AFE regions in one dataframe
  left_join(
    region_list_compliment %>% 
      mutate(region_code = recode(region,
                                  "Africa Eastern and Southern" = "AFE",
                                  "Africa Western and Central" = "AFW",
                                  .default = region)) %>% 
      transmute(country_code, detailed_region = region, detailed_region_code = region_code),
    by = "country_code"
  ) %>%
  # Index SSF region to effectively reclassify it into AFE and AFW
  mutate(
    group_name      = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region, group),
    group_code = if_else(group_code == "SSF" & detailed_region %in% target_regions,
                          detailed_region_code, group_code)
  ) %>%
  # Ensure that region_code follows the changes regions
  select(names(region_list)[1:2], group_name, group_code) 
  
group_list_updated <- group_list %>%
  # Remove the "Sub-Saharan Africa" row
  filter(group_name != "Sub-Saharan Africa") %>%
  # Append new rows with the desired groups and group_category "Region"
  bind_rows(
    tibble(
      group_name = c("Africa Eastern and Southern", "Africa Western and Central"),
      group_category = "Region"
    )
  ) %>% 
  arrange(group_category, group_name)


write_rds(
  country_list_updated,
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

write_rds(
  group_list_updated,
  here(
    "data",
    "output",
    "wb_country_groups.rds"
  )
)
  
```


## Calculate distance to frontier

Closeness to frontier (CTF) is global, meaning that we identify the worst and best performance in the full sample (all countries). For each indicator $i$, we compare the last available value of indicator $i$ with the worst and best
performance for indicator $i$ among all countries and in the last $y$ years (2013 - most recent data).^[In the [Doing Business report](https://www.doingbusiness.org/content/dam/doingBusiness/media/Annual-Reports/English/DB17-Chapters/DB17-DTF-and-DBRankings.pdf) they consider the last 5 years, but here for some indicators we have shorter time series.]

```{r, echo = FALSE, warning=FALSE, message=FALSE}

#load in cleaned indicators from step 3
cliar_indicators <-
  read_rds(
    here(
      "data",
      "output",
      "compiled_indicators.rds"
    )
  ) %>%
  # filter to only years 2013 or later
  filter(
    year >= 2013
  )

#read in country list from step 4
country_list <- read_rds(
  here(
    "data",
    "output",
    "wb_country_list.rds"
  )
)

#read in db_variables
db_variables <- read_rds(
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)

vars_ctf <- db_variables |>
  filter(
    benchmarked_ctf == "Yes"
  ) |>
  pull(variable)

# country income group and region
country_income_and_region <- read_xlsx(
      here(
        "data",
        "input", 
        "wb",
        "CLASS.xlsx"
      ),
      sheet = "List of economies",
      n_max = 219
    ) %>%
    transmute(
      country_code = Code,
      region = Region,
      income_group = `Income group`
    ) |>
  # exclude non-WB member countries
  filter(
    country_code != "CUB" & 
      country_code != "PRK"
  )


#create new table to hold rescaled values
cliar_indicators_rescaled <- cliar_indicators |> 
  mutate(
    # V-DEM: political and executive corruption: flip direction because “The directionality of the V-Dem corruption index runs from less corrupt to more corrupt unlike the other V-Dem variables that generally run from less democratic to more democratic situation”.
    vdem_core_v2x_pubcorr = -1 * vdem_core_v2x_pubcorr,
    vdem_core_v2x_execorr = -1 * vdem_core_v2x_execorr,
    # V-DEM: political polarization, higher scores denote higher polarization, which can lead to institutional weakness
    # so we decide to flip the indicator by multiplying by -1
    vdem_core_v2cacamps = -1 * vdem_core_v2cacamps,
    # PRM indicators: Countries are graded between 0 (less control/involvement) and 6 (more control/involvement).
    # Methodological note for PRM indicates that 1998 and 2013 indicators are comparable,
    # but not with 2018 due to change in methodology, so we only retain post-2018 data.
    across(
      c(
        starts_with("oecd_pmr")
      ),
      ~ ifelse(year < 2018, NA, 6 - .x)
    ),
    # Enterprise Survey: Percent Of Firms Identifying X As A Major Constraint
    across(
      c(starts_with("wb_enterprisesurveys")),
      ~ 100 - .
    ),
    # Freedom house: Countries are graded between 1 (most free) and 7 (least free)
    across(
      c(starts_with("fh_fiw")),
      ~ (8 - .x)
    ),
    # WDI: ensure that pupil-teacher ratio increases lead to a worse score
    # note that because there is no pre-defined maximum for the ratio so we flip direction multiplying by -1
    across(
      c(wdi_seprmenrltczs, wdi_sesecenrltczs),
      ~ -1 * .x
    ),
    # GFDB:Bank concentration, the higher it is, the less competition. therefore indicator is flipped
    wb_gfdb_oi_01 = 100 - wb_gfdb_oi_01
  )



country_average <-
  #filter only data from years we are using
  cliar_indicators_rescaled %>%
  filter(between(year,2019,2023)) |> 
  #this groups countries together so average can be taken 
  group_by(
    country_code
  ) %>%
  summarise(
    across(
      all_of(c(vars_static_ctf)),
      ~ mean(., na.rm = TRUE)
    ),
    #Try switching with 2023 for max(year)
    wdi_nygdppcapppkd = wdi_nygdppcapppkd[year == 2023]
  )

country_last_year <-
  #filter only data from years we are using
  cliar_indicators_rescaled %>%
  filter(between(year,2019,2023)) |>  
  arrange(country_code, year) |> 
  #this groups countries together so average can be taken 
  group_by(
    country_code
  ) |> 
  select(
    all_of(c(vars_static_ctf))
  ) |> 
  # fill missing observations for each indicator with the latest available data
  fill() |> 
  # slice last available data for each country_code
  slice_tail() |> 
  ungroup()




# static
min_max <-
  cliar_indicators_rescaled %>%
  filter(between(year,2019,2023)) |> 
  summarise(
    across(
      all_of(vars_static_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  )

# dynamic: note that there are quite a few cases of Infinite warnings (due to missingness)
min_max_dynamic <- cliar_indicators_rescaled %>%
  filter(
    between(year,2014,2023)
  ) |> 
  summarise(
    across(
      all_of(vars_dynamic_ctf),
      list(
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE)
      ),
      .names = "{.col}-{.fn}"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_to = c("variable", ".value"),
    names_pattern = "(.*)-(.*)"
  ) %>%
  filter(!is.infinite(min) & !is.infinite(max))


ctf <-
  country_average %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )

# reproduce CTF scores using latest available data for each country-indicator
ctf_static_last_year <- country_last_year %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max,
    by = "variable"
  ) %>%
  mutate(
    ctf = (min - value) / (min - max),
    ctf = ifelse(
      ctf == 0,
      0.01,
      ctf
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code"),
    names_from = "variable",
    values_from = "ctf"
  ) %>%
  select(-starts_with("gdp")) %>%
  left_join(
    country_average %>%
      select(country_code)
  )
  
ctf_dynamic <-
  cliar_indicators_rescaled %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  left_join(
    min_max_dynamic,
    by = c("variable")
  ) %>%
  mutate(
    ctf_dyn = (min - value) / (min - max),
    ctf_dyn = ifelse(
      ctf_dyn == 0,
      0.01,
      ctf_dyn
    )
  ) %>%
  pivot_wider(
    id_cols = c("country_code", "year"),
    names_from = "variable",
    values_from = "ctf_dyn"
  ) %>%
  left_join(
    cliar_indicators_rescaled %>%
      select(country_code, year)
  )



# static
group_ctf <-
  #join country list with ctf
  country_list %>%
  left_join(
    ctf,
    by = "country_code"
  ) %>%
  #group by group code
  group_by(
    group_code, 
    group_name
  ) %>%
  #take median
  summarise(
    across(
      c(all_of(vars_static_ctf)),
      ~ median(., na.rm = TRUE)
    ),
    .groups = "drop"  # optionally ungroup after summarise
  ) %>%
  filter(!is.na(group_name)) %>%  # use group_name instead of group
  rename(
    country_name = group_name,  # rename group_name to country_name
    country_code = group_code
  )

#add group_ctf value to ctf dataset
ctf <- tibble::add_column(ctf, country_group = 0, .after = "country_code")
group_ctf <- tibble::add_column(group_ctf, country_group = 1, .after = "country_code")

# dynamic
group_ctf_dynamic <- country_list %>%
  #join country list with ctf
  left_join(
    ctf_dynamic,
    by = "country_code",
    relationship = "many-to-many"
  ) %>%
  # group by group_code, group_name, and year
  group_by(group_code, group_name, year) %>%
  # take median
  summarise(across(all_of(vars_dynamic_ctf),
                   ~ median(., na.rm = TRUE)),
            .groups = "drop") %>%  # optionally drop grouping
  # filter out rows with missing group_name
  filter(!is.na(group_name)) %>%
  # rename group_name to country_name and group_code to country_code
  rename(country_name = group_name,
         country_code = group_code)

ctf_dynamic <- add_column(ctf_dynamic, country_group = 0, .after = "country_code")
group_ctf_dynamic <- add_column(group_ctf_dynamic, country_group = 1, .after = "country_code")




# static
ctf <-
  ctf %>%
  # add country codes and names
  left_join(
    country_list |> distinct(country_code, country_name),
    by = c("country_code")
  ) |>
  # add gdp per capita (PPP) data
  # use average value (as in legacy ctf)
  left_join(
    country_average |> select(country_code, wdi_nygdppcapppkd),
    by = c("country_code")
  ) |>
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) |>
  bind_rows(group_ctf) %>%
  ungroup() %>%
  arrange(country_name) |>
  select(
    country_code,
    country_name,
    everything()
  )

# dynamic
ctf_dynamic <-
  ctf_dynamic %>%
  # add country codes and names
  left_join(
    country_list %>% distinct(country_code, country_name),
    by = "country_code"
  ) %>%
  # add gdp per capita (PPP) data
  left_join(
    cliar_indicators %>% select(country_code, year, wdi_nygdppcapppkd),
    by = c("country_code", "year")
  ) %>%
  # rename and transform gdp per capita to log
  mutate(
    log_gdp = log(wdi_nygdppcapppkd)
  ) %>%
  bind_rows(group_ctf_dynamic) %>%
  ungroup() %>%
  arrange(country_name) %>%
  select(
    country_code,
    country_name,
    everything()
  )


# static
ctf_long <-
  ctf %>%
  pivot_longer(
    all_of(vars_static_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var),
    by = "variable"
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group_name),
    relationship = "many-to-many",
    by = "country_code",
  )

ctf_long_clean <-
  ctf_long %>%
  group_by(family_name, family_var, country_name, country_code, group_name, country_group) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_long) %>% 
  rename(group = group_name)

# dynamic
ctf_dynamic_long <-
  ctf_dynamic %>%
  pivot_longer(
    all_of(vars_dynamic_ctf),
    names_to = "variable"
  ) %>%
  select(-contains("gdp")) %>%
  left_join(
    db_variables %>%
      select(variable, var_name, family_name, family_var)
  ) %>%
  left_join(
    country_list %>%
      select(country_code, group_name),
    relationship = "many-to-many",
    by = "country_code",
  ) 

ctf_dynamic_long_clean <-
  ctf_dynamic_long %>%
  group_by(family_name, family_var, country_name, country_code, country_group, group_name, year) %>%
  summarise(value = median(value, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    variable = family_var,
    var_name = family_name
  ) %>%
  bind_rows(ctf_dynamic_long) %>% 
  rename(group = group_name)



# static
ctf_static_family <- ctf |> 
  compute_family_average(
    vars = vars_static_family_ctf,
    db_variables = db_variables
  )

# dynamic
ctf_dynamic_family <- ctf_dynamic |> 
  # only retain even years because data is updated every two-years
  filter(
    year %% 2 == 0
  ) |> 
  compute_family_average(
    vars = c(vars_dynamic_family_ctf, vars_dynamic_partial_ctf),
    type = "dynamic",
    db_variables = db_variables
  )

# join family averages to ctfs
ctf_clean <- ctf |> 
  left_join(
    ctf_static_family,
    by = "country_code"
  )

ctf_dynamic_clean <- ctf_dynamic |> 
  left_join(
    ctf_dynamic_family,
    by = c("country_code", "year")
  )


# select family averages to diagnose
vars_family_static_ctf <- ctf_static_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

vars_family_dynamic_ctf <- ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  colnames() |> 
  str_replace(
    "_avg",
    ""
  )

# missingness by institutional family average ### [KEY FOR GRAPH]
# static
ctf_static_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Static CTF",
    subtitle = "Unit of Analysis: Country"
  )

# dynamic
ctf_dynamic_family |> 
  select(ends_with("avg")) |> 
  naniar::gg_miss_var(
    show_pct = TRUE
  ) +
  ggtitle(
    "Percentage of Missing Institutional Family Averages: Dynamic CTF",
    subtitle = "Unit of Analysis: Country-Year"
  )

# static family averages diagnosis
theme_set(
  theme_minimal()
)


vars_family_static_ctf |> 
  set_names(vars_family_static_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_static_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss(variable)))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Static Benchmarking"
  )
  
# dynamic family averages diagnosis
vars_family_dynamic_ctf |> 
  set_names(vars_family_dynamic_ctf) |> 
  map_dfr(
    ~ select(
      ctf,
      all_of(
        intersect(vars_dynamic_ctf, get(.))
        )
      )|> 
        miss_var_summary(),
    .id = "family_var"
  ) |> 
  left_join(db_variables) |> 
  select(-variable) |> 
  rename(variable = var_name) |> 
  ggplot(
    aes(pct_miss, variable)
  ) +
  geom_col() +
  geom_label(
    aes(label = round(pct_miss(variable)))
  ) +
  facet_wrap(
    vars(family_var),
    scales = "free_y",
    ncol = 2
  ) +
  ggtitle(
    "Missingness by Indicator in the Dynamic Benchmarking"
  )




test_that(
  "All countries are covered",
  {
    expect_setequal(
      ctf_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
    expect_setequal(
      ctf_dynamic_clean |> filter(country_group == 0) |> distinct(country_code) |> pull(),
      country_list |> distinct(country_code) |> pull()
    )
  }
)

test_that(
  "All indicators are covered",
  {
    ## Shel added _avg to the pattern to take care of the new family level indicators (that all have an _avg suffix)
    expect_setequal(
      ctf_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_static_ctf
    )
    expect_setequal(
      ctf_dynamic_clean |> colnames() |> str_subset("year|country|gdp|_avg$", negate = TRUE),
      vars_dynamic_ctf
    )
  }
)




db_variables <- db_variables %>% 
  mutate(
    across(where(is.character), str_squish)
  ) |> 
  rename(
    rank_id = indicator_order
  ) |> 
  mutate(
    rank_id = rank_id + 1
  )

# add family level vars
family_level_vars <- db_variables %>% 
  distinct(family_var, family_name) %>% 
  rowwise() %>% 
  mutate(
    variable = paste0(family_var, "_avg"),
    var_name = paste0(family_name, " Average"),
    var_level = "indicator",
    description = "The cluster-level average is an unweighted average of the corresponding and included indicators of this cluster. See Methodological note for details on the inclusion criteria.",
    description_short = "The cluster-level average is an unweighted average of the corresponding and included indicators for this cluster.",
    source = "CLIAR",
    benchmarked_ctf = "Yes",
    rank_id = 1
  )

db_variables <- db_variables %>% 
  bind_rows(family_level_vars) %>%
  arrange(family_var, rank_id)





ctf_complete <- ctf_clean |> 
  left_join(
    country_income_and_region,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, everything()
  )

ctf_dynamic_complete <- ctf_dynamic_clean |> 
  left_join(
    country_income_and_region,
    by = c("country_code")
  ) |> 
  select(
    country_code, country_name, income_group, region, year, everything()
  )




ctf_static_variance <- ctf_complete |> 
  compute_family_variance(
    vars_static_ctf,
    db_variables = db_variables
  )

ctf_dynamic_variance <- ctf_dynamic_complete |> 
  compute_family_variance(
    vars_dynamic_ctf,
    type = "dymamic", 
    db_variables
  )




ctf_static_last_year_long <- ctf_static_last_year |> 
  pivot_longer(
    cols = c(
      all_of(vars_static_ctf)
    ),
    names_to = "variable",
    values_to = "ctf_last_year"
  )

ctf_static_long <- ctf_clean |> 
  filter(country_group == 0) |> 
  select(country_code, all_of(vars_static_ctf)) |> 
  pivot_longer(
    cols = c(
      all_of(vars_static_ctf)
    ),
    names_to = "variable",
    values_to = "ctf_year_average"
  )

# merge datasets using country code and variable to compute correlation
ctf_robustness <- ctf_static_last_year_long |> 
  inner_join(
    ctf_static_long,
    by = c("country_code", "variable")
  )

# (a) scatterplot of last year vs. year-average ctf scores
ctf_robustness |> 
  ggplot() +
  geom_point(
    aes(ctf_year_average, ctf_last_year),
    color = "steelblue3",
    alpha = 0.7
  ) +
  labs(
    x = "CTF score: 5-year average",
    y = "CTF score: latest available data",
    caption = "The unit of analysis is at the country-indicator level. Please note that indicators for which either value were missing are not plotted."
  ) +
  ggtitle(
    "Correlation between CTF scores computed using (a) 5-Year Average and (b) Last-Year values for indicators"
  ) +
  theme_minimal()

# (b) distribution of correlations by indicator
ctf_robustness |> 
  group_by(variable) |> 
  summarise(
    correlation = cor(ctf_last_year, ctf_year_average, use = "pairwise.complete", method = "pearson")
  ) |> 
  ggplot() +
  geom_histogram(
    aes(correlation, y = stat(width*density), binwidth = 0.01)
  ) +
  geom_vline(
    xintercept = 0.95,
    linetype = "dashed",
    color = "red3"
  ) +
  scale_y_continuous(
    labels = percent_format()
  ) +
  coord_cartesian(
    xlim = c(0.9, 1)
  ) +
  labs(
    x = "Correlation between CTF scores",
    y = "Percentage of Indicators",
    caption = "Dashed red line indicators a correlation above 0.95. 5 out of 137 (3.6%) indicators have a correlation below 0.95. No indicators have a correlation between 0.9."
  ) +
  ggtitle(
    "Distribution of indicator-level correlations of CTF scores"
  ) +
  theme_minimal()




write_rds(
  ctf_complete,
  here(
    "data",
    "output",
    "closeness_to_frontier.rds"
  )
)

write_rds(
  ctf_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_long.rds"
  )
)

write_rds(
  ctf_dynamic_complete,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic.rds"
  )
)

write_rds(
  ctf_dynamic_long_clean,
  here(
    "data",
    "output",
    "closeness_to_frontier_dynamic_long.rds"
  )
)

write_rds(
  ctf_static_variance,
  here(
    "data",
    "output", 
    "closeness_to_frontier_var_static.rds"
  )
)

write_rds(
  ctf_dynamic_variance,
  here(
    "data",
    "output", 
    "closeness_to_frontier_var_dynamic.rds"
  )
)

write_rds(
  db_variables,
  here(
    "data",
    "output",
    "db_variables.rds"
  )
)




```


## Output the spatial data 
```{r, echo = FALSE, message = FALSE, warning = FALSE}

ctf <-
  read_rds(
    here(
      "data",
      "output",
      "closeness_to_frontier.rds"
    )
  )
avg_columns = names(ctf)[grep("_avg", names(ctf))]
raw_indicators <-
  read_rds(
    here(
      "data",
      "output",
      "compiled_indicators.rds"
    )
  )

db_variables <-
  read_rds(
    here(
      "data",
      "output",
      "db_variables.rds"
    )
  )


world_map <-
  read_sf(
    here(
      "data",
      "input",
      "wb",
      "WB_countries_Admin0_lowres.geojson"
    )
  )

disputed_areas <-
  read_sf(
    here(
      "data",
      "input",
      "wb",
      "WB_disputed_areas_Admin0_10m_lowres.geojson"
    )
  )

disputed_areas <-
  disputed_areas %>%
  transmute(country_code = str_trim(WB_A3)) %>%
  filter(
    !is.na(country_code),
    country_code != ""
  )

world_map <-
  world_map %>%
  select(country_code = WB_A3) 

world_map <-
  world_map %>%
  bind_rows(
    disputed_areas
  )

# simplify map to improve loading performance
simple_world_map <-
  world_map %>%
  # fix wrapping of dateline to avoid spurious ribbon
  # source: https://github.com/r-spatial/sf/issues/1046
  st_transform(4326) %>% 
  st_wrap_dateline() |> 
  # project into robinson coordinate system
  st_transform(crs = '+proj=robin') %>%
  # simplify polygons to improve rendering
  st_simplify(
    dTolerance = 0.05
  ) 


ctf <-
  ctf %>%
  pivot_longer(
    cols = all_of(c(vars_static_ctf, avg_columns)),
    values_to = "ctf"
  ) %>%
  mutate(
    bin = case_when(
      ctf < .2 ~ "0.0 - 0.2",
      ctf < .4 ~ "0.2 - 0.4",
      ctf < .5 ~ "0.4 - 0.6",
      ctf < .8 ~ "0.6 - 0.8",
      ctf <= 1 ~ "0.8 - 1.0" 
    )
  ) %>%
  pivot_wider(
    id_cols = starts_with("country_"),
    names_from = name,
    values_from = c(bin, ctf)
  )



raw <-
  raw_indicators %>%
  select(
    -c(income_group, region)
  ) %>%
  pivot_longer(
    cols = 4:ncol(.)
  ) %>%
  filter(!is.na(value)) %>%
  group_by(country_code,name) %>%
  filter(year == max(year)) %>%
  pivot_wider(
    values_from = c(value, year),
    names_from = name,
    id_cols = country_code
  )

final_world_map <-
  world_map %>%
  left_join(
    raw
  ) %>%
  left_join(
    ctf
  )


final_world_map %>%
  write_rds(
    here(
      "data",
      "output",
      "indicators_map.rds"
    )
  )


final_world_map


```


## Move final data to app folder

```{r, echo = FALSE, message=FALSE, warning=FALSE}

file.copy(
  list.files(
    here(
      "data",
      "output"
    ),
    full.names = TRUE
  ),
  here(
    "..",
    "app",
    "data"
  ),
  recursive = TRUE,
  overwrite = TRUE
)

```



























































































